---
title: "mike_gene_lists"
output: html_document
---

# General Script to generate lists of interest.
# 7/30/20

# 1-1 DEGs in common and not between Zeb heart_51_56 (24 hpf) and Ciona endo, heart, (and mes) (Larva). And other exploratory analyses.
# Also uses human orthologs.  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(Seurat)
library(dplyr)
library(ggplot2)
```

```{r include=TRUE}
one_one_dir = "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/get_geneset_attempts/v3/one_to_one_khid_zeb_gene_dict.csv" 

one_one_df <- read.table(one_one_dir,
                         sep = ",",
                         header = FALSE,
                         stringsAsFactors = FALSE)

one2one_khid_list = one_one_df$V1
one2one_zeb_genes = one_one_df$V2
```

# Import KHID -> Human Ortholog File
```{r include=TRUE}
khid_human_ortho_dir <- "/home/pprakriti/Desktop/orthology_maps_temps/ANISEED-Cirobu-GeneName-3bestBlastHitHuman.rnames"
khid_human_ortho_df <- read.table(khid_human_ortho_dir,
                                  sep = "\t",
                                  stringsAsFactors = FALSE,
                                  header = TRUE)
```

# Ciona TF list
```{r include=TRUE}
ciona_tf_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/ciona_regulatory_regions/ciona_TFs.csv"

ciona_tf_df <- read.table(ciona_tf_dir,
                          sep = ",",
                          stringsAsFactors = FALSE,
                          header = TRUE)
```

```{r include=TRUE}
# 1863 -> 964 
ciona_tfs <- ciona_tf_df$KH.model.ID
ciona_tfs <- ciona_tfs[!ciona_tfs == ""]
ciona_tfs <- paste("KH2012:", ciona_tfs, sep = "")

# 258
one2one_logic <- ciona_tfs %in% one2one_khid_list
one2one2_ciona_tfs <- ciona_tfs[one2one_logic]
```
############################################################

# 7/30/20

# Get all DEGs (logFC > 1) for Zeb heart_51_56.
```{r include=TRUE}
mike_zeb_heart_degs <- c(rownames(zeb_ans_list$edgeR_res_list$heart_51_56_noto),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_muscles),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_pec_fin_bud),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_panc_prim_endo),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_meso),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_leuko),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_diff_neus),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_epi_1),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_epi_2),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_heart_52),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_tail_spinal_cord))

# 1871 
mike_zeb_heart_degs <- unique(mike_zeb_heart_degs)

# 313
mike_zeb_heart_one2one_indices <- which(one2one_zeb_genes %in% mike_zeb_heart_degs)
```

# Ciona Endo, Heart, Meso DEGs.
```{r include=TRUE}
mike_ciona_endo_degs <- c(rownames(ciona_ans_list$edgeR_res_list$endo_cns),
                          rownames(ciona_ans_list$edgeR_res_list$endo_noto),
                          rownames(ciona_ans_list$edgeR_res_list$endo_heart),
                          rownames(ciona_ans_list$edgeR_res_list$endo_mus),
                          rownames(ciona_ans_list$edgeR_res_list$endo_mes),
                          rownames(ciona_ans_list$edgeR_res_list$endo_epi))

mike_ciona_heart_degs <- c(rownames(ciona_ans_list$edgeR_res_list$heart_noto),
                           rownames(ciona_ans_list$edgeR_res_list$heart_mus),
                           rownames(ciona_ans_list$edgeR_res_list$heart_mes),
                           rownames(ciona_ans_list$edgeR_res_list$heart_epi),
                           rownames(ciona_ans_list$edgeR_res_list$heart_endo),
                           rownames(ciona_ans_list$edgeR_res_list$heart_cns))

mike_ciona_mes_degs <- c(rownames(ciona_ans_list$edgeR_res_list$mes_noto),
                         rownames(ciona_ans_list$edgeR_res_list$mes_heart),
                         rownames(ciona_ans_list$edgeR_res_list$mes_mus),
                         rownames(ciona_ans_list$edgeR_res_list$mes_epi),
                         rownames(ciona_ans_list$edgeR_res_list$mes_endo),
                         rownames(ciona_ans_list$edgeR_res_list$mes_cns))

# 3287 -> 1171 
mike_ciona_endo_degs <- unique(mike_ciona_endo_degs)
mike_ciona_endo_one2one_indices <- which(one2one_khid_list %in% mike_ciona_endo_degs)
# 2379 -> 926 
mike_ciona_heart_degs <- unique(mike_ciona_heart_degs)
mike_ciona_heart_one2one_indices <- which(one2one_khid_list %in% mike_ciona_heart_degs)
# 1504 -> 534
mike_ciona_mes_degs <- unique(mike_ciona_mes_degs)
mike_ciona_mes_one2one_indices <- which(one2one_khid_list %in% mike_ciona_mes_degs)
```

# What pairwise indices are in common?
```{r include=TRUE}
# 202
cz_endo_heart <- intersect(mike_ciona_endo_one2one_indices, mike_zeb_heart_one2one_indices)
# 168
cz_heart_heart <- intersect(mike_ciona_heart_one2one_indices, mike_zeb_heart_one2one_indices)
# 97
cz_mes_heart <- intersect(mike_ciona_mes_one2one_indices, mike_zeb_heart_one2one_indices)
```

# What indices are shared among Ciona Endo and Heart?
```{r include=TRUE}
# 164 (Heart and Endo share a lot of 1-1 orthologs with Zeb Heart). # 93 in common among all.
mike_common_indices <- intersect(cz_endo_heart, cz_heart_heart)
mike_only_endo <- setdiff(cz_endo_heart, cz_heart_heart)
mike_only_heart <- setdiff(cz_heart_heart, cz_endo_heart)
```

# Gene Lists.
```{r include=TRUE}
endo_khids <- one2one_khid_list[mike_only_endo]
endo_human_df <- khid_human_ortho_df[khid_human_ortho_df$Gene.ID %in% endo_khids, ]
endo_human_df

heart_khids <- one2one_khid_list[mike_only_heart]
heart_human_df <- khid_human_ortho_df[khid_human_ortho_df$Gene.ID %in% heart_khids, ]
heart_human_df

common_khids <- one2one_khid_list[mike_common_indices]
common_human_df <- khid_human_ortho_df[khid_human_ortho_df$Gene.ID %in% common_khids, ]
common_human_df
```
# csv files
```{r include=TRUE}
write.table(x = common_human_df, 
            file = "common_orthologs.csv", 
            sep = "\t",
            row.names = FALSE)
```

```{r include=TRUE}
write.table(x = endo_human_df,
            file = "ciona_endo_orthologs.tsv",
            sep = "\t",
            row.names = FALSE)

write.table(x = heart_human_df,
            file = "ciona_heart_orthologs.tsv",
            sep = "\t",
            row.names = FALSE)

```

# 8/6/20
# Get the khids and zeb_genes for each of the gene lists.
```{r include=TRUE}
temp_only_endo <- one_one_df %>% filter(V1 %in% endo_khids)
temp_only_heart <- one_one_df %>% filter(V1 %in% heart_khids)
temp_common <- one_one_df %>% filter(V1 %in% common_khids)
```

```{r include=TRUE}
write.table(x = temp_only_endo,
            file = "endo_orthologs.csv",
            sep = ",",
            row.names = FALSE)

write.table(x = temp_only_heart,
            file = "heart_orthologs.csv",
            sep = ",",
            row.names = FALSE)

write.table(x = temp_common,
            file = "common_orthologs.csv",
            sep = ",",
            row.names = FALSE)
```








"""
Negatively Correlated Tissues
"""
# What about negative correlating Ciona tissues? How many orthologs do they share with Zeb Heart? 
```{r include=TRUE}
mike_ciona_cns_degs <- c(rownames(ciona_ans_list$edgeR_res_list$cns_noto),
                         rownames(ciona_ans_list$edgeR_res_list$cns_heart),
                         rownames(ciona_ans_list$edgeR_res_list$cns_mus),
                         rownames(ciona_ans_list$edgeR_res_list$cns_mes),
                         rownames(ciona_ans_list$edgeR_res_list$cns_epi),
                         rownames(ciona_ans_list$edgeR_res_list$cns_endo))

mike_ciona_mus_degs <- c(rownames(ciona_ans_list$edgeR_res_list$mus_noto),
                         rownames(ciona_ans_list$edgeR_res_list$mus_heart),
                         rownames(ciona_ans_list$edgeR_res_list$mus_mes),
                         rownames(ciona_ans_list$edgeR_res_list$mus_epi),
                         rownames(ciona_ans_list$edgeR_res_list$mus_endo),
                         rownames(ciona_ans_list$edgeR_res_list$mus_cns))

mike_ciona_noto_degs <- c(rownames(ciona_ans_list$edgeR_res_list$noto_heart),
                          rownames(ciona_ans_list$edgeR_res_list$noto_mus),
                          rownames(ciona_ans_list$edgeR_res_list$noto_mes),
                          rownames(ciona_ans_list$edgeR_res_list$noto_epi),
                          rownames(ciona_ans_list$edgeR_res_list$noto_endo),
                          rownames(ciona_ans_list$edgeR_res_list$noto_cns))

# We don't just care about the genes in common, but their expression levels.
# Only 127 indices in common among these tissues. 
# 2573 -> 509
mike_ciona_cns_degs <- unique(mike_ciona_cns_degs)
mike_ciona_cns_one2one_indices <- which(one2one_khid_list %in% mike_ciona_cns_degs)
# 2336 -> 380 
mike_ciona_mus_degs <- unique(mike_ciona_mus_degs)
mike_ciona_mus_one2one_indices <- which(one2one_khid_list %in% mike_ciona_mus_degs)
# 2283 -> 442
mike_ciona_noto_degs <- unique(mike_ciona_noto_degs)
mike_ciona_noto_one2one_indices <- which(one2one_khid_list %in% mike_ciona_noto_degs)

```

###########################################################

# 7/31/20 

# Does ciona mesp/any zeb mesp show up with logFC > 1?
# No for all. 
```{r include=TRUE}
c_mesp = "KH2012:KH.C3.100"
c_mesp %in% mike_ciona_heart_degs

z_mesp = c("mespaa", "mespba", "mespbab", "mespbb", "msgn1")
z_mesp %in% mike_zeb_heart_degs
```

################

# Let's see if they show up with logFC > 0.

################

# Get all DEGs (logFC > 1) for Zeb heart_51_56.
```{r include=TRUE}
mike_zeb_heart_degs_0 <- c(rownames(zeb_ans_list_0$edgeR_res_list$heart_51_56_noto),
                         rownames(zeb_ans_list_0$edgeR_res_list$heart_51_56_muscles),
                         rownames(zeb_ans_list_0$edgeR_res_list$heart_51_56_pec_fin_bud),
                         rownames(zeb_ans_list_0$edgeR_res_list$heart_51_56_panc_prim_endo),
                         rownames(zeb_ans_list_0$edgeR_res_list$heart_51_56_meso),
                         rownames(zeb_ans_list_0$edgeR_res_list$heart_51_56_leuko),
                         rownames(zeb_ans_list_0$edgeR_res_list$heart_51_56_diff_neus),
                         rownames(zeb_ans_list_0$edgeR_res_list$heart_51_56_epi_1),
                         rownames(zeb_ans_list_0$edgeR_res_list$heart_51_56_epi_2),
                         rownames(zeb_ans_list_0$edgeR_res_list$heart_51_56_heart_52),
                         rownames(zeb_ans_list_0$edgeR_res_list$heart_51_56_tail_spinal_cord))

# 9296 vs. 1871 
mike_zeb_heart_degs_0 <- unique(mike_zeb_heart_degs_0)

# 1560 vs. 313 
mike_zeb_heart_one2one_indices_0 <- which(one2one_zeb_genes %in% mike_zeb_heart_degs_0)
```

# Ciona Endo, Heart, Meso DEGs.
```{r include=TRUE}
mike_ciona_endo_degs_0 <- c(rownames(ciona_ans_list_0$edgeR_res_list$endo_cns),
                          rownames(ciona_ans_list_0$edgeR_res_list$endo_noto),
                          rownames(ciona_ans_list_0$edgeR_res_list$endo_heart),
                          rownames(ciona_ans_list_0$edgeR_res_list$endo_mus),
                          rownames(ciona_ans_list_0$edgeR_res_list$endo_mes),
                          rownames(ciona_ans_list_0$edgeR_res_list$endo_epi))

mike_ciona_heart_degs_0 <- c(rownames(ciona_ans_list_0$edgeR_res_list$heart_noto),
                           rownames(ciona_ans_list_0$edgeR_res_list$heart_mus),
                           rownames(ciona_ans_list_0$edgeR_res_list$heart_mes),
                           rownames(ciona_ans_list_0$edgeR_res_list$heart_epi),
                           rownames(ciona_ans_list_0$edgeR_res_list$heart_endo),
                           rownames(ciona_ans_list_0$edgeR_res_list$heart_cns))

mike_ciona_mes_degs_0 <- c(rownames(ciona_ans_list_0$edgeR_res_list$mes_noto),
                         rownames(ciona_ans_list_0$edgeR_res_list$mes_heart),
                         rownames(ciona_ans_list_0$edgeR_res_list$mes_mus),
                         rownames(ciona_ans_list_0$edgeR_res_list$mes_epi),
                         rownames(ciona_ans_list_0$edgeR_res_list$mes_endo),
                         rownames(ciona_ans_list_0$edgeR_res_list$mes_cns))

# 10105 -> 2622 
mike_ciona_endo_degs_0 <- unique(mike_ciona_endo_degs_0)
mike_ciona_endo_one2one_indices_0 <- which(one2one_khid_list %in% mike_ciona_endo_degs_0)
# 6407 -> 2004 
mike_ciona_heart_degs_0 <- unique(mike_ciona_heart_degs_0)
mike_ciona_heart_one2one_indices_0 <- which(one2one_khid_list %in% mike_ciona_heart_degs_0)
# 4875 -> 1374
mike_ciona_mes_degs_0 <- unique(mike_ciona_mes_degs_0)
mike_ciona_mes_one2one_indices_0 <- which(one2one_khid_list %in% mike_ciona_mes_degs_0)
```

# What pairwise indices are in common?
```{r include=TRUE}
# 1424
cz_endo_heart_0 <- intersect(mike_ciona_endo_one2one_indices_0, mike_zeb_heart_one2one_indices_0)
# 1188 
cz_heart_heart_0 <- intersect(mike_ciona_heart_one2one_indices_0, mike_zeb_heart_one2one_indices_0)
# 890
cz_mes_heart_0 <- intersect(mike_ciona_mes_one2one_indices_0, mike_zeb_heart_one2one_indices_0)
```

# What indices are shared among Ciona Endo and Heart?
```{r include=TRUE}
# 1159/1424, 1188 (endo_heart, heart_heart)
mike_common_indices_0 <- intersect(cz_endo_heart_0, cz_heart_heart_0)

# 265 
mike_only_endo_0 <- setdiff(cz_endo_heart_0, cz_heart_heart_0)
# 29 
mike_only_heart_0 <- setdiff(cz_heart_heart_0, cz_endo_heart_0)
```

# Gene Lists.
```{r include=TRUE}
endo_khids_0 <- one2one_khid_list[mike_only_endo_0]
endo_human_df_0 <- khid_human_ortho_df[khid_human_ortho_df$Gene.ID %in% endo_khids_0, ]
endo_human_df
# Bra -> ETV1 (endo). I couldn't find bra here... timing thing? 

heart_khids_0 <- one2one_khid_list[mike_only_heart_0]
heart_human_df_0 <- khid_human_ortho_df[khid_human_ortho_df$Gene.ID %in% heart_khids_0, ]
heart_human_df_0

common_khids_0 <- one2one_khid_list[mike_common_indices_0]
common_human_df_0 <- khid_human_ortho_df[khid_human_ortho_df$Gene.ID %in% common_khids_0, ]
common_human_df_0
```
```{r include=TRUE}
# Filtered.
c_mesp = "KH2012:KH.C3.100"
c_mesp %in% mike_ciona_heart_degs_0

# Unfiltered: All but mespbab.
z_mesp = c("mespaa", "mespba", "mespbab", "mespbb", "msgn1")
z_mesp %in% mike_zeb_heart_degs_0
```
```{r include=TRUE}
FeaturePlot(zeb_integrated_50,
            features = z_mesp)
```
