---
title: "batch_larva_24hpf_brainmap"
output: html_document
---

# Uses Code from one2many_orthology_map_generator.Rmd
# Subsets zeb.avexp.df for Neural Zeb CTs.
# Uses Chen's brainmap CTs -> LTB2/larva Average Expression Vector.
# Rest of pipeline is used for visualization.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(Seurat)
library(dplyr)
library(ggplot2)
library(Matrix)
library(ggcorrplot)
library(psych)
library(stringr)
library(plotly)
```

"""

(1) Make Neural Ciona Average Expression Matrix (ciona.neural.avexp.df).
I need 2 data structures:

(a) ciona.neural.CT.list
(b) chen.cns.data

"""
## Make ciona.neural.cell.type.list.
# Get all the data (will subset) and metadata (to get all CTs and their cells).
```{r include=TRUE}
batch.chen.neural.cells <- CNS.Seurat.LTB2.lv@cell.names
chen.CNS.metadata <- CNS.Seurat.LTB2.lv@meta.data
```

# Get batch-corrected data matrix values
```{r include=TRUE}
batch.chen.neural.data <- batch.ciona.data[batch.chen.neural.cells, ]
```

```{r include=TRUE}
batch.common.neural.ciona <- intersect(colnames(batch.ciona.data), batch.chen.neural.cells)  
```

# TO DO

# Iterate through chen.CNS.CTs to make ciona.neural.CT.list.
```{r include=TRUE}
ciona.neural.CT.list <- list()

for (chen.CNS.CT in chen.CNS.CTs) {
  # Get dataframe relevant only to that CT. 
  filtered.neural.df <- chen.CNS.metadata %>% filter(newcluster.comb.del.anno == chen.CNS.CT)
  # Get CT's cells.
  CT.cells <- rownames(filtered.neural.df)
  # Update list.
  ciona.neural.CT.list[[chen.CNS.CT]] <- CT.cells
}
```



# Modified
```{r include=TRUE}
# 22 
mod.zeb.neural.CTs <- c(names(cell_type_list_2), names(mod.cell.type.list.3), "lens", "optic_cup", "rpe", "otic_plac", "tail_spinal_cord", "tail_PSM")

mod.zeb.neural.CT.list <- mod.zeb.cell.type.list[mod.zeb.neural.CTs]
```

# Get subset of Zeb Average Expression Matrix for only Zeb Neural CTs and
# update by removing zeb_genes that correspond to not.qualified.ciona.khids.
# Use: not.in.CNS.indices.

# Modified
```{r include=TRUE}
# 3134 x 25 
batch.mod.zeb.neural.gsm <- batch.mod.zeb.gsm[ ,mod.zeb.neural.CTs]
```

# TO DO #




# TO DO #
# Let's look at the entire similarity matrix. (Both)
# Make ciona.mod.zeb.gsm
```{r include=TRUE}
ciona.mod.zeb.gsm <- cbind(ciona.gsm, mod.zeb.gsm)
```

# TO DO #
# Modify the colnames to specify organism. 
```{r include=TRUE}
neural.ciona.colnames <- paste0("ciona_", colnames(ciona.gsm))
neural.zeb.colnames <- paste0("zeb_", colnames(mod.zeb.gsm))

colnames(neural.ciona.mod.zeb.gsm) <- c(neural.ciona.colnames, neural.zeb.colnames)
```


### Pipeline 1: Adjusted p_vals, Visualizes significant p_vals.
# Uses psych::corr.test
"""
(5.1) Use corr.test to make Correlation and P-Value Matrices.
"""

# Self-Self
```{r include=TRUE}
# batch.mod.zeb.neural.gsm
batch.neural.mod.corR.output <- corr.test(x= batch.mod.zeb.neural.gsm,
                         y = batch.mod.zeb.neural.gsm,
                         method = "spearman",
                         adjust = "fdr")
```

```{r include=TRUE}
batch.neural.mod.corR.mat <- batch.neural.mod.corR.output$r
batch.neural.mod.corR.pval.mat <- batch.neural.mod.corR.output$p 
```


# SPECIFY #
```{r include=TRUE}
# batch.neural.mod.corR.mat
# batch.neural.mod.corR.pval.mat

your.corR.mat <- batch.neural.mod.corR.mat
your.corR.pval.mat <- batch.neural.mod.corR.pval.mat
```
"""
(5.2) Visualize.
"""

# Parameters.
```{r include=TRUE}
# Corr legend range. 
# min(corR.mat)
min.index <- min(your.corR.mat)
# max(corR.mat)
max.index <- max(your.corR.mat)
leeway <- 0.01
limits <- c(min.index-leeway, max.index+leeway)

# Aesthetics and labels. 
your.title <- "Similarity Matrix for Zebrafish Neural Cell Types"
your.xlab <- "Ciona Larva"
your.ylab <- "Zeb 24hpf"
your.fill <- "Corr"
#4388F0, 42B5DD
your.color <- "#56B273"
your.face <- "bold"
```

```{r include=TRUE}
p <- ggcorrplot(corr = your.corR.mat,
           p.mat = your.corR.pval.mat)
```

```{r include=TRUE}
p + scale_fill_gradient2(limit = limits,
                          low = "#4C7CC4", mid = "white", high = "#BE1E0B") +
  
  ggplot2::labs(x = your.xlab, y = your.ylab, title = your.title, fill = your.fill) +
  
  ggplot2::theme(plot.title = element_text(size=16, color=your.color, face=your.face),
                 axis.text.x = element_text(angle=45, color="black", size=5),
                 axis.text.y = element_text(angle=45, color="black", size=5),
                 axis.title.x = element_text(angle = 0, color = your.color, face = your.face),
                 axis.title.y = element_text(angle = 0, color = your.color, face = your.face),
                 legend.title = element_text(color = your.color, size = 9),
                 legend.text = element_text(size = 9)
                 
  )
```
"""
(5.3) (a) Get # Significant Correlations. 
      (b) Get Significance between zeb_CT and ciona_CT
"""

# CHANGE zeb.gsm/mod.zeb.gsm #
```{r include=TRUE}
num.sig <- sum(your.corR.pval.mat < 0.05)
num.sig

num.CTs <- ncol(zeb.gsm)*ncol(zeb.gsm)
num.CTs
perc.sig <- num.sig/num.CTs*100
perc.sig
```

