---
title: "batch_one2many_orthology_map_generator"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(Seurat)
library(dplyr)
library(ggplot2)
library(Matrix)
library(ggcorrplot)
library(psych)
library(stringr)
library(plotly)
```

"""
Helper Function to make Gene Specificity Matrix (Tosches)
"""
```{r include=TRUE}
make_gene_specificity_matrix <- function(average_expression_matrix) {
  # Given an average expression matrix, convert to a gene specificity matrix (Tosches)
  # Args:
  #   average_expression_matrix: 
  #       e.g. ciona_average_expression_matrix <- cbind(ciona_df_1, ciona_df_2)
  #
  # Routine:
  #     g_c/(1/N)sum(i in C)g_i
  #
  # Returns:
  #   gsm: Output of above routine.
  gsm_1 <- average_expression_matrix
  # makes new column with  mean of the row (average expression of gene across all cell types)
  gsm_1 <- gsm_1 %>% mutate(gene_CTs_avexp = rowMeans(.))
  num_cell_types <- ncol(gsm_1)-1
  gsm <- gsm_1[, 1:num_cell_types]/gsm_1[, num_cell_types+1]
  
  return(gsm)
}
```

##### Batch-corrected data from ciona_larva_batch_integrated and finished_zeb_seurat #####
```{r include=TRUE}
# 13472 x 47782
batch.ciona.data <- readRDS("/home/pprakriti/Desktop/batch_correction/ciona/gencomp_ciona_batch_correct_dir/gencomp_ciona_batch_data.rds")
# 24232 x 34750
batch.zeb.data <- readRDS("/home/pprakriti/Desktop/batch_correction/zeb/gencomp_zeb_batch_correct_dir/gencomp_zeb_batch_data.rds")
```

```{r include=TRUE}
batch.ciona.CT.list <- ciona_cell_type_list
batch.zeb.CT.list <- mod.zeb.cell.type.list
```

##### Part 1: Make Heatmaps! #####

# Read in "one2one_many_dict.csv"
```{r include=TRUE}
export.qualified.batch.ortho.dict.csv <- "/home/pprakriti/Desktop/finish_gencom_zeb_seurat/munging/export_qualified_batch_ortho_dict.csv"
# 3078
qualified.batch.ortho.dict <- read.table(export.qualified.batch.ortho.dict.csv,
                                         sep = ",",
                                         header = FALSE,
                                         stringsAsFactors = FALSE)
```

# qualified.batch.ortho.dict df -> batch.one2one.many.list = {khid : ['aimp1a' 'aimp1b']} 
# Note: All lists are of length 1.
```{r include=TRUE}
# ??
batch.one2one.many.list <- list()
num.khids <- dim(qualified.batch.ortho.dict)[1]

for (i in 1:num.khids) {
  khid <- qualified.batch.ortho.dict$V1[i]
  
  zeb.genes <- qualified.batch.ortho.dict$V2[i]
  zeb.genes <- strsplit(zeb.genes, " ")
  batch.one2one.many.list[[khid]] <- zeb.genes
}
```

# Ciona genes of interest- length of column should be the number of these genes.
```{r include=TRUE}
# 3078
batch.qualified.ciona.khids <- names(batch.one2one.many.list)
```



```{r}

ortho <- tibble(zebgene = c("zebgene1", "zebgene2", "zebgene3"), ciogene = c("ciogene1,ciogene2", "ciogene3", "ciogene4,ciogene5,ciogene"))

ortho <- ortho %>%
   separate_rows(ciogene, sep = ",")



zebra <- data.frame(zebgene = c("zebgene1", "zebgene2", "zebgene3", "zebgene4", "zebgene5"), cell1 = c(0,2,3,4,5), cell2 = c(4,2,6,4,3))
ciona <- data.frame(ciogene = c("ciogene1", "ciogene2", "ciogene3", "ciogene4", "ciogene5"), cell1 = c(2,3,4,5,6), cell2 = c(1,1,1,4,3))

zebra
ortho
ciona
 
zebra %>%
  left_join(ortho) %>%
  inner_join(ciona, by = "ciogene", suffix = c("_zeb", "_cio"))

ciona %>%
  left_join(ortho) %>%
    group_by(zebgene) %>%
        summarize(
                  sumcell1= sum(cell1), 
                  sumcell2 = sum(cell2))


zebgeneciona <- ciona %>%
  left_join(ortho) %>%
    select(-ciogene) %>%
    group_by(zebgene) %>%
        summarize_at(vars(cell1:cell2), sum)


zebgeneciona %>%
  full_join(zebra, by = "zebgene", suffix = c("_cio", "_zeb")) -> tbl


cor(tbl, method = "spearman")


#cell1,cell2,0.34
#cell1,cell3,0.9
#cell2,cell3,0.1


#cell1,noto
#cell2,eyeball


#cell1,cell2,0.34,noto,eyeball
#cell1,cell3,0.9,noto,noto
#cell2,cell3,0.1,noto,noto



qualified.batch.ortho.dict %>%
  
batch.ciona.data 




```

<!-- # Make precursory Average Expression Matrix (ciona.df). -->
<!-- ```{r include=TRUE} -->
<!-- # Each row of a column should be a gene name.  -->
<!-- batch.ciona.dummy.col <- rep(0, length(batch.qualified.ciona.khids)) -->
<!-- batch.ciona.df <- data.frame("batch.ciona.dummy" = batch.ciona.dummy.col) -->
<!-- ``` -->

<!-- # Make Ciona Average Expression Matrix. -->
<!-- ```{r include=TRUE} -->
<!-- # For each Ciona CT -->
<!-- for (i in 1:length(batch.ciona.CT.list)) { -->
<!--   # Get its name.  -->
<!--   batch.ciona.CT <- names(batch.ciona.CT.list)[i] -->
<!--   cat("ciona CT = ", batch.ciona.CT, "\n\n") -->

<!--   # All of its cells. -->
<!--   batch.ciona.cells <- batch.ciona.CT.list[[i]] -->

<!--   # Subset the matrix based on cells.  -->
<!--   batch.ciona.data.pre <- batch.ciona.data[batch.qualified.ciona.khids, batch.ciona.cells] -->
<!--   batch.ciona.data.df <- as.data.frame(batch.ciona.data.pre) -->

<!--   # Get the average expression of each qualified.ciona.khid for the CT. -->
<!--   batch.ciona.row <- rowMeans(batch.ciona.data.df) -->
<!--   # Add to ciona.df. In the end, you should have 7 cols, each for a CT. -->
<!--   batch.ciona.df <- cbind(batch.ciona.df, batch.ciona.row) -->
<!-- } -->
<!-- # Get rid of the dummy column. -->
<!-- batch.ciona.df <- subset(batch.ciona.df, select = -(batch.ciona.dummy)) -->
<!-- ``` -->

<!-- ```{r include=TRUE} -->
<!-- # Each column is a CT. -->
<!-- batch.ciona.colnames <- names(batch.ciona.CT.list) -->
<!-- colnames(batch.ciona.df) <- batch.ciona.colnames -->
<!-- ``` -->

# Ciona Average Expression Matrix.
```{r include=TRUE}
batch.ciona.avexp.df <- batch.ciona.df
```

############### START DO NOT TOUCH!!!! #################
################# MODIFIED ZEB CTs ###################

<!-- # Let us now make zeb.df.  -->
<!-- # num_col = # CTs (43); num_rows = # of qualified.ciona.khids. -->
<!-- ```{r include=TRUE} -->
<!-- # length(zeb_cell_type_list)- keep below -->
<!-- batch.mod.num.zeb.df.cols <- length(mod.zeb.cell.type.list) -->
<!-- # Because this is the number of Ciona khids. -->
<!-- batch.mod.num.zeb.df.rows <- length(batch.qualified.ciona.khids) -->
<!-- # 3134 x 39 -->
<!-- batch.mod.zeb.df <- data.frame(matrix(, nrow=batch.mod.num.zeb.df.rows, ncol=batch.mod.num.zeb.df.cols)) -->
<!-- ``` -->

<!-- # Get colnames that correspond to various Zeb CTs. -->
<!-- ```{r include=TRUE} -->
<!-- batch.mod.zeb.df.colnames <- names(mod.zeb.cell.type.list) -->
<!-- colnames(batch.mod.zeb.df) <- batch.mod.zeb.df.colnames -->
<!-- ``` -->

<!-- # Get rownames that represent mapping. -->
<!-- ```{r include=TRUE} -->
<!-- # I discovered that there were 2 zeb_genes (ube2c_2 and rpl37_2) that mapped to 2 different khids that were  -->
<!-- # labeled as 1-1. Their names are munged here. -->
<!-- batch.mod.zeb.df.rownames <- c() -->
<!-- # seen.zeb.rownames <- c() -->

<!-- for (i in 1:length(batch.one2one.many.list)) { -->
<!--   khid <- names(batch.one2one.many.list)[i] -->
<!--   cat("khid = ", khid, "\n\n") -->

<!--   batch.mod.zeb.names <- batch.one2one.many.list[[i]][[1]] -->
<!--   # cat(zeb.names, "\n\n") -->

<!--   batch.mod.zeb.name.string <- paste(batch.mod.zeb.names, collapse = "_") -->
<!--   # cat("zeb name string = ", zeb.name.string, "\n\n") -->

<!--   if (batch.mod.zeb.name.string %in% batch.mod.zeb.df.rownames) { -->
<!--     # cat("PROBLEM zeb name string = ", zeb.name.string, "\n\n") -->

<!--     # Add _2 to seen.zeb.rownames to avoid redundant rowname conflicts.  -->
<!--     batch.mod.zeb.name.string <- paste(batch.mod.zeb.name.string, "2", sep = "_") -->
<!--     # seen.zeb.rownames <- c(seen.zeb.rownames, zeb.name.string) -->

<!--   } -->
<!--   batch.mod.zeb.df.rownames <- c(batch.mod.zeb.df.rownames, batch.mod.zeb.name.string) -->
<!-- } -->

<!-- # Modify zeb.df with these rownames.  -->
<!-- rownames(batch.mod.zeb.df) <- batch.mod.zeb.df.rownames -->
<!-- ``` -->

<!-- # Make average expression dataframe. -->
<!-- ```{r include=TRUE} -->
<!-- # For each Zeb CT -->
<!-- for (i in 1:length(mod.zeb.cell.type.list)) { -->
<!--   batch.mod.zeb.CT.name <- names(mod.zeb.cell.type.list)[i] -->
<!--   # Get its cells.  -->
<!--   batch.mod.zeb.cells <- mod.zeb.cell.type.list[[i]] -->
<!--   batch.mod.zeb.length <- length(batch.mod.zeb.cells) -->
<!--   cat("Zeb CT = ", batch.mod.zeb.CT.name, "\n", batch.mod.zeb.length) -->

<!--   # Get 1-1/1-many zeb genes. -->
<!--   for (j in 1:length(batch.one2one.many.list)) { -->
<!--     cat("i = ", i, "j = ", j, "\n\n") -->
<!--     batch.mod.one.many.zeb.genes <- batch.one2one.many.list[[j]][[1]] -->

<!--     # Subset Zeb Data based on these genes. -->
<!--     batch.mod.zeb.sub <- batch.zeb.data[batch.mod.one.many.zeb.genes, batch.mod.zeb.cells] -->

<!--     # Get Average Expression. -->
<!--     batch.mod.zeb.av <- sum(batch.mod.zeb.sub)/batch.mod.zeb.length -->
<!--     # Add to correct entry.  -->
<!--     batch.mod.zeb.df[j, i] <- batch.mod.zeb.av -->
<!--   } -->
<!-- } -->
<!-- ``` -->

<!-- # Zeb Average Expression Matrix -->
<!-- ```{r include=TRUE} -->
<!-- batch.mod.zeb.avexp.df <- batch.mod.zeb.df -->
<!-- ``` -->

############### END DO NOT TOUCH!!!! #################
################# MODIFIED ZEB CTs ###################


"""
(4) Make the GSM Dataframes, ciona/zeb_gsm_v4
"""
```{r include=FALSE}
batch.ciona.gsm <- make_gene_specificity_matrix(batch.ciona.avexp.df)
rownames(batch.ciona.gsm) <- rownames(batch.ciona.avexp.df)
```

# Modified
```{r include=TRUE}
batch.mod.zeb.gsm <- make_gene_specificity_matrix(batch.mod.zeb.avexp.df)
rownames(batch.mod.zeb.gsm) <- rownames(batch.mod.zeb.avexp.df)
```

# Both: Problem is that there are 2 notos! 
```{r include=TRUE}
batch.ciona.mod.zeb.gsm <- cbind(batch.ciona.gsm, batch.mod.zeb.gsm)
batch.cmz.colnames <- colnames(batch.ciona.mod.zeb.gsm)

batch.cmz.replace <- c(paste("ciona_", (batch.cmz.colnames[1:7])), "zeb_noto", batch.cmz.colnames[9:length(batch.cmz.colnames)])

colnames(batch.ciona.mod.zeb.gsm) <- batch.cmz.replace
```

#### QUESTION WHAT IS THIS ####

# THIS IS SO VERY HACKY- BECAUSE THERE'S AN OVERLAP IN VARIABLE NAME WITH BRAINMAP #
```{r include=TRUE}
batch.CT.ciona.mod.zeb.gsm <- batch.ciona.mod.zeb.gsm
```

### Pipeline 1: Adjusted p_vals, Visualizes significant p_vals.
# Uses psych::corr.test

"""
(5.1) Use corr.test to make Correlation and P-Value Matrices.
"""

# Mod
# CHANGE THESE batch.ciona.gsm, batch.mod.zeb.gsm
```{r include=TRUE}
# batch.ciona.gsm
# batch.mod.zeb.gsm
batch.mod.corR.output <- corr.test(x= batch.ciona.gsm,
                                   y = batch.ciona.gsm
                                   ,
                                   method = "spearman",
                                   adjust = "fdr")
```

# Mod 
```{r include=TRUE}
batch.mod.corR.mat <- batch.mod.corR.output$r
batch.mod.corR.pval.mat <- batch.mod.corR.output$p 
```

# Both
```{r include=TRUE}
batch.CT.ciona.mod.zeb.corR.output <- corr.test(x= batch.CT.ciona.mod.zeb.gsm,
                         y = batch.CT.ciona.mod.zeb.gsm,
                         method = "spearman",
                         adjust = "fdr")
```

# Both
```{r include=TRUE}
batch.CT.ciona.mod.zeb.corR.mat <- batch.CT.ciona.mod.zeb.corR.output$r
batch.CT.ciona.mod.zeb.corR.pval.mat <- batch.CT.ciona.mod.zeb.corR.output$p 
```

"""
(5.2) Visualize.
"""
# SPECIFY #
```{r include=TRUE}
batch.your.corR.mat <- batch.CT.ciona.mod.zeb.corR.mat
batch.your.corR.pval.mat <- batch.CT.ciona.mod.zeb.corR.pval.mat
```

# Parameters.
```{r include=TRUE}
# Corr legend range. 
# min(corR.mat)
# Zeb 24hpf
# Ciona

min.index <- min(batch.your.corR.mat)
# max(corR.mat)
max.index <- max(batch.your.corR.mat)
leeway <- 0.01
limits <- c(min.index-leeway, max.index+leeway)

# Aesthetics and labels. 
your.title <- "Batch-Corrected Similarity Matrix of Zeb 24hpf and Ciona CTs"
your.xlab <- "Ciona"
your.ylab <- "Zeb 24hpf"
your.fill <- "Corr"
#4388F0, 42B5DD
your.color <- "#56B273"
your.face <- "bold"
```

```{r include=TRUE}
p <- ggcorrplot(corr = batch.your.corR.mat,
           p.mat = batch.your.corR.pval.mat)
```

```{r include=TRUE}
# angle=45, 90/0

p + scale_fill_gradient2(limit = limits,
                          low = "#4C7CC4", mid = "white", high = "#BE1E0B") +
  
  ggplot2::labs(x = your.xlab, y = your.ylab, title = your.title, fill = your.fill) +
  
  ggplot2::theme(plot.title = element_text(size = 10, color = your.color, face = your.face),
                 axis.title.x = element_text(angle = 0, color = your.color, face = your.face),
                 axis.title.y = element_text(angle = 90, color = your.color, face = your.face),
                 axis.text.x = element_text(angle=45, color="black", size=10),
                 axis.text.y = element_text(angle=45, color="black", size=10),
                 legend.title = element_text(color = your.color, size = 9),
                 legend.text = element_text(size = 9)
  )
```


"""
(5.3) (a) Get # Significant Correlations. 
      (b) Get Significance between zeb_CT and ciona_CT
"""

```{r include=TRUE}
num.sig <- sum(batch.your.corR.pval.mat < 0.05)
num.sig

# batch.mod.zeb.gsm
num.CTs <- ncol(batch.mod.zeb.gsm)*ncol(batch.mod.zeb.gsm)
num.CTs
perc.sig <- num.sig/num.CTs*100
perc.sig
```
# Question: How do correcltions change if I vary the number of Optic Cup cells?
```{r include=TRUE}
# Get distribution of num_cells for Zeb CTs. 
```

# Distribution of Cells 
```{r include=TRUE}
mod.zeb.neural.CT.nums <- sapply(mod.zeb.neural.CT.list, length)
hist(mod.zeb.neural.CT.nums, freq = FALSE, breaks = 10)
mean(mod.zeb.neural.CT.nums)
```


















###################### UNUSED ####################

# Only heart_52 is f*** up. 
# So I'm just going to do the hacky thing of calculating it separately
# and then modifying zeb.avexp.df 

####################### START FIX HEART 52! ######################

```{r include=TRUE}
fixed.heart.zeb.df.dummy.col <- rep(0, length(qualified.ciona.khids))
fixed.heart.zeb.df <- data.frame("heart_52" = fixed.heart.zeb.df.dummy.col)

fixed.heart.zeb.cells <- zeb_cell_type_list$heart_52
fixed.heart.length <- length(fixed.heart.zeb.cells)

# For each KHID
for (j in 1:length(batch.one2one.many.list)) {
  cat("i = ", i, "j = ", j, "\n\n")

# Get its zeb orthologs. 
  fixed.heart.one.many.zeb.genes <- batch.one2one.many.list[[j]][[1]]

# Subset Zeb Data based on these zeb orthologs.
fixed.heart.zeb.sub <- zeb_data[fixed.heart.one.many.zeb.genes, fixed.heart.zeb.cells]
# Get Average Expression.
fixed.heart.zeb.av <- sum(fixed.heart.zeb.sub)/fixed.heart.length
# Add to correct entry. 
fixed.heart.zeb.df[j, 1] <- fixed.heart.zeb.av
}
```

# Get the Average Expression values for heart_52 (fixed.heart.zeb.column)
```{r include=TRUE}
# Correct! 
fixed.heart.zeb.df
# We want its values.
fixed.heart.zeb.column <- fixed.heart.zeb.df$heart_52
```

# Replace heart_52 column in zeb.avexp.df
```{r include=TRUE}
zeb.avexp.df$heart_52 <- fixed.heart.zeb.column
```

####################### END FIX HEART 52! ######################
