---
title: "validate_get_geneset_v4"
output: html_document
---

# Follows from/Works in parallel with "get_geneset_v4.Rmd"/"get_geneset_troubleshooting.Rmd"

# Note: It was initially created to validate its pipeline against 25 genes.
#       Discovered that the resultant heatmap was really great.
#       Implemented 7/23/20.

# General Description and Notes below:

# Specify gene lists (zeb_genes, khid_list) and
# CT lists (ciona_cell_type_list, zeb_cell_type_list_v4)
# to get data matrices.

# CAUTION!
# (1) ciona_cell_type_list consists of cells from clusters in larva stage.
# (2) zeb_cell_type_list consists of cells from clusters in zeb 24hpf.
# (3) zeb_cell_type_list_v4 is something you specify! It is a subset of zeb_cell_type_list.
#     It currently consists of the same 16 CTs used in "get_geneset_troubleshooting.Rmd".

# Gene Lists:
# (1) Unique unfiltered 1-1 orthologs (2592)
# one2one_ciona_khids, one2one_zeb_genes

# (2) 25 genes (from "get_geneset_troubleshooting.Rmd)
# final_khids, final_zeb_genes

# Note:
# Zeb 16 CTs: (1st heatmaps using v4: 25, 2592)
# noto, heart_52, heart_51_56, muscles, epi_1, epi_2, panc_prim_endo, meso, pec_fin_bud, ph_arch_ndnf, iono, leuko, lens, optic_cup, diff_neus, nc_grem2

# Zeb 12 CTs: (To make pairwise DEGs)
# pec_fin_bud, panc_prim, noto, muscles, meso, leuko, diff_neus, epi_1, _2, heart_51_56, _52, tail_spinal_cord 

# TO DO:: Segways into: 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(Seurat)
library(dplyr)
library(ggplot2)
```

# Gene List
```{r include=TRUE}
one_one_dir = "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/get_geneset_attempts/v3/one_to_one_khid_zeb_gene_dict.csv" 

one_one_df <- read.table(one_one_dir,
                         sep = ",",
                         header = FALSE,
                         stringsAsFactors = FALSE)

one2one_khid_list = one_one_df$V1
one2one_zeb_genes = one_one_df$V2
```

"""
Helper Function to make Gene Specificity Matrix (Tosches)
"""
```{r include=TRUE}
make_gene_specificity_matrix <- function(average_expression_matrix) {
  # Given an average expression matrix, convert to a gene specificity matrix (Tosches)
  # Args:
  #   average_expression_matrix: 
  #       e.g. ciona_average_expression_matrix <- cbind(ciona_df_1, ciona_df_2)
  #
  # Routine:
  #     g_c/(1/N)sum(i in C)g_i
  #
  # Returns:
  #   gsm: Output of above routine.
  gsm_1 <- average_expression_matrix
  # makes new column with  mean of the row (average expression of gene across all cell types)
  gsm_1 <- gsm_1 %>% mutate(gene_CTs_avexp = rowMeans(.))
  num_cell_types <- ncol(gsm_1)-1
  gsm <- gsm_1[, 1:num_cell_types]/gsm_1[, num_cell_types+1]
  
  return(gsm)
}
```

```{r include=TRUE}
'%notin%' <- Negate('%in%')
```

"""""""""""""""""""""""""""""""
Workflow
These are already 1-1 orthologs.

final_khids/final_zeb_genes (25)
one2one2_khid_list/one2one2_zeb_genes (2592)

"""""""""""""""""""""""""""""""

# Input gene lists. 
```{r include=TRUE}
khid_list <- final_khids
zeb_genes <- final_zeb_genes
```

# Get all unfiltered genes in Zeb and Ciona. 
# These are genes that can even be considered for downstream analyses. 
```{r include=TRUE}
# 30677 x 34750
zeb_data <- zeb_integrated_50[["RNA"]]@data
# zeb_data <- GetAssayData(zeb_integrated_50, slot="data") only for VariableFeatures.

zeb_rownames <- rownames(zeb_data)
common_zeb_genes <- intersect(zeb_rownames, zeb_genes)

# 14433 x 12005
ciona_data <- clean_chen_larva_integrated_20[["RNA"]]@data

ciona_rownames <- rownames(ciona_data)
common_ciona_khids <- intersect(ciona_rownames, khid_list)
```

# Get indices of input zeb genes that are not filtered.
# Zeb 
```{r include=TRUE}
# For each input gene, check that it is unflitered.
qualified_zeb_indices <- which(zeb_genes %in% zeb_rownames)

# Check if any genes showed up twice in your input gene list.
dup_zeb_genes <- duplicated(zeb_genes)
dup_zeb_indices <- which(dup_zeb_genes == TRUE)
# Genes at dup_zeb_indices will have showed up multiple times in input gene list.
validate_dup_zeb_genes <- zeb_genes[dup_zeb_indices]

# These are the indices of input genes that are unfiltered.
qualified_zeb_indices <- qualified_zeb_indices[qualified_zeb_indices %notin% dup_zeb_indices]
```

# Ciona 
```{r include=TRUE}
qualified_ciona_indices <- which(khid_list %in% ciona_rownames)

dup_ciona_genes <- duplicated(khid_list)
dup_ciona_indices <- which(dup_ciona_genes == TRUE)
validate_dup_ciona_genes <- khid_list[dup_ciona_indices]

qualified_ciona_indices <- qualified_ciona_indices[qualified_ciona_indices %notin% dup_ciona_indices]
```

# Which indices are in common?
```{r include=TRUE}
common_indices <- intersect(qualified_zeb_indices, qualified_ciona_indices)
```

# Get qualified genes.
```{r include=TRUE}
qualified_zeb_genes <- zeb_genes[common_indices]
qualified_ciona_khids <- khid_list[common_indices]
```

"""
Ciona: Make Average Expression Dataframes for Ciona CTs (7).
ciona_avexp_df_v4 = ciona_df
"""

## Speficy ciona_cell_type_list ##
```{r include=TRUE}
ciona_dummy_col <- rep(0, length(qualified_ciona_khids))
ciona_df <- data.frame(ciona_dummy=ciona_dummy_col)

for (i in 1:length(ciona_cell_type_list)) {
  cat("i = ", i, "\n")
  ciona_cells <- ciona_cell_type_list[[i]]
  # Get gene exp values for all cells in a CT.
  ciona_data_pre <- ciona_data[qualified_ciona_khids, ciona_cells]
  ciona_data_df <- as.data.frame(ciona_data_pre)
  # Get av exp for each gene for all CTs.
  ciona_row <- rowMeans(ciona_data_df)
  ciona_df <- cbind(ciona_df, ciona_row)
}

# Remove ciona_dummy column.
ciona_df <- subset(ciona_df, select=-(ciona_dummy))

ciona_colnames <- names(ciona_cell_type_list)
colnames(ciona_df) <- ciona_colnames

# The Average Expression Dataframe 
ciona_avexp_df_v4 <- ciona_df
```

"""
Zeb: Make Average Expression Dataframes for Zeb CTs (12/16).
zeb_avexp_df_v4 = zeb_df

These are the same CTs used in Module v3 in "get_geneset_troubleshooting.Rmd"
"""

## Specify zeb_cell_type_list_v4 ##
```{r include=TRUE}
zeb_cell_type_list_v4 <- zeb_CT_12
```
                             
```{r include=TRUE}
zeb_dummy_col <- rep(0, length(qualified_zeb_genes))
zeb_df <- data.frame(zeb_dummy=zeb_dummy_col)

####

for (i in 1:length(zeb_cell_type_list_v4)) {
  cat("i = ", i, "\n")
  zeb_cells <- zeb_cell_type_list_v4[[i]]
  # Get gene exp values for all cells in a CT.
  zeb_data_pre <- zeb_data[qualified_zeb_genes, zeb_cells]
  zeb_data_df <- as.data.frame(zeb_data_pre)
  # Get av exp for each gene for all CTs.
  zeb_row <- rowMeans(zeb_data_df)
  zeb_df <- cbind(zeb_df, zeb_row)
}

# Remove ciona_dummy column.
zeb_df <- subset(zeb_df, select=-(zeb_dummy))

zeb_colnames <- names(zeb_cell_type_list_v4)
colnames(zeb_df) <- zeb_colnames

# The Average Expression Dataframe
zeb_avexp_df_v4 <- zeb_df
```

"""
Make the GSM Dataframes, Cor Df 
"""
```{r include=FALSE}
ciona_gsm_v4 <- make_gene_specificity_matrix(ciona_avexp_df_v4)
zeb_gsm_v4 <- make_gene_specificity_matrix(zeb_avexp_df_v4)

cor_df_v4 <- make_cor_df(ciona_gsm_v4, zeb_gsm_v4)
```

```{r include=TRUE}
cor_df_v4 <- cor_df_v4 %>% transform(cor = as.numeric(cor))
```

# Visualize
```{r include=TRUE}
# "RdYlBu", "PiYG"
cor_df_v4_heatmap <- ggplot(data = cor_df_v4,
                         aes(x=ciona_CTs, y=zeb_CTs, fill=cor)) +
                         geom_tile() +
                         scale_fill_distiller(palette = "RdBu")
              

cor_df_v4_heatmap
```

### ZEB CT LISTS ###

```{r include=TRUE}
zeb_CT_16 <- list(noto = noto,
                             heart_52 = heart_52,
                             heart_51_56 = heart_51_56,
                             muscles = muscles,
                             epi_1 = epi_1,
                             epi_2 = epi_2,
                             panc_prim_endo = panc_prim_endo,
                             meso = meso,
                             pec_fin_bud = pec_fin_bud,
                             ph_arch_ndnf = ph_arch_ndnf,
                             iono = iono,
                             leuko = leuko,
                             lens = lens,
                             optic_cup = optic_cup,
                             diff_neus = diff_neus,
                             nc_grem2 = nc_grem2)

zeb_CT_12 <- list(noto = noto,
                             heart_52 = heart_52,
                             heart_51_56 = heart_51_56,
                             muscles = muscles,
                             epi_1 = epi_1,
                             epi_2 = epi_2,
                             panc_prim_endo = panc_prim_endo,
                             meso = meso,
                             pec_fin_bud = pec_fin_bud,
                             leuko = leuko,
                             diff_neus = diff_neus,
                             tail_spinal_cord = tail_spinal_cord)
```



