---
title: "get_pairwise_zeb_ciona_degs"
output: html_document

---
# Follows from: ciona_larvae_clustering.Rmd and zeb_degs_heatmaps.Rmd.
# Note: Uses the ClusterIDs and cell names from above scripts. 

# Works in parallel with: None.

# General Description: Script implements various methods to get gene set
# to be used for downstream cross-species cell type comparisons. 

# Uses env_get_pairwise_zeb_ciona_degs.RData

## Module v1: Tosches 
# (1) Generates unique_ciona_deg_vec (444) and unique_zeb_deg_vec (1372) from supersets of top50 pairwise DEGs (Tosches Method).
# (2) These vectors are manipulated in "get_one_to_one_gene_lists.py" to make
#     unique_ciona_KHID_vec and zeb_ortho_gene_vec
# (3) Expression patterns are visualized in Ciona tissues
#     and Zeb notochord.
# (4) First exploratory analyses of 10/top50 Ciona notochord DEGs are performed. 

# TO DO Segways into 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(Seurat)
library(dplyr)
library(ggplot2)
library(purrr)
library(Hmisc)
library(pvclust)
```

"""
v1 Module Start
"""

"""
Let's get all pairwise-cluster DEGs in Ciona (444)
"""

```{r include=TRUE}
ciona_cell_type_list <- list(endo = ciona_larva_endo,
                             epi = ciona_larva_epi,
                             mes = ciona_larva_mes,
                             mus = ciona_larva_mus,
                             heart = ciona_larva_heart,
                             cns = ciona_larva_cns,
                             noto = ciona_larva_noto)
```

```{r include=TRUE}
test_ciona_cell_type_list <- list(mes = ciona_larva_mes,
                                  mus = ciona_larva_mus,
                                  noto = ciona_larva_noto)
```

# Do routine.
# Test Case passed.
# Thus, set test_ciona_cell_type_list to ciona_cell_type_list.
```{r include=TRUE}
# ~10 mins
# 444
test_ciona_deg_vec <- c()

test_ciona_cell_type_list <- ciona_cell_type_list

for (i in 1:length(test_ciona_cell_type_list)) {
  for (j in 1:length(test_ciona_cell_type_list)) {
    if (i != j) {
      cat("i = ", i, "j = ", j, "\n\n")
      cell_type_marker_df <- FindMarkers(object = clean_chen_larva_integrated_20,
                                     ident.1 = test_ciona_cell_type_list[[i]],
                                     ident.2 = test_ciona_cell_type_list[[j]],
                                     test.use = "MAST")
      
      munged_cell_type_marker_df <- munge_markers(cell_type_marker_df)[1:50, ]
      munged_cell_type_markers <- rownames(munged_cell_type_marker_df)
      
      test_ciona_deg_vec <- c(test_ciona_deg_vec, munged_cell_type_markers)
    }
  }
}

unique_test_ciona_deg_vec <- unique(test_ciona_deg_vec)

# Rename above
# 444
unique_ciona_deg_vec <- unique_test_ciona_deg_vec
```
"""
Let's get all pairwise-cluster DEGs in Zebrafish
"""

```{r include=TRUE}
# 43 cell types 
zeb_cell_type_list <- do.call(c, list(cell_type_list_1,
                                      cell_type_list_2,
                                      cell_type_list_3,
                                      cell_type_list_4))
```


```{r include=TRUE}
# 3 h
# 1372 
zeb_deg_vec <- c()

for (i in 1:length(zeb_cell_type_list)) {
  for (j in 1:length(zeb_cell_type_list)) {
    if (i != j) {
      cat("i = ", i, "j = ", j, "\n\n")
      cell_type_marker_df <- FindMarkers(object = zeb_integrated_50,
                                     ident.1 = zeb_cell_type_list[[i]],
                                     ident.2 = zeb_cell_type_list[[j]],
                                     test.use = "MAST")
      
      munged_cell_type_marker_df <- munge_markers(cell_type_marker_df)[1:50, ]
      munged_cell_type_markers <- rownames(munged_cell_type_marker_df)
      
      zeb_deg_vec <- c(zeb_deg_vec, munged_cell_type_markers)
    }
  }
}

unique_zeb_deg_vec <- unique(zeb_deg_vec)
```

"""
Export these DEGs
"""

```{r include=TRUE}
write.csv(x = unique_zeb_deg_vec,
          file = "unique_zeb_deg_vec.csv",
          row.names = FALSE)

write.csv(x = unique_ciona_deg_vec,
          file = "unique_ciona_deg_vec.csv",
          row.names = FALSE)
```

"""
What do the profiles of the 30 1-1 DEGs look like?
"""

```{r include=TRUE}
ciona_ortho_KHID_vec <- c('KH2012:KH.C3.724', 'KH2012:KH.L107.7', 'KH2012:KH.C5.302', 'KH2012:KH.C1.1067', 'KH2012:KH.C7.633', 'KH2012:KH.C11.2')
```

```{r include=TRUE}
DoHeatmap(object = clean_chen_larva_integrated_20,
          features = ciona_ortho_KHID_vec,
          cells = ciona_larva_endo,
          slot = "data",
          size = 2)
```
```{r include=TRUE}
DoHeatmap(object = clean_chen_larva_integrated_20,
          features = ciona_ortho_KHID_vec,
          cells = ciona_larva_epi,
          slot = "data",
          size = 2)
```

```{r include=TRUE}
DoHeatmap(object = clean_chen_larva_integrated_20,
          features = ciona_ortho_KHID_vec,
          cells = ciona_larva_mes,
          slot = "data",
          size = 2)
```

```{r include=TRUE}
DoHeatmap(object = clean_chen_larva_integrated_20,
          features = ciona_ortho_KHID_vec,
          cells = ciona_larva_mus,
          slot = "data",
          size = 2)
```

```{r include=TRUE}
DoHeatmap(object = clean_chen_larva_integrated_20,
          features = ciona_ortho_KHID_vec,
          cells = ciona_larva_heart,
          slot = "data",
          size = 2)
```

```{r include=TRUE}
DoHeatmap(object = clean_chen_larva_integrated_20,
          features = ciona_ortho_KHID_vec,
          cells = ciona_larva_cns,
          slot = "data",
          size = 2)
```


"""
Notochords?
"""

# Ciona
```{r include=TRUE}
DoHeatmap(object = clean_chen_larva_integrated_20,
          features = ciona_ortho_KHID_vec,
          cells = ciona_larva_noto,
          slot = "data",
          size = 2)
```

```{r include=TRUE}
zeb_ortho_gene_vec <- c('tgfb3', 'lhx5', 'blvrb', 'hpca', 'col1a2', 'crip1')
```

# Zeb
```{r include=TRUE}
DoHeatmap(object = zeb_integrated_50,
          features = zeb_ortho_gene_vec,
          cells = noto,
          slot = "data",
          size = 2)
```

"""
Comparative Mona Analysis of Noto Top50 DEGs
"""

"""
Ciona
"""
# (Ciona) Get top50 DEGs 
```{r include=TRUE}
ciona_noto_top50_markers <- get_top_n_df(ciona_larva_noto, clean_chen_larva_integrated_20, "MAST", 50)

write.csv(rownames(ciona_noto_top50_markers), "ciona_noto_top50_markers.csv", row.names = FALSE)
```

# (Ciona) List of 1-1 orthologs
```{r include=TRUE}
ciona_ortho_KHID_vec <- c("KH2012:KH.C3.724", "KH2012:KH.L107.7", "KH2012:KH.C5.302", "KH2012:KH.C1.1067", "KH2012:KH.C7.633", "KH2012:KH.C11.2")
```

# Exploratory Questions
# (Ciona) Are any of these in top50 DEGs for Ciona Noto?
```{r include=TRUE}
# Yes!!

if (any(ciona_ortho_KHID_vec %in% rownames(ciona_noto_top50_markers))) {
  print(ciona_ortho_KHID_vec[ciona_ortho_KHID_vec %in% rownames(ciona_noto_top50_markers)])
} 

# KH2012:KH.C3.724, COL1A1/2

# KH2012:KH.C7.633, COL1A1/2
```

# (Ciona) What are the first 10 markers?
```{r include=TRUE}
# From code, from Christelle Best Human Hits

ciona_noto_top10_markers <- rownames(ciona_noto_top50_markers)[1:10]
# KH2012:KH.S423.2, FIBCD1, TNR, TNXB
ciona_noto_top10_markers[1]
# noto8! KH2012:KH.C11.737, CALM1, CALM3, CALML3
ciona_noto_top10_markers[2]
# KH2012:KH.C13.35, CNMD, TNMD
ciona_noto_top10_markers[3]
# KH2012:KH.C8.749, None 
ciona_noto_top10_markers[4]
# KH2012:KH.C10.8, FAT4, PROS1, SVEP1
ciona_noto_top10_markers[5]
# KH2012:KH.C9.174, None 
ciona_noto_top10_markers[6]
# KH2012:KH.C9.698, GPX4/7/8
ciona_noto_top10_markers[7]
# KH2012:KH.L18.30, PID1
ciona_noto_top10_markers[8]
# KH2012:KH.C8.470, TFPI, TFPI2, WFIKKN2 
ciona_noto_top10_markers[9]
# KH2012:KH.C11.328, SERPINB10, SERPINB9, SERPINC1
ciona_noto_top10_markers[10]

```

# What are the orthologs of these genes?
```{r include=TRUE}
# zeb/human ortholog (from Ensembl)

# (1) ERROR KH2012:KH.S423.2 -> ENSCING00000017001 -> None/None 
# *There should be a human ortholog in Ensembl
# *Correct that ENSC is in unmapped_list

# (2) ERROR KH.C11.737 -> ENSCING00000019441 -> None/None
# *There should be a human ortholog in Ensembl
# *Correct that ENSC is in unmapped_list

# (3) CORRECT KH.C13.35 -> ENSCING00000016942
# -> tnmd  (ENSDARG00000052615)
# -> cnmd  (ENSDARG00000100133)/
# --> TNMD  (ENSG00000000005)
# --> CNMD  (ENSG00000136110)
# *Correct that ENSC is in many_list

# (4) Skipped

# (5) KH.C10.8 -> ENSCING00000005858 (FAT4, PROS1, SVEP1)
# -> ndufs2  (ENSDARG00000007526)
# --> NDUFS2  (ENSG00000158864)
# *This is a 1-1 ortholog
# *Correct that ENSC is in correct_list
# *KH.C10.8 in unique_ciona_deg_vec, but ndufs2 is not in unique_zeb_deg_vec

# (7) KH.C9.698 -> ENSCING00000012924 (GPX4/7/8)
# many-to-many Zeb  
# (ENSDARG00000003077) -> ENSCING00000001683, ENSCING00000012924


```

"""
TO DO
"""

# (Zeb) Are any of these in top50 DEGs for Zeb Noto?
```{r include=TRUE}
# No :(
zeb_true_vec <- zeb_ortho_gene_vec %in% ciona_noto_top50_markers
```

# (Ciona) What are the first 10 markers?
```{r include=TRUE}


```