---
title: "validate_get_geneset_v4_pairwise"
output: html_document
---
# TO DO: 
#     1. Fix the dplyr stuff at the end.
#     2. Get rid of cor, keep just the cor.test implementation.

# Version for pairwise DEGs. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(Seurat)
library(dplyr)
library(ggplot2)
```

# Gene List
```{r include=TRUE}
one_one_dir = "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/get_geneset_attempts/v3/one_to_one_khid_zeb_gene_dict.csv" 

one_one_df <- read.table(one_one_dir,
                         sep = ",",
                         header = FALSE,
                         stringsAsFactors = FALSE)

one2one_khid_list = one_one_df$V1
one2one_zeb_genes = one_one_df$V2
```

"""
Helper Function to make Gene Specificity Matrix (Tosches)
"""
```{r include=TRUE}
make_gene_specificity_matrix <- function(average_expression_matrix) {
  # Given an average expression matrix, convert to a gene specificity matrix (Tosches)
  # Args:
  #   average_expression_matrix: 
  #       e.g. ciona_average_expression_matrix <- cbind(ciona_df_1, ciona_df_2)
  #
  # Routine:
  #     g_c/(1/N)sum(i in C)g_i
  #
  # Returns:
  #   gsm: Output of above routine.
  gsm_1 <- average_expression_matrix
  # makes new column with  mean of the row (average expression of gene across all cell types)
  gsm_1 <- gsm_1 %>% mutate(gene_CTs_avexp = rowMeans(.))
  num_cell_types <- ncol(gsm_1)-1
  gsm <- gsm_1[, 1:num_cell_types]/gsm_1[, num_cell_types+1]
  
  return(gsm)
}
```

```{r include=TRUE}
'%notin%' <- Negate('%in%')
```

"""""""""""""""""""""""""""""""
Workflow

final_khids/final_zeb_genes (25, already 1-1 orthologs)
one2one2_khid_list/one2one2_zeb_genes (2592, already 1-1 orthologs)

"""""""""""""""""""""""""""""""

###################################################

# Pairwise DEGs from all Ciona CTs and 12 Zeb CTs
```{r include=TRUE}
v4_ciona_pairwise_degs <- ciona_ans_list$unique_edgeR_degs
v4_ciona_pairwise_degs_0 <- ciona_ans_list_0$unique_edgeR_degs

v4_zeb_pairwise_degs <- zeb_ans_list$unique_edgeR_degs
v4_zeb_pairwise_degs_0 <- zeb_ans_list_0$unique_edgeR_degs
```

###################################################

### DO THIS!!! ###
### INPUT v4_ciona_pairwise_degs_0 HERE ###

###################################################

# Input pairwise DEG lists.
```{r include=TRUE}
khid_pairwise <- v4_ciona_pairwise_degs
zeb_gene_pairwise <- v4_zeb_pairwise_degs
```

##################################################

# Get all unfiltered genes in Zeb and Ciona. 
# Checks if input genes can be used for downstream analyses. 
```{r include=TRUE}
zeb_data <- zeb_integrated_50[["RNA"]]@data
zeb_rownames <- rownames(zeb_data)

unfiltered_zeb_pairwise <- intersect(zeb_rownames, zeb_gene_pairwise)

ciona_data <- clean_chen_larva_integrated_20[["RNA"]]@data
ciona_rownames <- rownames(ciona_data)

unfiltered_ciona_pairwise <- intersect(ciona_rownames, khid_pairwise)
```

# Get the indices of 1-1 orthologs that are pairwise DEGs.
```{r include=TRUE}
zeb_pairwise_ortho_indices <- which(one2one_zeb_genes %in% zeb_gene_pairwise)
ciona_pairwise_ortho_indices <- which(one2one_khid_list %in% khid_pairwise)
```

```{r include=TRUE}
common_pairwise_indices <- intersect(zeb_pairwise_ortho_indices, ciona_pairwise_ortho_indices)
```

# Get qualified genes.
```{r include=TRUE}
qualified_zeb_genes <- one2one_zeb_genes[common_pairwise_indices]
qualified_ciona_khids <- one2one_khid_list[common_pairwise_indices]
```

"""
Ciona: Make Average Expression Dataframes for Ciona CTs (7).
ciona_avexp_df_v4 = ciona_df
"""

## Speficy ciona_cell_type_list and  ##
```{r include=TRUE}
ciona_dummy_col <- rep(0, length(qualified_ciona_khids))
ciona_df <- data.frame(ciona_dummy=ciona_dummy_col)

for (i in 1:length(ciona_cell_type_list)) {
  cat("i = ", i, "\n")
  ciona_cells <- ciona_cell_type_list[[i]]
  # Get gene exp values for all cells in a CT.
  ciona_data_pre <- ciona_data[qualified_ciona_khids, ciona_cells]
  ciona_data_df <- as.data.frame(ciona_data_pre)
  # Get av exp for each gene for all CTs.
  ciona_row <- rowMeans(ciona_data_df)
  ciona_df <- cbind(ciona_df, ciona_row)
}

# Remove ciona_dummy column.
ciona_df <- subset(ciona_df, select=-(ciona_dummy))

ciona_colnames <- names(ciona_cell_type_list)
colnames(ciona_df) <- ciona_colnames

# The Average Expression Dataframe 
ciona_avexp_df_v4 <- ciona_df
```

"""
Zeb: Make Average Expression Dataframes for Zeb CTs (16).
zeb_avexp_df_v4 = zeb_df

These are the same CTs used in Module v3 in "get_geneset_troubleshooting.Rmd"
"""

## Specify zeb_cell_type_list_v4 ##
```{r include=TRUE}
zeb_cell_type_list_v4 <- zeb_CT_12
```
                             
```{r include=TRUE}
zeb_dummy_col <- rep(0, length(qualified_zeb_genes))
zeb_df <- data.frame(zeb_dummy=zeb_dummy_col)

####

for (i in 1:length(zeb_cell_type_list_v4)) {
  cat("i = ", i, "\n")
  zeb_cells <- zeb_cell_type_list_v4[[i]]
  # Get gene exp values for all cells in a CT.
  zeb_data_pre <- zeb_data[qualified_zeb_genes, zeb_cells]
  zeb_data_df <- as.data.frame(zeb_data_pre)
  # Get av exp for each gene for all CTs.
  zeb_row <- rowMeans(zeb_data_df)
  zeb_df <- cbind(zeb_df, zeb_row)
}

# Remove ciona_dummy column.
zeb_df <- subset(zeb_df, select=-(zeb_dummy))

zeb_colnames <- names(zeb_cell_type_list_v4)
colnames(zeb_df) <- zeb_colnames

# The Average Expression Dataframe
zeb_avexp_df_v4 <- zeb_df
```

"""
Make the GSM Dataframes, Cor Df 
"""
```{r include=FALSE}
ciona_gsm_v4 <- make_gene_specificity_matrix(ciona_avexp_df_v4)
zeb_gsm_v4 <- make_gene_specificity_matrix(zeb_avexp_df_v4)
```

##############################################################

### HERE IS WHERE YOU USE THE NEW MAKE_COR_DF FUNCTION

##############################################################

```{r include=TRUE}
make_COR_TEST_df <- function(ciona_gsm, zeb_gsm) {
  cz_cor_df <- data.frame(ciona_CTs = 0,
                             zeb_CTs = 0,
                             p_val = 0,
                             rho = 0)
  
  for (i in 1:ncol(ciona_gsm)) {
    for (j in 1:ncol(zeb_gsm)) {
      # CT expression vectors 
      ciona_CT_col <- ciona_gsm[, i]
      zeb_CT_col <- zeb_gsm[, j]
      # CT name
      ciona_CT <- colnames(ciona_gsm)[i]
      zeb_CT <- colnames(zeb_gsm)[j]
      cat("i= ", i, "j= ", j, "ciona_CT= ", ciona_CT, "zeb_CT= ", zeb_CT, "\n")
      cz_COR_TEST_res <- cor.test(ciona_CT_col, zeb_CT_col, method = "spearman")
      cz_p_val <- cz_COR_TEST_res$p.value
      cz_rho <- cz_COR_TEST_res$estimate
      
      cz_row <- c(ciona_CT, zeb_CT, cz_p_val, cz_rho)
      cat("row = ", cz_row)
      cz_cor_df <- rbind(cz_cor_df, cz_row)
    }
  }
  cz_cor_df <- cz_cor_df[-1, ]
  return(cz_cor_df)
}
```

##############################################################

### TEST MAKE_COR_DF FUNCTION

##############################################################

### DO THIS!!! ###

# Test make_COR_TEST_df
```{r include=TRUE}
test_c_gsm <- ciona_gsm_v4
test_z_gsm <- zeb_gsm_v4
test_cor_test <- make_COR_TEST_df(test_c_gsm, test_z_gsm)

```

##############################################################

### SKIP THIS HERE IS WHERE YOU USE THE NEW MAKE_COR_DF FUNCTION

### INITAL/REAL TEST WITHOUT P-VALS

```{r include=TRUE}
cor_df_v4 <- make_cor_df(ciona_gsm_v4, zeb_gsm_v4)
```

##############################################################

                              ***

##############################################################

### DO THIS!!! ###

### USE TEST_COR_TEST TO MAKE HEATMAP 

```{r include=TRUE}
# test_c_gsm <- ciona_gsm_v4
# test_z_gsm <- zeb_gsm_v4
# test_cor_test <- make_COR_TEST_df(test_c_gsm, test_z_gsm)

cor_df_v4 <- test_cor_test
cor_df_v4 <- cor_df_v4 %>% transform(rho = as.numeric(rho))
```

##### VISUALIZE IT!!!

```{r include=TRUE}
# "RdYlBu", "PiYG"
cor_df_v4_heatmap <- ggplot(data = cor_df_v4,
                         aes(x=ciona_CTs, y=zeb_CTs, fill=rho)) +
                         geom_tile() +
                         scale_fill_distiller(palette = "RdBu")
              

cor_df_v4_heatmap
```

##### WE CAN SEE WHICH PAIRS HAVE SIGNIFICANT P-VALUES ######
```{r include=TRUE}
test_sig <- subset(cor_df_v4, p_val < 5e-2)
```








### ZEB CT LISTS ###
```{r include=TRUE}

zeb_CT_12 <- list(noto = noto,
                 heart_52 = heart_52,
                 heart_51_56 = heart_51_56,
                 muscles = muscles,
                 epi_1 = epi_1,
                 epi_2 = epi_2,
                 panc_prim_endo = panc_prim_endo,
                 meso = meso,
                 pec_fin_bud = pec_fin_bud,
                 leuko = leuko,
                 diff_neus = diff_neus,
                 tail_spinal_cord = tail_spinal_cord)
```


