---
title: "larva_24hpf_brainmap"
output: html_document
---

# Uses Code from one2many_orthology_map_generator.Rmd
# Subsets zeb.avexp.df for Neural Zeb CTs.
# Uses Chen's brainmap CTs -> LTB2/larva Average Expression Vector.
# Rest of pipeline is used for visualization.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(Seurat)
library(dplyr)
library(ggplot2)
library(Matrix)
library(ggcorrplot)
library(psych)
library(stringr)
library(plotly)
```

"""

(1) Make Neural Ciona Average Expression Matrix (ciona.neural.avexp.df).
I need 2 data structures:

(a) ciona.neural.CT.list
(b) chen.cns.data

"""
## Make ciona.neural.cell.type.list.
# Get all the data (will subset) and metadata (to get all CTs and their cells).
```{r include=TRUE}
chen.CNS.data <- CNS.Seurat.LTB2.lv@data
chen.CNS.metadata <- CNS.Seurat.LTB2.lv@meta.data
```

# Get all chen CNS CTs.
```{r include=TRUE}
# 41
chen.CNS.CTs <- unique(chen.CNS.metadata$newcluster.comb.del.anno)
chen.CNS.CTs <- chen.CNS.CTs[-("NA" %in% chen.CNS.CTs)]
chen.CNS.khids <- rownames(chen.CNS.data)
```

# Iterate through chen.CNS.CTs to make ciona.neural.CT.list.
```{r include=TRUE}
ciona.neural.CT.list <- list()

for (chen.CNS.CT in chen.CNS.CTs) {
  # Get dataframe relevant only to that CT. 
  filtered.neural.df <- chen.CNS.metadata %>% filter(newcluster.comb.del.anno == chen.CNS.CT)
  # Get CT's cells.
  CT.cells <- rownames(filtered.neural.df)
  # Update list.
  ciona.neural.CT.list[[chen.CNS.CT]] <- CT.cells
}
```

# Ciona genes of interest = 1-1 and 1-many Orthologs (names(one2one.many.list)).
```{r include=TRUE}
# 3140
qualified.ciona.khids <- names(one2one.many.list)
```

# For some reason, 6 qualified.ciona.khids are not present in this Ciona gene model.
```{r include=TRUE}
not.in.CNS.indices <- which(qualified.ciona.khids %notin% chen.CNS.khids)

not.qualified.ciona.khids <- qualified.ciona.khids[not.in.CNS.indices]

not.qualified.ciona.khids
```
# Remove not.qualified.ciona.khids and Update qualified.ciona.khids.
```{r include=TRUE}
# 3134
re.qualified <- qualified.ciona.khids[-not.in.CNS.indices]
# Update qualified.ciona.khids
qualified.ciona.khids <- re.qualified
```

# Make precursory Average Expression Matrix (ciona.neural.df).
```{r include=TRUE}
ciona.neural.dummy.col <- rep(0, length(qualified.ciona.khids))
ciona.neural.df <- data.frame("ciona.dummy" = ciona.neural.dummy.col)
```

# Make Ciona Average Expression Matrix.
```{r include=TRUE}
# For each Neural Ciona CT
for (i in 1:length(ciona.neural.CT.list)) {
  # Get its name. 
  ciona.CT <- names(ciona.neural.CT.list)[i]
  cat("ciona CT = ", ciona.CT, "\n\n")
  
  # All of its cells.
  ciona.cells <- ciona.neural.CT.list[[i]]
  
  # Subset the matrix based on cells. 
  ciona.data.pre <- chen.CNS.data[qualified.ciona.khids, ciona.cells]
  ciona.data.df <- as.data.frame(ciona.data.pre)
  
  # Get the average expression of each qualified.ciona.khid for the CT.
  ciona.row <- rowMeans(ciona.data.df)
  # Add to ciona.neural.df. In the end, you should have 7 cols, each for a CT.
  ciona.neural.df <- cbind(ciona.neural.df, ciona.row)
}
# Get rid of the dummy column.
ciona.neural.df <- subset(ciona.neural.df, select = -(ciona.dummy))

# Each column is a CT.
ciona.colnames <- names(ciona.neural.CT.list)
colnames(ciona.neural.df) <- ciona.colnames
```
# Ciona Average Expression Matrix.
```{r include=TRUE}
# 3134 x 41
ciona.neural.avexp.df <- ciona.neural.df
```

"""
(2) Make Neural Zeb Average Expression Matrix.

Remove zeb_genes that correspond to not.qualified.ciona.khids.
"""
# Zeb Neural CTs and corresponding Cell Type List.
```{r include=TRUE}
zeb.neural.CTs <- c(cell_type_flags_2, cell_type_flags_3, "lens", "optic_cup", "rpe", "otic_plac", "tail_spinal_cord", "tail_PSM")

zeb.neural.CT.list <- zeb_cell_type_list[zeb.neural.CTs]
```

# Modified
```{r include=TRUE}
# 22 
mod.zeb.neural.CTs <- c(names(cell_type_list_2), names(mod.cell.type.list.3), "lens", "optic_cup", "rpe", "otic_plac", "tail_spinal_cord", "tail_PSM")

mod.zeb.neural.CT.list <- mod.zeb.cell.type.list[mod.zeb.neural.CTs]
```

# Get subset of Zeb Average Expression Matrix for only Zeb Neural CTs and
# update by removing zeb_genes that correspond to not.qualified.ciona.khids.
# Use: not.in.CNS.indices.
```{r include=TRUE}
# 3134 x 25 
zeb.neural.avexp.df <- zeb.avexp.df[-not.in.CNS.indices ,zeb.neural.CTs]
```

# Modified
```{r include=TRUE}
# 3134 x 25 
mod.zeb.neural.avexp.df <- mod.zeb.avexp.df[-not.in.CNS.indices ,mod.zeb.neural.CTs]
```

"""
Perform the rest of the pipeline.
"""

"""
(4) Make the GSM Dataframes, ciona/zeb.gsm 
    using ciona/zeb.neural.avexp.df 
"""
```{r include=FALSE}
ciona.gsm <- make_gene_specificity_matrix(ciona.neural.avexp.df)
rownames(ciona.gsm) <- rownames(ciona.neural.avexp.df)

zeb.gsm <- make_gene_specificity_matrix(zeb.neural.avexp.df)
rownames(zeb.gsm) <- rownames(zeb.neural.avexp.df)
```

# Modified
```{r include=FALSE}
# 3134 x 22
mod.zeb.gsm <- make_gene_specificity_matrix(mod.zeb.neural.avexp.df)
rownames(mod.zeb.gsm) <- rownames(mod.zeb.neural.avexp.df)
```

# Can only 1-many genes recapitulate these heatmaps?
```{r include=TRUE}
many.zeb.rows <- rownames(zeb.gsm)
many.zeb.grep <- grepl("_", many.zeb.rows)

many.zeb.gsm <- zeb.gsm[many.zeb.grep, ]
many.ciona.gsm <- ciona.gsm[many.zeb.grep, ]
```

### Pipeline 1: Adjusted p_vals, Visualizes significant p_vals.
# Uses psych::corr.test
"""
(5.1) Use corr.test to make Correlation and P-Value Matrices.
"""

```{r include=TRUE}
corR.output <- corr.test(x= ciona.gsm,
                         y = zeb.gsm,
                         method = "spearman",
                         adjust = "fdr")
```

```{r include=TRUE}
corR.mat <- corR.output$r
corR.pval.mat <- corR.output$p 
```

# Modified
```{r include=TRUE}
mod.corR.output <- corr.test(x= ciona.gsm,
                         y = mod.zeb.gsm,
                         method = "spearman",
                         adjust = "fdr")
```

```{r include=TRUE}
mod.corR.mat <- mod.corR.output$r
mod.corR.pval.mat <- mod.corR.output$p 
```

# SPECIFY #
```{r include=TRUE}
your.corR.mat <- corR.mat
your.corR.pval.mat <- corR.pval.mat
```
"""
(5.2) Visualize.
"""

# Parameters.
```{r include=TRUE}
# Corr legend range. 
# min(corR.mat)
min.index <- min(your.corR.mat)
# max(corR.mat)
max.index <- max(your.corR.mat)
leeway <- 0.01
limits <- c(min.index-leeway, max.index+leeway)

# Aesthetics and labels. 
your.title <- "+1-Many Neural Larva CTs vs. Zeb CTs, logFC > 0"
your.xlab <- "Ciona Larva"
your.ylab <- "Zeb 24hpf"
your.fill <- "Corr"
#4388F0, 42B5DD
your.color <- "#56B273"
your.face <- "bold"
```

```{r include=TRUE}
p <- ggcorrplot(corr = your.corR.mat,
           p.mat = your.corR.pval.mat)
```

```{r include=TRUE}
p + scale_fill_gradient2(limit = limits,
                          low = "#4C7CC4", mid = "white", high = "#BE1E0B") +
  
  ggplot2::labs(x = your.xlab, y = your.ylab, title = your.title, fill = your.fill) +
  
  ggplot2::theme(plot.title = element_text(size = 10, color = your.color, face = your.face),
                 axis.title.x = element_text(angle = 0, color = your.color, face = your.face),
                 axis.title.y = element_text(angle = 90, color = your.color, face = your.face),
                 
  )
```
"""
(5.3) (a) Get # Significant Correlations. 
      (b) Get Significance between zeb_CT and ciona_CT
"""

# CHANGE zeb.gsm/mod.zeb.gsm #
```{r include=TRUE}
num.sig <- sum(your.corR.pval.mat < 0.05)
num.sig

num.CTs <- ncol(ciona.gsm)*ncol(zeb.gsm)
num.CTs
perc.sig <- num.sig/num.CTs*100
perc.sig
```


