---
title: "mike_gene_lists"
output: html_document
---

# General Script to generate lists of interest.
# 7/30/20: 
# 1-1 DEGs in common and not between Zeb heart_51_56 and Ciona endo, heart, (and mes). 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(Seurat)
library(dplyr)
library(ggplot2)
```

# Import KHID -> Human Ortholog File
```{r include=TRUE}
khid_human_ortho_dir <- "/home/pprakriti/Desktop/orthology_maps_temps/ANISEED-Cirobu-GeneName-3bestBlastHitHuman.rnames"
khid_human_ortho_df <- read.table(khid_human_ortho_dir,
                                  sep = "\t",
                                  stringsAsFactors = FALSE,
                                  header = TRUE)
```

# Get all DEGs (logFC > 1) for Zeb heart_51_56.
```{r include=TRUE}
mike_zeb_heart_degs <- c(rownames(zeb_ans_list$edgeR_res_list$heart_51_56_noto),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_muscles),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_pec_fin_bud),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_panc_prim_endo),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_meso),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_leuko),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_diff_neus),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_epi_1),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_epi_2),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_heart_52),
                         rownames(zeb_ans_list$edgeR_res_list$heart_51_56_tail_spinal_cord))

# 1871 
mike_zeb_heart_degs <- unique(mike_zeb_heart_degs)

# 313
mike_zeb_heart_one2one_indices <- which(one2one_zeb_genes %in% mike_zeb_heart_degs)
```

# Ciona Endo, Heart, Meso DEGs.
```{r include=TRUE}
mike_ciona_endo_degs <- c(rownames(ciona_ans_list$edgeR_res_list$endo_cns),
                          rownames(ciona_ans_list$edgeR_res_list$endo_noto),
                          rownames(ciona_ans_list$edgeR_res_list$endo_heart),
                          rownames(ciona_ans_list$edgeR_res_list$endo_mus),
                          rownames(ciona_ans_list$edgeR_res_list$endo_mes),
                          rownames(ciona_ans_list$edgeR_res_list$endo_epi))

mike_ciona_heart_degs <- c(rownames(ciona_ans_list$edgeR_res_list$heart_noto),
                           rownames(ciona_ans_list$edgeR_res_list$heart_mus),
                           rownames(ciona_ans_list$edgeR_res_list$heart_mes),
                           rownames(ciona_ans_list$edgeR_res_list$heart_epi),
                           rownames(ciona_ans_list$edgeR_res_list$heart_endo),
                           rownames(ciona_ans_list$edgeR_res_list$heart_cns))

mike_ciona_mes_degs <- c(rownames(ciona_ans_list$edgeR_res_list$mes_noto),
                         rownames(ciona_ans_list$edgeR_res_list$mes_heart),
                         rownames(ciona_ans_list$edgeR_res_list$mes_mus),
                         rownames(ciona_ans_list$edgeR_res_list$mes_epi),
                         rownames(ciona_ans_list$edgeR_res_list$mes_endo),
                         rownames(ciona_ans_list$edgeR_res_list$mes_cns))

# 3287 -> 1171 
mike_ciona_endo_degs <- unique(mike_ciona_endo_degs)
mike_ciona_endo_one2one_indices <- which(one2one_khid_list %in% mike_ciona_endo_degs)
# 2379 -> 926 
mike_ciona_heart_degs <- unique(mike_ciona_heart_degs)
mike_ciona_heart_one2one_indices <- which(one2one_khid_list %in% mike_ciona_heart_degs)
# 1504 -> 534
mike_ciona_mes_degs <- unique(mike_ciona_mes_degs)
mike_ciona_mes_one2one_indices <- which(one2one_khid_list %in% mike_ciona_mes_degs)
```

# What pairwise indices are in common?
```{r include=TRUE}
# 202
cz_endo_heart <- intersect(mike_ciona_endo_one2one_indices, mike_zeb_heart_one2one_indices)
# 168
cz_heart_heart <- intersect(mike_ciona_heart_one2one_indices, mike_zeb_heart_one2one_indices)
# 97
cz_mes_heart <- intersect(mike_ciona_mes_one2one_indices, mike_zeb_heart_one2one_indices)
```

# What indices are shared among Ciona Endo and Heart?
```{r include=TRUE}
# 164 (Heart and Endo share a lot of 1-1 orthologs with Zeb Heart). # 93 in common among all.
mike_common_indices <- intersect(cz_endo_heart, cz_heart_heart)
mike_only_endo <- setdiff(cz_endo_heart, cz_heart_heart)
mike_only_heart <- setdiff(cz_heart_heart, cz_endo_heart)
```

# Gene Lists.
```{r include=TRUE}
endo_khids <- one2one_khid_list[mike_only_endo]
endo_human_df <- khid_human_ortho_df[khid_human_ortho_df$Gene.ID %in% endo_khids, ]
endo_human_df

heart_khids <- one2one_khid_list[mike_only_heart]
heart_human_df <- khid_human_ortho_df[khid_human_ortho_df$Gene.ID %in% heart_khids, ]
heart_human_df

common_khids <- one2one_khid_list[mike_common_indices]
common_human_df <- khid_human_ortho_df[khid_human_ortho_df$Gene.ID %in% common_khids, ]
common_human_df
```
# csv files
```{r include=TRUE}
write.table(x = common_human_df, 
            file = "common_orthologs.csv", 
            sep = "\t",
            row.names = FALSE)
```

```{r include=TRUE}
write.table(x = endo_human_df,
            file = "ciona_endo_orthologs.tsv",
            sep = "\t",
            row.names = FALSE)

write.table(x = heart_human_df,
            file = "ciona_heart_orthologs.tsv",
            sep = "\t",
            row.names = FALSE)

```
"""
Negatively Correlated Tissues
"""
# What about negative correlating Ciona tissues? How many orthologs do they share with Zeb Heart? 
```{r include=TRUE}
mike_ciona_cns_degs <- c(rownames(ciona_ans_list$edgeR_res_list$cns_noto),
                         rownames(ciona_ans_list$edgeR_res_list$cns_heart),
                         rownames(ciona_ans_list$edgeR_res_list$cns_mus),
                         rownames(ciona_ans_list$edgeR_res_list$cns_mes),
                         rownames(ciona_ans_list$edgeR_res_list$cns_epi),
                         rownames(ciona_ans_list$edgeR_res_list$cns_endo))

mike_ciona_mus_degs <- c(rownames(ciona_ans_list$edgeR_res_list$mus_noto),
                         rownames(ciona_ans_list$edgeR_res_list$mus_heart),
                         rownames(ciona_ans_list$edgeR_res_list$mus_mes),
                         rownames(ciona_ans_list$edgeR_res_list$mus_epi),
                         rownames(ciona_ans_list$edgeR_res_list$mus_endo),
                         rownames(ciona_ans_list$edgeR_res_list$mus_cns))

mike_ciona_noto_degs <- c(rownames(ciona_ans_list$edgeR_res_list$noto_heart),
                          rownames(ciona_ans_list$edgeR_res_list$noto_mus),
                          rownames(ciona_ans_list$edgeR_res_list$noto_mes),
                          rownames(ciona_ans_list$edgeR_res_list$noto_epi),
                          rownames(ciona_ans_list$edgeR_res_list$noto_endo),
                          rownames(ciona_ans_list$edgeR_res_list$noto_cns))

# We don't just care about the genes in common, but their expression levels.
# Only 127 indices in common among these tissues. 
# 2573 -> 509
mike_ciona_cns_degs <- unique(mike_ciona_cns_degs)
mike_ciona_cns_one2one_indices <- which(one2one_khid_list %in% mike_ciona_cns_degs)
# 2336 -> 380 
mike_ciona_mus_degs <- unique(mike_ciona_mus_degs)
mike_ciona_mus_one2one_indices <- which(one2one_khid_list %in% mike_ciona_mus_degs)
# 2283 -> 442
mike_ciona_noto_degs <- unique(mike_ciona_noto_degs)
mike_ciona_noto_one2one_indices <- which(one2one_khid_list %in% mike_ciona_noto_degs)

```


