---
title: "orthology_map_heatmap_generator"
output: html_document
---

# Adapted from "gene_geneset_v4_pairwise.Rmd"
# Refer to "mike_gene_lists.Rmd" for further munging.

# Inputs: (1) larva/zeb.dir (different lists based on logFC, munged in
# "get_common_degs.py").
#         (2) zeb_cell_type_list_v4 (different lists based on Zeb CT composition)
#                                   (All/No Neural).
#         (3) Aesthetics in 5.2 for Heatmaps.

# Note: All filtering is done on qualified_ciona_khids and qualified_zeb_genes.

# Also gene list analyses are here. 

# TO DO:
#     (1) Clean up Nitta df
#     (2) Sketchy Kai Gene Lists (getting correct zeb genes)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(Seurat)
library(dplyr)
library(ggplot2)
library(Matrix)
library(ggcorrplot)
library(psych)
library(stringr)
library(plotly)
```

##### Part 1: Make Heatmaps! #####

"""
  (1) Specify qualified_ciona_khids, qualified_zeb_genes (1-1 DEG orthologs).
      Note: These are Embryo 1-1 DEG orthologs.
      
  (2) Specify Cell Type Lists.
  
  (3) Make ciona_avexp_df_v4, zeb_avexp_df_v4

"""
## CHANGE ##
```{r include=TRUE}
# Note: These files correspond to gene lists generated from different logFC values.

# larva.dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/1_CURRENT/one2one_larva_24hpf/logFC_0/one2one_24hpf_larva_khids_logFC0.csv"
# 
# zeb.dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/1_CURRENT/one2one_larva_24hpf/logFC_0/one2one_larva_24hpf_genes_logFC0.csv"

# These are all 2516 1-1 DEG Orthologs.
# larva.dir <- "/home/pprakriti/Desktop/all_larva_2516_DEGs.csv"
# zeb.dir <- "/home/pprakriti/Desktop/all_24hpf_2516_DEGs.csv"

larva.khids.df <- read.table(larva.dir,
                         sep = ",",
                         header = FALSE,
                         stringsAsFactors = FALSE)

zeb.genes.df <- read.table(zeb.dir,
                         sep = ",",
                         header = FALSE,
                         stringsAsFactors = FALSE)

# For logFC>0, there are 2466 1-1 DEG Orthologs.  
larva.khids <- larva.khids.df$V1
zeb.genes <- zeb.genes.df$V1
```

# Get 1-1 Ortholog Gene lists from above.
```{r include=TRUE}
qualified_ciona_khids <- larva.khids
qualified_zeb_genes <- zeb.genes
```

# This is the baseline. Expression of all 1-1 orthologs (2594).
```{r include=TRUE}
qualified_ciona_khids_pre <- one_one_df$V1
qualified_zeb_genes_pre <- one_one_df$V2

in_ciona_indices <- which(qualified_ciona_khids_pre %in% rownames(ciona_data))
in_zeb_indices <- which(qualified_zeb_genes_pre %in% rownames(zeb_data))
common_indices <- intersect(in_ciona_indices, in_zeb_indices)

qualified_ciona_khids <- qualified_ciona_khids_pre[common_indices]
qualified_zeb_genes <- qualified_zeb_genes_pre[common_indices]
```

# Specify Zeb Cell Type List. zeb_cell_type_list has all Zeb CTs. 
```{r include=TRUE}
# Note: We will change zeb_cell_type_list_v4 based on All/No Neural
#       ciona_cell_type_list never changes.

# ciona_cell_type_list
zeb_cell_type_list_v4 <- zeb_cell_type_list
```

# Make precursory Average Expression Matrix (ciona_df).
```{r include=TRUE}
ciona_dummy_col <- rep(0, length(qualified_ciona_khids))
```

# Make Ciona Average Expression Matrix (ciona_avexp_df_v4).
```{r include=TRUE}
ciona_df <- data.frame(ciona_dummy=ciona_dummy_col)

# For each Ciona CT
for (i in 1:length(ciona_cell_type_list)) {
  cat("i = ", i, "\n")
  # Get its cells.
  ciona_cells <- ciona_cell_type_list[[i]]
  
  # Get gene exp values for all genes in all cells.
  ciona_data_pre <- ciona_data[qualified_ciona_khids, ciona_cells]
  ciona_data_df <- as.data.frame(ciona_data_pre)
  
  # Get av exp for each gene.
  ciona_row <- rowMeans(ciona_data_df)
  ciona_df <- cbind(ciona_df, ciona_row)
}

# Remove ciona_dummy column.
ciona_df <- subset(ciona_df, select=-(ciona_dummy))

# Munge.
ciona_colnames <- names(ciona_cell_type_list)
colnames(ciona_df) <- ciona_colnames
```

# The Average Expression Dataframe (ciona_avexp_df_v4).
```{r include=TRUE}
ciona_avexp_df_v4 <- ciona_df
```

# Make precursory Average Expression Matrix (zeb_df). 
```{r include=TRUE}
zeb_dummy_col <- rep(0, length(qualified_zeb_genes))
```

# Make Zeb Average Expression Matrix (zeb_avexp_df_v4).
```{r include=TRUE}
zeb_df <- data.frame(zeb_dummy=zeb_dummy_col)

for (i in 1:length(zeb_cell_type_list_v4)) {
  cat("i = ", i, "\n")

  zeb_cells <- zeb_cell_type_list_v4[[i]]
  
  # Get gene exp values for all cells in a CT.
  zeb_data_pre <- zeb_data[qualified_zeb_genes, zeb_cells]
  zeb_data_df <- as.data.frame(zeb_data_pre)
  
  # Get av exp for each gene for all CTs.
  zeb_row <- rowMeans(zeb_data_df)
  zeb_df <- cbind(zeb_df, zeb_row)
}

# Remove zeb_dummy column.
zeb_df <- subset(zeb_df, select=-(zeb_dummy))

# Munge. 
zeb_colnames <- names(zeb_cell_type_list_v4)
colnames(zeb_df) <- zeb_colnames
```

# The Average Expression Dataframe (zeb_avexp_df_v4).
```{r include=TRUE}
zeb_avexp_df_v4 <- zeb_df
```

"""
(4) Make the GSM Dataframes, ciona/zeb_gsm_v4
"""
```{r include=FALSE}
ciona_gsm_v4 <- make_gene_specificity_matrix(ciona_avexp_df_v4)
rownames(ciona_gsm_v4) <- rownames(ciona_avexp_df_v4)

zeb_gsm_v4 <- make_gene_specificity_matrix(zeb_avexp_df_v4)
rownames(zeb_gsm_v4) <- rownames(zeb_avexp_df_v4)
```

### Pipeline 1: Adjusted p_vals, Visualizes significant p_vals.
# Uses psych::corr.test
"""
(5.1) Use corr.test to make Correlation and P-Value Matrices.
"""
```{r include=TRUE}
corR_output <- corr.test(x= ciona_gsm_v4,
                         y = zeb_gsm_v4,
                         method = "spearman",
                         adjust = "fdr")
```

```{r include=TRUE}
corR_mat <- corR_output$r
corR_pval_mat <- corR_output$p 
```

"""
(5.2) Visualize.
"""

# Parameters.
```{r include=TRUE}
# Corr legend range. 
min_index <- min(corR_mat)
max_index <- max(corR_mat)
leeway <- 0.01
limits <- c(min_index-leeway, max_index+leeway)

# Aesthetics and labels. 
your.title <- "Larva CTs vs. Zeb CTs, All 1-1 DEG Orthologs (2516)"
your.xlab <- "Ciona Larva"
your.ylab <- "Zeb 24hpf"
your.fill <- "Corr"
#4388F0, 42B5DD
your.color <- "#56B273"
your.face <- "bold"
```

```{r include=TRUE}
p <- ggcorrplot(corr = corR_mat,
           p.mat = corR_pval_mat)
```

```{r include=TRUE}
p + scale_fill_gradient2(limit = limits,
                          low = "#4C7CC4", mid = "white", high = "#BE1E0B") +
  
  ggplot2::labs(x = your.xlab, y = your.ylab, title = your.title, fill = your.fill) +
  
  ggplot2::theme(plot.title = element_text(size = 10, color = your.color, face = your.face),
                 axis.title.x = element_text(angle = 0, color = your.color, face = your.face),
                 axis.title.y = element_text(angle = 90, color = your.color, face = your.face),
                 
  )
   
```
"""
(5.3) (a) Get # Significant Correlations. 
      (b) Get Significance between zeb_CT and ciona_CT
"""
```{r include=TRUE}
num.sig <- sum(corR_pval_mat < 0.05)
num.sig

num.CTs <- ncol(ciona_gsm_v4)*ncol(zeb_gsm_v4)
perc.sig <- num.sig/num.CTs*100
perc.sig
```

```{r include=TRUE}
# CHANGE
ciona.index <- 3 
zeb.index <- 4 

for (i in 1:ciona.index) {
  for (j in 1:zeb.index) {
    ciona.CT.list <- c("noto", "mus", "heart" )
    zeb.CT.list <- c("noto", "muscles", "heart_52", "heart_51_56")
    
    ciona.CT <- ciona.CT.list[i]
    zeb.CT <- zeb.CT.list[j]
    
    cat("ciona CT = ", ciona.CT, "\n", "zeb CT= ", zeb.CT, "\n")
    p.val <- corR.pval.mat[ciona.CT, zeb.CT]
    p.val <- signif(p.val, 3)
    cat(p.val, "\n")
    correlation <- corR.mat[ciona.CT, zeb.CT]
    correlation <- signif(correlation, 3)
    cat(correlation, "\n\n")
  } 
}
```

##### Part 2: TF SMG ANALYSES #####
"""
Various lists for TF and SMG filtering
"""

# TF List 1: Nitta 2019 (SELEX Project)

# TO DO: Clean up the dataframe, not just get gene names. 
```{r include=TRUE}
ciona.tf.dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/ciona_regulatory_regions/unmunged_ciona_TFs.csv"

ciona.tf.df <- read.table(ciona.tf.dir,
                          sep = ",",
                          stringsAsFactors = FALSE,
                          header = TRUE)

# Important Variable (964 Nitta TFs)
ciona.tfs <- ciona.tf.df$KH.model.ID
ciona.tfs <- ciona.tfs[!ciona.tfs == ""]
ciona.tfs <- paste("KH2012:", ciona.tfs, sep = "")
```

# Aniseed Human Ortholog File
```{r include=TRUE}
khid.human.ortho.dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/lifechanging_aniseed_files/ANISEED-Cirobu-GeneName-3bestBlastHitHuman.rnames"

# 26426
khid.human.ortho.df <- read.table(khid.human.ortho.dir,
                                  sep = "\t",
                                  stringsAsFactors = FALSE,
                                  header = TRUE)
```

"""
How many of these 1-1 DEG Orthologs are TFs?
"""

# KHID and Zeb Names
```{r include=TRUE}
ciona.tf.indices <- which(qualified_ciona_khids %in% ciona.tfs)

# What are their names?
qual.ciona.tfs <- qualified_ciona_khids[ciona.tf.indices]
qual.zeb.tfs <- qualified_zeb_genes[ciona.tf.indices]

cat(qual.ciona.tfs, sep="\n")
cat("\n")
cat(qual.zeb.tfs, sep="\n")
```
# Human Orthologs 
```{r include=TRUE}
qual.human.tfs <- khid.human.ortho.df[khid.human.ortho.df$Gene.ID %in% qual.ciona.tfs, ]
qual.human.tfs
```
# Print Results. 
```{r include=TRUE}
khid.names <- qual.human.tfs$Gene.ID
khid.human.names <- qual.human.tfs$Gene.Name

for (i in 1:length(khid.names)) {
  my.name <- khid.names[i]
  my.human.name <- khid.human.names[i]
  
  cat(my.name, "=", my.human.name, "\n")
}
```
"""
Analyses using Kai's files.
"""
# TF and SMG List: Kai (Ghost Curation)
```{r include=TRUE}
kai.tf.smg.dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/ciona_regulatory_regions/kai_tf_smg_list.csv"

kai.tf.smg.df <- read.table(kai.tf.smg.dir,
                            sep = ",",
                            header = TRUE,
                            stringsAsFactors = FALSE)
```

# Munge KHIDs.
```{r include=TRUE}
add.kh.tag <- function(kh.name) {
  full.kh.name <- paste0("KH2012:", kh.name)
  return(full.kh.name)
}

new.col <- as.data.frame(sapply(kai.tf.smg.df[, 1], add.kh.tag))
colnames(new.col) <- "KH.gene.model"
kai.tf.smg.df[, 1] <- new.col 

# Important Variable (1023 Kai TF/SMGs)
all.kai.genes <- as.vector(kai.tf.smg.df$KH.gene.model)
```

# Which 1-1 DEG Orthologs are TF/SMGs?
```{r include=TRUE}
kai.filtered.df <- kai.tf.smg.df %>% filter(KH.gene.model %in% qualified_ciona_khids)
```

# Print Results 
```{r include=TRUE}
# Kai genes are filtered (within 1-1 DEG Ortholog List) NOT ALL KAI GENES
kai.genes <- as.vector(kai.filtered.df$KH.gene.model)
kai.gene.names <- kai.filtered.df$Ghost.Name
kai.class <- kai.filtered.df$Ghost.class

for (i in 1:length(kai.genes)) {
  my.gene <- kai.genes[i]
  my.gene.name <- kai.gene.names[i]
  my.class <- kai.class[i]
  
  cat(my.gene, "=", my.gene.name, "(", my.class, ")","\n")
}
```

# Quick Utility to get ciona khid and zeb gene names for kai.genes
```{r include=TRUE}
# Tells you INDICES of 1-1 ciona khids that are kai genes.
kai.gene.indices <- which(qualified_ciona_khids %in% kai.genes)

# These tell you which 1-1 ciona khids are kai genes. 
kai.ciona.genes <- qualified_ciona_khids[kai.gene.indices]
kai.zeb.genes <- qualified_zeb_genes[kai.gene.indices]
```

##### Part 3: GENE LIST ANALYSES #####
"""
Start For Individual CT Analyses (Re-Analyses)
"""
# CHANGE directories for individual CTs.
```{r include=TRUE}
ciona.CT.dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/1_CURRENT/one2one_larva_24hpf/logFC_0/24hpf_2hearts_gene_analyses/2CT_analyses/larva_noto_24hpf_noto_analyses/larva_noto_24hpf_noto_DEG_logFC0_khids.csv"

zeb.CT.dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/1_CURRENT/one2one_larva_24hpf/logFC_0/24hpf_2hearts_gene_analyses/2CT_analyses/larva_noto_24hpf_noto_analyses/larva_noto_24hpf_noto_DEG_logFC0_zebgenes.csv"

ciona.CT.df <- read.table(ciona.CT.dir,
                          sep =",",
                          header = FALSE,
                          stringsAsFactors = FALSE)

zeb.CT.df <- read.table(zeb.CT.dir,
                          sep =",",
                          header = FALSE,
                          stringsAsFactors = FALSE)

ciona.CT.genes <- ciona.CT.df$V1
zeb.CT.genes <- zeb.CT.df$V1

length(ciona.CT.genes)
```

# Nitta and Kai Filtering for individual CTs. 
(Can use below in Visualizations as ciona_genes and zeb_genes)
```{r include=TRUE}
# Which of these are Nitta TFs?
ciona.CT.nitta.indices <- which(ciona.CT.genes %in% ciona.tfs)
ciona.CT.nitta <- ciona.CT.genes[ciona.CT.nitta.indices]
length(ciona.CT.nitta)

# Which of these are Kai TF SMGs?
ciona.CT.kai.indices <- which(ciona.CT.genes %in% kai.genes)
ciona.CT.kai <- ciona.CT.genes[ciona.CT.kai.indices]
length(ciona.CT.kai)
```

# Get Human Orthologs for individual CTs.
# CHANGE filtered.genes = ciona.CT.nitta/kai
```{r include=TRUE}
filtered.genes <- ciona.CT.kai
filtered.genes
cat("\n\n")
  
# Dataframe: KHID, Human Ortholog
filtered.human.khids <- khid.human.ortho.df[khid.human.ortho.df$Gene.ID %in% filtered.genes, ]
filtered.names <- filtered.human.khids$Gene.Name

filtered.names
cat("\n\n")

filtered.human.khids
```


"""
End For Individual CT Analyses (Re-Analyses)
"""

"""""""
Part 3: What are the highly expressed genes here?
Note: All Analyses below pertain to logFC>0. 

(1) Pick Genes:
a) all 1-1 DEG Orthologs (2466)
qualified_ciona_khids, qualified_zeb_genes
Correlation of 2466 1-1 DEG Orthologs

b) Nitta filtering (235) 
qual.ciona.tfs, qual.zeb.tfs
Correlation of Nitta TFs

c) Kai filtering (197)
kai.ciona.genes, kai.zeb.genes
Correlation of Kai TF and SMGs

d) For individual CTs
ciona.CT.genes, zeb.CT.genes
(would have been defined before) filtered.genes <- ciona.CT.nitta, ciona.CT.kai

(2) Pick pairs of CTs
ciona.CT, zeb.CT

""""""""

# Specify Genes and CTs.
```{r include=TRUE}
# Change
ciona.CT <- "noto"
zeb.CT <- "noto"
ciona_genes <- ciona.CT.genes
zeb_genes <- zeb.CT.genes

ciona.CT.av.exp <- ciona_gsm_v4[ciona_genes, ciona.CT]
zeb.CT.av.exp <- zeb_gsm_v4[zeb_genes, zeb.CT]

scatter.df <- data.frame(ciona.CT = ciona.CT.av.exp,
                         zeb.CT = zeb.CT.av.exp,
                         khid = ciona_genes,
                         zeb.genes = zeb_genes)

zeb.noto <- "zeb_noto"
colnames(scatter.df)[1:2] <- c(ciona.CT, zeb.noto)
```

(3) Visualize
```{r include=TRUE}
# Change
your.title <- "Correlation of CT 1-1 DEG Orthologs"
your.av.exp.cutoff.ciona <- 1
your.av.exp.cutoff.zeb <- 1

new.labels <- gsub("KH2012:KH.", "", ciona_genes)
 
scatter.plot <- ggplot(scatter.df,
                       aes(x = ciona.CT.av.exp, y = zeb.CT.av.exp)) +
                       geom_point() + 
  
                       geom_text(size=2.5, hjust=0, vjust=0, angle=0, aes(label = ifelse(ciona.CT.av.exp>your.av.exp.cutoff.ciona & zeb.CT.av.exp>your.av.exp.cutoff.zeb, as.character(new.labels), ""))) +
  
  ggtitle(your.title) +
  xlab(ciona.CT) +
  ylab(zeb.CT) +
  geom_abline()

scatter.plot
```

(4) Get the Human Orthologs of above KHIDs. (Manually Curated from Scatter Plot)
```{r include=TRUE}
res.ciona.khids <- c("C5.525", "C5.1", "L171.10", "C3.308")

res.ciona.khids <- paste0("KH2012:KH.", res.ciona.khids)

# Dataframe: KHID, Human Ortholog
res.human.khids <- khid.human.ortho.df[khid.human.ortho.df$Gene.ID %in% res.ciona.khids, ]

res.names <- res.human.khids$Gene.Name
res.names
```

# Interactive Scatter Plot
```{r include=TRUE}
# x = ciona.CT.av.exp, y = zeb.CT.av.exp
fig <- plot_ly(type = "scatter", scatter.df, x = ~noto, y = ~zeb_noto, text = ~khid)

fig
```

(4) Get the Human Orthologs of above KHIDs. (Manually Curated from Interactive Scatter Plot)
```{r include=TRUE}
my.genes <- c("KH2012:KH.C14.310")
my.genes
cat("\n\n")
  
# Dataframe: KHID, Human Ortholog
my.human.khids <- khid.human.ortho.df[khid.human.ortho.df$Gene.ID %in% my.genes, ]
my.names <- my.human.khids$Gene.Name

my.names
cat("\n\n")

my.human.khids
```


















### Unused below

### (Old) Pipeline 2: Unadjusted p_vals, Does not visualize significant p_vals. 
# Uses stats::cor.test
"""
(5.1) Make cor_df using make_core_df function 
"""

```{r include=TRUE}
make_cor_df <- function(ciona_gsm, zeb_gsm) {
  # Given two gene specificity matrices, make a dataframe with 4 columns: 2 with CT names,
  # p-value (NOT ADJUSTED) and rho (correlation coefficient).
  # 
  # Args:
  #   ciona_gsm, zeb_gsm: Self-explanatory.
  #
  # Returns: Dataframe given above description.
  cz_cor_df <- data.frame(ciona_CTs = 0,
                             zeb_CTs = 0,
                             p_val = 0,
                             rho = 0)
  
  for (i in 1:ncol(ciona_gsm)) {
    for (j in 1:ncol(zeb_gsm)) {
      # CT expression vectors 
      ciona_CT_col <- ciona_gsm[, i]
      zeb_CT_col <- zeb_gsm[, j]
      # CT name
      ciona_CT <- colnames(ciona_gsm)[i]
      zeb_CT <- colnames(zeb_gsm)[j]
      
      cat("i= ", i, "j= ", j, "ciona_CT= ", ciona_CT, "zeb_CT= ", zeb_CT, "\n")
      cz_COR_TEST_res <- cor.test(ciona_CT_col, zeb_CT_col, method = "spearman", adju)
      cz_p_val <- cz_COR_TEST_res$p.value
      cz_rho <- cz_COR_TEST_res$estimate
      
      cz_row <- c(ciona_CT, zeb_CT, cz_p_val, cz_rho)
      cat("row = ", cz_row)
      
      cz_cor_df <- rbind(cz_cor_df, cz_row)
    }
  }
  cz_cor_df <- cz_cor_df[-1, ]
  return(cz_cor_df)
}
```

# Make cor_df 
```{r include=TRUE}
c_gsm <- ciona_gsm_v4
z_gsm <- zeb_gsm_v4
cor_df <- make_cor_df(c_gsm, z_gsm)
```

"""
(6.1) Munge cor_df.
"""
```{r include=TRUE}
cor_df_v4 <- cor_df
cor_df_v4 <- cor_df_v4 %>% transform(rho = as.numeric(rho))
cor_df_v4 <- cor_df_v4 %>% transform(p_val = as.numeric(p_val))
```

"""
(7.1) Visualize! 
"""
```{r include=TRUE}
# "RdYlBu", "PiYG"
cor_df_v4_heatmap <- ggplot(data = cor_df_v4,
                         aes(x=ciona_CTs, y=zeb_CTs, fill=rho)) +
                         geom_tile() +
                         scale_fill_distiller(palette = "RdBu")
              
cor_df_v4_heatmap
```

"""
(8.1) Get significant p-values (unadjusted).
"""

```{r include=TRUE}
sig_df <- subset(cor_df_v4, p_val < 0.05)
```

######

# Past directories/files used. 
```{r include=TRUE}
# (1) All CTs, logFC>1 

"/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/1_CURRENT/one2one_larva_24hpf/logFC_1/one2one_24hpf_larva_khids_logFC1.csv" 

"/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/1_CURRENT/one2one_larva_24hpf/logFC_1/one2one_larva_24hpf_genes_logFC1.csv"


```

