---
title: "one2many_orthology_map_generator"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "orthology_map_heatmap_generator"
output: html_document
---
# 10/2020 NOTE: ciona_data and zeb_data has been modified to have DATA VALUES FROM 
# INTEGRATED NOT RNA (batch-corrected) ASSAY SLOT.

# Adapted from "gene_geneset_v4_pairwise.Rmd"
# Refer to "mike_gene_lists.Rmd" for further munging.

# Inputs: (1) larva/zeb.dir (different lists based on logFC, munged in
# "get_common_degs.py").
#         (2) zeb_cell_type_list_v4 (different lists based on Zeb CT composition)
#                                   (All/No Neural).
#         (3) Aesthetics in 5.2 for Heatmaps.

# Note: All filtering is done on qualified_ciona_khids and qualified_zeb_genes.

# Also gene list analyses are here. 

# TO DO:
#     (1) Clean up Nitta df
#     (2) Sketchy Kai Gene Lists (getting correct zeb genes)

```{r include=FALSE}
library(Seurat)
library(dplyr)
library(ggplot2)
library(Matrix)
library(ggcorrplot)
library(psych)
library(stringr)
library(plotly)
```

##### 10/2020: Modify ciona/zeb_data #####
```{r include=TRUE}
ciona_data <- clean_chen_larva_integrated_20[["RNA"]]@data

zeb_data <- zeb_integrated_50[["RNA"]]@data
```

##### Part 1: Make Heatmaps! #####

# Read in "one2one_many_dict.csv"
```{r include=TRUE}
filtered.one2one.many.dict.dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/1_CURRENT/one2one_many_larva_24hpf/filtered_one2one_many_export_dict_20_09_07.csv"
# 3140
one2one.many.dict <- read.table(filtered.one2one.many.dict.dir,
                                sep = ",",
                                header = FALSE,
                                stringsAsFactors = FALSE)
```


# one2one.many.dict df -> one2one.many.list = {khid : ['aimp1a' 'aimp1b']} 
# Note: All lists are of length 1.
```{r include=TRUE}
# 3140
one2one.many.list <- list()
num.khids <- dim(one2one.many.dict)[1]

for (i in 1:num.khids) {
  khid <- one2one.many.dict$V1[i]
  
  zeb.genes <- one2one.many.dict$V2[i]
  zeb.genes <- strsplit(zeb.genes, " ")
  one2one.many.list[[khid]] <- zeb.genes
}
```

# Ciona genes of interest- length of column should be the number of these genes.
```{r include=TRUE}
# 3140
qualified.ciona.khids <- names(one2one.many.list)
```

# Make precursory Average Expression Matrix (ciona.df).
```{r include=TRUE}
# Each row of a column should be a gene name. 
ciona.dummy.col <- rep(0, length(qualified.ciona.khids))
ciona.df <- data.frame("ciona.dummy" = ciona.dummy.col)
```

# Make Ciona Average Expression Matrix.
```{r include=TRUE}
# For each Ciona CT
for (i in 1:length(ciona_cell_type_list)) {
  # Get its name. 
  ciona.CT <- names(ciona_cell_type_list)[i]
  cat("ciona CT = ", ciona.CT, "\n\n")
  
  # All of its cells.
  ciona.cells <- ciona_cell_type_list[[i]]
  
  # Subset the matrix based on cells. 
  ciona.data.pre <- ciona_data[qualified.ciona.khids, ciona.cells]
  ciona.data.df <- as.data.frame(ciona.data.pre)
  
  # Get the average expression of each qualified.ciona.khid for the CT.
  ciona.row <- rowMeans(ciona.data.df)
  # Add to ciona.df. In the end, you should have 7 cols, each for a CT.
  ciona.df <- cbind(ciona.df, ciona.row)
}
# Get rid of the dummy column.
ciona.df <- subset(ciona.df, select = -(ciona.dummy))

# Each column is a CT.
ciona.colnames <- names(ciona_cell_type_list)
colnames(ciona.df) <- ciona.colnames
```

# Ciona Average Expression Matrix.
```{r include=TRUE}
ciona.avexp.df <- ciona.df
```

############### START DO NOT TOUCH!!!! #################
################# MODIFIED ZEB CTs ###################

# Let us now make zeb.df. 
# num_col = # CTs (43); num_rows = # of qualified.ciona.khids.
```{r include=TRUE}
# length(zeb_cell_type_list)- keep below
mod.num.zeb.df.cols <- length(mod.zeb.cell.type.list)
# Because this is the number of Ciona khids.
mod.num.zeb.df.rows <- length(qualified.ciona.khids)
# 3134 x 39
mod.zeb.df <- data.frame(matrix(, nrow=mod.num.zeb.df.rows, ncol=mod.num.zeb.df.cols))
```

# Get colnames that correspond to various Zeb CTs.
```{r include=TRUE}
mod.zeb.df.colnames <- names(mod.zeb.cell.type.list)
colnames(mod.zeb.df) <- mod.zeb.df.colnames
```

# Get rownames that represent mapping.
```{r include=TRUE}
# I discovered that there were 2 zeb_genes (ube2c_2 and rpl37_2) that mapped to 2 different khids that were 
# labeled as 1-1. Their names are munged here.

mod.zeb.df.rownames <- c()
# seen.zeb.rownames <- c()

for (i in 1:length(one2one.many.list)) {
  khid <- names(one2one.many.list)[i]
  cat("khid = ", khid, "\n\n")
  
  mod.zeb.names <- one2one.many.list[[i]][[1]]
  # cat(zeb.names, "\n\n")
  
  mod.zeb.name.string <- paste(mod.zeb.names, collapse = "_")
  # cat("zeb name string = ", zeb.name.string, "\n\n")
  
  if (mod.zeb.name.string %in% mod.zeb.df.rownames) {
    # cat("PROBLEM zeb name string = ", zeb.name.string, "\n\n")
    
    # Add _2 to seen.zeb.rownames to avoid redundant rowname conflicts. 
    mod.zeb.name.string <- paste(mod.zeb.name.string, "2", sep = "_")
    # seen.zeb.rownames <- c(seen.zeb.rownames, zeb.name.string)

  }
  mod.zeb.df.rownames <- c(mod.zeb.df.rownames, mod.zeb.name.string)
}

# Modify zeb.df with these rownames. 
rownames(mod.zeb.df) <- mod.zeb.df.rownames
```

# Make average expression dataframe.
```{r include=TRUE}
# For each Zeb CT
for (i in 1:length(mod.zeb.cell.type.list)) {
  mod.zeb.CT.name <- names(mod.zeb.cell.type.list)[i]
  # Get its cells. 
  mod.zeb.cells <- mod.zeb.cell.type.list[[i]]
  mod.zeb.length <- length(mod.zeb.cells)
  cat("Zeb CT = ", mod.zeb.CT.name, "\n", mod.zeb.length)
  
  # Get 1-1/1-many zeb genes.
  for (j in 1:length(one2one.many.list)) {
    cat("i = ", i, "j = ", j, "\n\n")
    mod.one.many.zeb.genes <- one2one.many.list[[j]][[1]]
    
    # Subset Zeb Data based on these genes.
    mod.zeb.sub <- zeb_data[mod.one.many.zeb.genes, mod.zeb.cells]
    
    # Get Average Expression.
    mod.zeb.av <- sum(mod.zeb.sub)/mod.zeb.length
    # Add to correct entry. 
    mod.zeb.df[j, i] <- mod.zeb.av
  }
}
```

# Zeb Average Expression Matrix
```{r include=TRUE}
mod.zeb.avexp.df <- mod.zeb.df
```

############### END DO NOT TOUCH!!!! #################
################# MODIFIED ZEB CTs ###################



############### START DO NOT TOUCH!!!! #################
#################### MODIFIED 43 ZEB CTs ######################## 


# Let us now make zeb.df. 
# num_col = # CTs (43); num_rows = # of qualified.ciona.khids.
```{r include=TRUE}
# length(zeb_cell_type_list)- keep below
num.zeb.df.cols <- length(zeb_cell_type_list)
# Because this is the number of Ciona khids. length(qualified.ciona.khids)- change below
num.zeb.df.rows <- length(qualified.ciona.khids)
# 3140 x 43 
zeb.df <- data.frame(matrix(, nrow=num.zeb.df.rows, ncol=num.zeb.df.cols))
```

# Get colnames that correspond to various Zeb CTs.
```{r include=TRUE}
zeb.df.colnames <- names(zeb_cell_type_list)
colnames(zeb.df) <- zeb.df.colnames
```

# Get rownames that represent mapping.
```{r include=TRUE}
# I discovered that there were 2 zeb_genes (ube2c_2 and rpl37_2) that mapped to 2 different khids that were 
# labeled as 1-1. Their names are munged here.

zeb.df.rownames <- c()
# seen.zeb.rownames <- c()

for (i in 1:length(one2one.many.list)) {
  khid <- names(one2one.many.list)[i]
  cat("khid = ", khid, "\n\n")
  
  zeb.names <- one2one.many.list[[i]][[1]]
  # cat(zeb.names, "\n\n")
  
  zeb.name.string <- paste(zeb.names, collapse = "_")
  # cat("zeb name string = ", zeb.name.string, "\n\n")
  
  if (zeb.name.string %in% zeb.df.rownames) {
    # cat("PROBLEM zeb name string = ", zeb.name.string, "\n\n")
    
    # Add _2 to seen.zeb.rownames to avoid redundant rowname conflicts. 
    zeb.name.string <- paste(zeb.name.string, "2", sep = "_")
    # seen.zeb.rownames <- c(seen.zeb.rownames, zeb.name.string)

  }
  zeb.df.rownames <- c(zeb.df.rownames, zeb.name.string)
}

# Modify zeb.df with these rownames. 
rownames(zeb.df) <- zeb.df.rownames
```

# Make average expression dataframe.
```{r include=TRUE}
# For each Zeb CT
for (i in 1:length(zeb_cell_type_list)) {
  zeb.CT.name <- names(zeb_cell_type_list)[i]
  # Get its cells. 
  zeb.cells <- zeb_cell_type_list[[i]]
  zeb.length <- length(zeb.cells)
  cat("Zeb CT = ", zeb.CT.name, "\n", zeb.length)
  
  # Get 1-1/1-many zeb genes.
  for (j in 1:length(one2one.many.list)) {
    cat("i = ", i, "j = ", j, "\n\n")
    one.many.zeb.genes <- one2one.many.list[[j]][[1]]
    
    # Subset Zeb Data based on these genes.
    zeb.sub <- zeb_data[one.many.zeb.genes, zeb.cells]
    
    # Get Average Expression.
    zeb.av <- sum(zeb.sub)/zeb.length
    # Add to correct entry. 
    zeb.df[j, i] <- zeb.av
  }
}
```

# Zeb Average Expression Matrix
```{r include=TRUE}
zeb.avexp.df <- zeb.df
```

############### END DO NOT TOUCH!!!! #################
#################### 43 ZEB CTs ######################## 

# Only heart_52 is f*** up. 
# So I'm just going to do the hacky thing of calculating it separately
# and then modifying zeb.avexp.df 

####################### START FIX HEART 52! ######################

```{r include=TRUE}
fixed.heart.zeb.df.dummy.col <- rep(0, length(qualified.ciona.khids))
fixed.heart.zeb.df <- data.frame("heart_52" = fixed.heart.zeb.df.dummy.col)

fixed.heart.zeb.cells <- zeb_cell_type_list$heart_52
fixed.heart.length <- length(fixed.heart.zeb.cells)

# For each KHID
for (j in 1:length(one2one.many.list)) {
  cat("i = ", i, "j = ", j, "\n\n")

# Get its zeb orthologs. 
  fixed.heart.one.many.zeb.genes <- one2one.many.list[[j]][[1]]

# Subset Zeb Data based on these zeb orthologs.
fixed.heart.zeb.sub <- zeb_data[fixed.heart.one.many.zeb.genes, fixed.heart.zeb.cells]
# Get Average Expression.
fixed.heart.zeb.av <- sum(fixed.heart.zeb.sub)/fixed.heart.length
# Add to correct entry. 
fixed.heart.zeb.df[j, 1] <- fixed.heart.zeb.av
}
```

# Get the Average Expression values for heart_52 (fixed.heart.zeb.column)
```{r include=TRUE}
# Correct! 
fixed.heart.zeb.df
# We want its values.
fixed.heart.zeb.column <- fixed.heart.zeb.df$heart_52
```

# Replace heart_52 column in zeb.avexp.df
```{r include=TRUE}
zeb.avexp.df$heart_52 <- fixed.heart.zeb.column
```

####################### END FIX HEART 52! ######################

"""
(4) Make the GSM Dataframes, ciona/zeb_gsm_v4
"""
```{r include=FALSE}
ciona.gsm <- make_gene_specificity_matrix(ciona.avexp.df)
rownames(ciona.gsm) <- rownames(ciona.avexp.df)
```

```{r include=TRUE}
zeb.gsm <- make_gene_specificity_matrix(zeb.avexp.df)
rownames(zeb.gsm) <- rownames(zeb.avexp.df)
```

# Modified
```{r include=TRUE}
mod.zeb.gsm <- make_gene_specificity_matrix(mod.zeb.avexp.df)
rownames(mod.zeb.gsm) <- rownames(mod.zeb.avexp.df)
```

# Both: Problem is that there are 2 notos! 
```{r include=TRUE}
ciona.mod.zeb.gsm <- cbind(ciona.gsm, mod.zeb.gsm)
cmz.colnames <- colnames(ciona.mod.zeb.gsm)
cmz.replace <- c(paste("ciona_", (cmz.colnames[1:7])), "zeb_noto", cmz.colnames[9:length(cmz.colnames)])
colnames(ciona.mod.zeb.gsm) <- cmz.replace
```

# THIS IS SO VERY HACKY- BECAUSE THERE'S AN OVERLAP IN VARIABLE NAME WITH BRAINMAP #
```{r include=TRUE}
CT.ciona.mod.zeb.gsm <- ciona.mod.zeb.gsm
```

# Can only 1-many genes recapitulate these heatmaps?
```{r include=TRUE}
many.zeb.rows <- rownames(zeb.gsm)
many.zeb.grep <- grepl("_", many.zeb.rows)

many.zeb.gsm <- zeb.gsm[many.zeb.grep, ]
many.ciona.gsm <- ciona.gsm[many.zeb.grep, ]
```

### Pipeline 1: Adjusted p_vals, Visualizes significant p_vals.
# Uses psych::corr.test
"""
(5.1) Use corr.test to make Correlation and P-Value Matrices.
"""
```{r include=TRUE}
corR.output <- corr.test(x= zeb.gsm,
                         y = zeb.gsm,
                         method = "spearman",
                         adjust = "fdr")
```

```{r include=TRUE}
corR.mat <- corR.output$r
corR.pval.mat <- corR.output$p 
```

# Mod
```{r include=TRUE}
mod.corR.output <- corr.test(x= ciona.gsm,
                         y = mod.zeb.gsm,
                         method = "spearman",
                         adjust = "fdr")
```

```{r include=TRUE}
mod.corR.mat <- mod.corR.output$r
mod.corR.pval.mat <- mod.corR.output$p 
```

# Both
```{r include=TRUE}
CT.ciona.mod.zeb.corR.output <- corr.test(x= CT.ciona.mod.zeb.gsm,
                         y = CT.ciona.mod.zeb.gsm,
                         method = "spearman",
                         adjust = "fdr")
```

```{r include=TRUE}
CT.ciona.mod.zeb.corR.mat <- CT.ciona.mod.zeb.corR.output$r
CT.ciona.mod.zeb.corR.pval.mat <- CT.ciona.mod.zeb.corR.output$p 
```

"""
(5.2) Visualize.
"""
# SPECIFY #
```{r include=TRUE}
your.corR.mat <- CT.ciona.mod.zeb.corR.mat
your.corR.pval.mat <- CT.ciona.mod.zeb.corR.pval.mat
```

# Parameters.
```{r include=TRUE}
# Corr legend range. 
# min(corR.mat)
min.index <- min(your.corR.mat)
# max(corR.mat)
max.index <- max(your.corR.mat)
leeway <- 0.01
limits <- c(min.index-leeway, max.index+leeway)

# Aesthetics and labels. 
your.title <- "Similarity Matrix for Ciona and Zebrafish CTs"
your.xlab <- "Ciona + Zeb 24hpf"
your.ylab <- "Ciona + Zeb 24hpf"
your.fill <- "Corr"
#4388F0, 42B5DD
your.color <- "#56B273"
your.face <- "bold"
```

```{r include=TRUE}
p <- ggcorrplot(corr = your.corR.mat,
           p.mat = your.corR.pval.mat)
```

```{r include=TRUE}
p + scale_fill_gradient2(limit = limits,
                          low = "#4C7CC4", mid = "white", high = "#BE1E0B") +
  
  ggplot2::labs(x = your.xlab, y = your.ylab, title = your.title, fill = your.fill) +
  
  ggplot2::theme(plot.title = element_text(size = 10, color = your.color, face = your.face),
                 axis.title.x = element_text(angle = 0, color = your.color, face = your.face),
                 axis.title.y = element_text(angle = 90, color = your.color, face = your.face),
                 axis.text.x = element_text(angle=45, color="black", size=10),
                 axis.text.y = element_text(angle=45, color="black", size=10),
                 legend.title = element_text(color = your.color, size = 9),
                 legend.text = element_text(size = 9)
  )
```


"""
(5.3) (a) Get # Significant Correlations. 
      (b) Get Significance between zeb_CT and ciona_CT
"""

# CHANGE zeb.gsm/mod.zeb.gsm #
```{r include=TRUE}
num.sig <- sum(your.corR.pval.mat < 0.05)
num.sig

# zeb.gsm/mod.zeb.gsm
num.CTs <- ncol(ciona.mod.zeb.gsm)*ncol(ciona.mod.zeb.gsm)
num.CTs
perc.sig <- num.sig/num.CTs*100
perc.sig
```

##### Part 2: TF SMG ANALYSES #####
"""
Various lists for TF and SMG filtering
"""

# TF List 1: Nitta 2019 (SELEX Project)

# TO DO: Clean up the dataframe, not just get gene names. 
```{r include=TRUE}
ciona.tf.dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/ciona_regulatory_regions/unmunged_ciona_TFs.csv"

ciona.tf.df <- read.table(ciona.tf.dir,
                          sep = ",",
                          stringsAsFactors = FALSE,
                          header = TRUE)

# Important Variable (964 Nitta TFs)
ciona.tfs <- ciona.tf.df$KH.model.ID
ciona.tfs <- ciona.tfs[!ciona.tfs == ""]
ciona.tfs <- paste("KH2012:", ciona.tfs, sep = "")
```

# Aniseed Human Ortholog File
```{r include=TRUE}
khid.human.ortho.dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/lifechanging_aniseed_files/ANISEED-Cirobu-GeneName-3bestBlastHitHuman.rnames"

# 26426
khid.human.ortho.df <- read.table(khid.human.ortho.dir,
                                  sep = "\t",
                                  stringsAsFactors = FALSE,
                                  header = TRUE)
```

"""
How many of these 1-1 DEG Orthologs are TFs?
"""

# KHID and Zeb Names
```{r include=TRUE}
ciona.tf.indices <- which(qualified_ciona_khids %in% ciona.tfs)

# What are their names?
qual.ciona.tfs <- qualified_ciona_khids[ciona.tf.indices]
qual.zeb.tfs <- qualified_zeb_genes[ciona.tf.indices]

cat(qual.ciona.tfs, sep="\n")
cat("\n")
cat(qual.zeb.tfs, sep="\n")
```
# Human Orthologs 
```{r include=TRUE}
qual.human.tfs <- khid.human.ortho.df[khid.human.ortho.df$Gene.ID %in% qual.ciona.tfs, ]
qual.human.tfs
```
# Print Results. 
```{r include=TRUE}
khid.names <- qual.human.tfs$Gene.ID
khid.human.names <- qual.human.tfs$Gene.Name

for (i in 1:length(khid.names)) {
  my.name <- khid.names[i]
  my.human.name <- khid.human.names[i]
  
  cat(my.name, "=", my.human.name, "\n")
}
```
"""
Analyses using Kai's files.
"""
# TF and SMG List: Kai (Ghost Curation)
```{r include=TRUE}
kai.tf.smg.dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/ciona_regulatory_regions/kai_tf_smg_list.csv"

kai.tf.smg.df <- read.table(kai.tf.smg.dir,
                            sep = ",",
                            header = TRUE,
                            stringsAsFactors = FALSE)
```

# Munge KHIDs.
```{r include=TRUE}
add.kh.tag <- function(kh.name) {
  full.kh.name <- paste0("KH2012:", kh.name)
  return(full.kh.name)
}

new.col <- as.data.frame(sapply(kai.tf.smg.df[, 1], add.kh.tag))
colnames(new.col) <- "KH.gene.model"
kai.tf.smg.df[, 1] <- new.col 

# Important Variable (1023 Kai TF/SMGs)
all.kai.genes <- as.vector(kai.tf.smg.df$KH.gene.model)
```

# Which 1-1 DEG Orthologs are TF/SMGs?
```{r include=TRUE}
kai.filtered.df <- kai.tf.smg.df %>% filter(KH.gene.model %in% qualified_ciona_khids)
```

# Print Results 
```{r include=TRUE}
# Kai genes are filtered (within 1-1 DEG Ortholog List) NOT ALL KAI GENES
kai.genes <- as.vector(kai.filtered.df$KH.gene.model)
kai.gene.names <- kai.filtered.df$Ghost.Name
kai.class <- kai.filtered.df$Ghost.class

for (i in 1:length(kai.genes)) {
  my.gene <- kai.genes[i]
  my.gene.name <- kai.gene.names[i]
  my.class <- kai.class[i]
  
  cat(my.gene, "=", my.gene.name, "(", my.class, ")","\n")
}
```
# Quick Utility to get ciona khid and zeb gene names for kai.genes
```{r include=TRUE}
# Tells you INDICES of 1-1 ciona khids that are kai genes.
kai.gene.indices <- which(qualified_ciona_khids %in% kai.genes)

# These tell you which 1-1 ciona khids are kai genes. 
kai.ciona.genes <- qualified_ciona_khids[kai.gene.indices]
kai.zeb.genes <- qualified_zeb_genes[kai.gene.indices]
```

##### Part 3: GENE LIST ANALYSES #####
"""
Start For Individual CT Analyses (Re-Analyses)
"""
# CHANGE directories for individual CTs.
```{r include=TRUE}
ciona.CT.dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/1_CURRENT/one2one_larva_24hpf/logFC_0/24hpf_2hearts_gene_analyses/2CT_analyses/larva_noto_24hpf_noto_analyses/larva_noto_24hpf_noto_DEG_logFC0_khids.csv"

zeb.CT.dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/1_CURRENT/one2one_larva_24hpf/logFC_0/24hpf_2hearts_gene_analyses/2CT_analyses/larva_noto_24hpf_noto_analyses/larva_noto_24hpf_noto_DEG_logFC0_zebgenes.csv"

ciona.CT.df <- read.table(ciona.CT.dir,
                          sep =",",
                          header = FALSE,
                          stringsAsFactors = FALSE)

zeb.CT.df <- read.table(zeb.CT.dir,
                          sep =",",
                          header = FALSE,
                          stringsAsFactors = FALSE)

ciona.CT.genes <- ciona.CT.df$V1
zeb.CT.genes <- zeb.CT.df$V1

length(ciona.CT.genes)
```

# Nitta and Kai Filtering for individual CTs. 
(Can use below in Visualizations as ciona_genes and zeb_genes)
```{r include=TRUE}
# Which of these are Nitta TFs?
ciona.CT.nitta.indices <- which(ciona.CT.genes %in% ciona.tfs)
ciona.CT.nitta <- ciona.CT.genes[ciona.CT.nitta.indices]
length(ciona.CT.nitta)

# Which of these are Kai TF SMGs?
ciona.CT.kai.indices <- which(ciona.CT.genes %in% kai.genes)
ciona.CT.kai <- ciona.CT.genes[ciona.CT.kai.indices]
length(ciona.CT.kai)
```

# Get Human Orthologs for individual CTs.
# CHANGE filtered.genes = ciona.CT.nitta/kai
```{r include=TRUE}
filtered.genes <- ciona.CT.kai
filtered.genes
cat("\n\n")
  
# Dataframe: KHID, Human Ortholog
filtered.human.khids <- khid.human.ortho.df[khid.human.ortho.df$Gene.ID %in% filtered.genes, ]
filtered.names <- filtered.human.khids$Gene.Name

filtered.names
cat("\n\n")

filtered.human.khids
```


"""
End For Individual CT Analyses (Re-Analyses)
"""

"""""""
Part 3: What are the highly expressed genes here?
Note: All Analyses below pertain to logFC>0. 

(1) Pick Genes:
a) all 1-1 DEG Orthologs (2466)
qualified_ciona_khids, qualified_zeb_genes
Correlation of 2466 1-1 DEG Orthologs

b) Nitta filtering (235) 
qual.ciona.tfs, qual.zeb.tfs
Correlation of Nitta TFs

c) Kai filtering (197)
kai.ciona.genes, kai.zeb.genes
Correlation of Kai TF and SMGs

d) For individual CTs
ciona.CT.genes, zeb.CT.genes
(would have been defined before) filtered.genes <- ciona.CT.nitta, ciona.CT.kai

(2) Pick pairs of CTs
ciona.CT, zeb.CT

""""""""

# Specify Genes and CTs.
```{r include=TRUE}
# Change
ciona.CT <- "noto"
zeb.CT <- "noto"
ciona_genes <- ciona.CT.genes
zeb_genes <- zeb.CT.genes

ciona.CT.av.exp <- ciona_gsm_v4[ciona_genes, ciona.CT]
zeb.CT.av.exp <- zeb_gsm_v4[zeb_genes, zeb.CT]

scatter.df <- data.frame(ciona.CT = ciona.CT.av.exp,
                         zeb.CT = zeb.CT.av.exp,
                         khid = ciona_genes,
                         zeb.genes = zeb_genes)

zeb.noto <- "zeb_noto"
colnames(scatter.df)[1:2] <- c(ciona.CT, zeb.noto)
```

(3) Visualize
```{r include=TRUE}
# Change
your.title <- "Correlation of CT 1-1 DEG Orthologs"
your.av.exp.cutoff.ciona <- 1
your.av.exp.cutoff.zeb <- 1

new.labels <- gsub("KH2012:KH.", "", ciona_genes)
 
scatter.plot <- ggplot(scatter.df,
                       aes(x = ciona.CT.av.exp, y = zeb.CT.av.exp)) +
                       geom_point() + 
  
                       geom_text(size=2.5, hjust=0, vjust=0, angle=0, aes(label = ifelse(ciona.CT.av.exp>your.av.exp.cutoff.ciona & zeb.CT.av.exp>your.av.exp.cutoff.zeb, as.character(new.labels), ""))) +
  
  ggtitle(your.title) +
  xlab(ciona.CT) +
  ylab(zeb.CT) +
  geom_abline()

scatter.plot
```

(4) Get the Human Orthologs of above KHIDs. (Manually Curated from Scatter Plot)
```{r include=TRUE}
res.ciona.khids <- c("C5.525", "C5.1", "L171.10", "C3.308")

res.ciona.khids <- paste0("KH2012:KH.", res.ciona.khids)

# Dataframe: KHID, Human Ortholog
res.human.khids <- khid.human.ortho.df[khid.human.ortho.df$Gene.ID %in% res.ciona.khids, ]

res.names <- res.human.khids$Gene.Name
res.names
```

# Interactive Scatter Plot
```{r include=TRUE}
# x = ciona.CT.av.exp, y = zeb.CT.av.exp
fig <- plot_ly(type = "scatter", scatter.df, x = ~noto, y = ~zeb_noto, text = ~khid)

fig
```

(4) Get the Human Orthologs of above KHIDs. (Manually Curated from Interactive Scatter Plot)
```{r include=TRUE}
my.genes <- c("KH2012:KH.C14.310")
my.genes
cat("\n\n")
  
# Dataframe: KHID, Human Ortholog
my.human.khids <- khid.human.ortho.df[khid.human.ortho.df$Gene.ID %in% my.genes, ]
my.names <- my.human.khids$Gene.Name

my.names
cat("\n\n")

my.human.khids
```


















### Unused below

# test.one2one.many.list
```{r include=TRUE}
test.one2one.many.list <- list("A" = list(c("C")),
                               "B" = list(c("D", "E")))
num.khids
```

# Test list of cell names
```{r include=TRUE}
# ~ciona/zeb_cell_type_list
test.ciona_cell_type_list <- list("N" = c("n1", "n2", "n3"),
                                  "P" = c("p1", "p2", "p3", "p4"))

test.zeb.cell.type.list <- list("J" = c("j1", "j2", "j3"),
                                "K" = c("k1", "k2"))
```

# Test gene x cells matrix
```{r include=TRUE}
# ~ciona/zeb_data (full raw counts).
# A -> C
# B -> D, E
test.ciona_data <- data.frame("n1" = c(0, 7),
                         "n2" = c(1, 8),
                         "n3" = c(2, 9),
                         "p1" = c(3, 10),
                         "p2" = c(4, 11),
                         "p3" = c(5, 12),
                         "p4" = c(6, 13))
rownames(test.ciona_data) <- c("A", "B")

test.zeb.data <- data.frame("j1" = c(0, 5, 10),
                       "j2" = c(1, 6, 11),
                       "j3" = c(2, 7, 12),
                       "k1" = c(3, 8, 13),
                       "k2" = c(4, 9, 14))
rownames(test.zeb.data) <- c("C", "D", "E")
```

# Make dummy df whose length is that of the number of ciona genes
```{r include=TRUE}
test.qualified.ciona.khids <- names(test.one2one.many.list)

test.ciona.dummy.col <- rep(0, length(test.qualified.ciona.khids))
test.ciona.df <- data.frame("test.ciona.dummy" = test.ciona.dummy.col)
```

# Make Ciona Average Expression Matrix
```{r include=TRUE}

for (i in 1:length(test.ciona_cell_type_list)) {
  test.ciona.CT <- test.qualified.ciona.khids[i]
  cat("test ciona CT = ", test.ciona.CT, "\n\n")
  test.ciona.cells <- test.ciona_cell_type_list[[i]]
  
  test.ciona_data.pre <- test.ciona_data[test.qualified.ciona.khids, test.ciona.cells]
  test.ciona_data.df <- as.data.frame(test.ciona_data.pre)
  
  test.ciona.row <- rowMeans(test.ciona_data.df)
  test.ciona.df <- cbind(test.ciona.df, test.ciona.row)
}

test.ciona.df <- subset(test.ciona.df, select=-(test.ciona.dummy))

test.ciona.colnames <- names(test.ciona_cell_type_list)
colnames(test.ciona.df) <- test.ciona.colnames

test.ciona.avexp.df <- test.ciona.df
```

```{r include=TRUE}
test.num.zeb.df.cols <- length(test.zeb.cell.type.list)
# Because this is the number of Ciona khids.
test.num.zeb.df.rows <- length(test.one2one.many.list)

test.zeb.df <- data.frame(matrix(, nrow=test.num.zeb.df.rows, ncol=test.num.zeb.df.cols))
```

# Get colnames that correspond to various Zeb CTs and rownames that represent mapping
```{r include=TRUE}
test.zeb.df.colnames <- names(test.zeb.cell.type.list) 

test.zeb.df.rownames <- c()
for (i in 1:length(test.one2one.many.list)) {
  test.zeb.names <- test.one2one.many.list[[i]][[1]]
  test.zeb.name.string <- paste(test.zeb.names, collapse="")
  test.zeb.df.rownames <- c(test.zeb.df.rownames, test.zeb.name.string)
}

colnames(test.zeb.df) <- test.zeb.df.colnames
rownames(test.zeb.df) <- test.zeb.df.rownames
```

```{r include=TRUE}
# For each Zeb CT
for (i in 1:length(test.zeb.cell.type.list)) {
  test.zeb.CT.name <- names(test.zeb.cell.type.list)[i]
  # Get its cells. 
  test.zeb.cells <- test.zeb.cell.type.list[[i]]
  test.length <- length(test.zeb.cells)
  cat("Zeb CT = ", test.zeb.CT.name, test.length, "\n")
  # Get 1-1/1-many zeb genes
  for (j in 1:length(test.one2one.many.list)) {
    test.one.many.zeb.genes <- test.one2one.many.list[[j]][[1]]
    # Subset Zeb Data based on these genes.
    test.zeb.sub <- test.zeb.data[test.one.many.zeb.genes, test.zeb.cells]
    # Get Average Expression.
    test.zeb.av <- sum(test.zeb.sub)/length(test.zeb.cells)
    # Add to correct entry. 
    test.zeb.df[j, i] <- test.zeb.av
  }
}
test.zeb.avexp.df <- test.zeb.df
```

# Getting the right format
# Read in csv to make dataframe where rownames/1st column are KHIDs
# Second column is string of many zeb genes
```{r include=TRUE}
test <- "a b 3"
test.2 <- strsplit(test, " ")
class(test.2)
# 
# test.2 <- test.2[[1]]
# test.2
# class(test.2)

test.3 <- "d e"
test.4 <- strsplit(test.3, " ")
# test.4 <- test.4[[1]]

test.row <- c(1, 2, 3)
test.rownames <- c("A", "B", "C")

test.df <- data.frame("A" = c(1, 2, 3))
test.df[1, 1] <- test
test.df[2, 1] <- test.3
rownames(test.df) <- test.rownames

# Read and munge in csv to make a dataframe with 2 columns 
# col.1 <- khid, col.2 = zeb_gene_string e.g. "a b c" or "a"
```

# Df -> master.list = {key : list of strings}
```{r include=TRUE}
# {A: ["a", "b, "c"], B: ["d"]} where A/B=khid; "a", "b", "c" m_zeb_genes/"d" o_zeb_gene
test.list <- list()

num.rows <- dim(test.df)[1]
for (i in 1:num.rows) {
  key <- rownames(test.df)[i]
  value <- test.df[i, 1]
  value <- strsplit(value, " ")
  test.list[[key]] <- value
}
```

```{r include=TRUE}
for (i in 1:length(test.list)) {
  value <- test.list[[i]][[1]]
  cat(paste(value, collapse = ""))
  cat("\n\n")
}
```
