---
title: "orthology_maps_data_inputs"
output: html_document
---

# Purpose of Notebook
# Import all data needed for Orthology Maps Projects

# Material for initial 24hpf clustering from Klein data is kept.
# Copy of it Transferred to zeb_24hpf_clustering.Rmd

## (Zebrafish) Klein : 4, 6, 8, 10, 14, 18, 24 hpf

## (Zebrafish) Schier: 
1) 30% epiboly (2)
2) 3-somite (1, 3)
3) 50% epiboly (4, 7)
4) 60% epiboly (3, 10)
5) 6-somite (2, 12)
6) 75% epiboly (3, 15)
7) 90% epiboly (3, 18)
8) bud (4, 22)
9) dome (1, 23)
10) high (2, 25)
11) oblong (2, 27)
12 (shield, 1, 28)

## Ciona
# iniG, midG, earN, latN, iniT1, earT1, midT2, latT1, latT2, larva

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=TRUE}
library(Seurat)
library(dplyr)
library(ggplot2)
library(purrr)
library(Hmisc)
library(pvclust)
```

############  KLEIN ZEBRAFISH ######### 

# Extract individual Raw UMI-filtered counts (csv). Example below. 
# https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSM3067195
# GSM3067195_24hpf.csv.gz

# [LOC100000009 x DEW050_GTCTCTCT_AGGAGCTT]
# 30677 x *
```{r include=TRUE}
zeb_4hpf_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/Klein_2018/GSM3067189_04hpf.csv" 
# 4278
zeb_4hpf_df <- read.table(zeb_4hpf_dir,
                          sep = ",",
                          header = TRUE,
                          stringsAsFactors = FALSE,
                          row.names = 1)

zeb_6hpf_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/Klein_2018/GSM3067190_06hpf.csv" 
# 5693
zeb_6hpf_df <- read.table(zeb_6hpf_dir,
                          sep = ",",
                          header = TRUE,
                          stringsAsFactors = FALSE)

zeb_8hpf_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/Klein_2018/GSM3067191_08hpf.csv" 
# 3569
zeb_8hpf_df <- read.table(zeb_8hpf_dir,
                          sep = ",",
                          header = TRUE,
                          stringsAsFactors = FALSE)

zeb_10hpf_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/Klein_2018/GSM3067192_10hpf.csv" 
# 4281
zeb_10hpf_df <- read.table(zeb_10hpf_dir,
                          sep = ",",
                          header = TRUE,
                          stringsAsFactors = FALSE)

zeb_14hpf_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/Klein_2018/GSM3067193_14hpf.csv" 
# 4002
zeb_14hpf_df <- read.table(zeb_14hpf_dir,
                          sep = ",",
                          header = TRUE,
                          stringsAsFactors = FALSE)

zeb_18hpf_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/Klein_2018/GSM3067194_18hpf.csv" 
# 6963
zeb_18hpf_df <- read.table(zeb_18hpf_dir,
                          sep = ",",
                          header = TRUE,
                          stringsAsFactors = FALSE)

zeb_24hpf_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/Klein_2018/GSM3067195_24hpf.csv" 
# 7970
zeb_24hpf_df <- read.table(zeb_24hpf_dir,
                          sep = ",",
                          header = TRUE,
                          stringsAsFactors = FALSE)
```

############  SCHIER ZEBRAFISH ######### 

# Data from:
# https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE106474
# GSE106474_UMICounts.txt.gz

# [A1CF x ZFDOME_WT_DS5_CGGACCGCAGGT]
# 23974 x *
```{r include=TRUE}
schier_all_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/Schier_2018/GSE106474_UMICounts.txt"

schier_all_df <- read.table(schier_all_dir,
                            header = TRUE,
                            sep = "\t",
                            stringsAsFactors = FALSE)
```

# Dimnames is a list
# Set rownames and colnames
```{r include=TRUE}
rows <- dimnames(schier_all_df)[[1]]
cols <- dimnames(schier_all_df)[[2]]

rownames(schier_all_df) <- rows
colnames(schier_all_df) <- cols
```

# Let's get all the unique names for stages
```{r include=TRUE}
all_schier_colnames <- unique(unlist(strsplit(colnames(schier_all_df), "_")))
schier_stage_names <- all_schier_colnames[grepl("ZF", all_schier_colnames)]
```

# 12 stages Dataframes 
```{r include=TRUE}
all_rownames <- rownames(ZFHIGH_df)

# 1 311
ZFHIGH_df <- select(schier_all_df, contains("ZFHIGH"))
colnames(ZFHIGH_df) <- dimnames(ZFHIGH_df)[[2]]

# 2 200
ZFOBLONG_df <- select(schier_all_df, contains("ZFOBLONG"))
rownames(ZFOBLONG_df) <- all_rownames
colnames(ZFOBLONG_df) <- dimnames(ZFOBLONG_df)[[2]]

# 3 1174
ZFDOME_df <- select(schier_all_df, contains("ZFDOME"))
rownames(ZFDOME_df) <- all_rownames
colnames(ZFDOME_df) <- dimnames(ZFDOME_df)[[2]]

# 4 1506
ZF30_df <- select(schier_all_df, contains("ZF30"))
rownames(ZF30_df) <- all_rownames
colnames(ZF30_df) <- dimnames(ZF30_df)[[2]]

# 5 5864 
ZF50_df <- select(schier_all_df, contains("ZF50"))
rownames(ZF50_df) <- all_rownames
colnames(ZF50_df) <- dimnames(ZF50_df)[[2]]

# 6 1046
ZFS_df <- select(schier_all_df, contains("ZFS"))
rownames(ZFS_df) <- all_rownames
colnames(ZFS_df) <- dimnames(ZFS_df)[[2]]

# 7 4201
ZF60_df <- select(schier_all_df, contains("ZF60"))
rownames(ZF60_df) <- all_rownames
colnames(ZF60_df) <- dimnames(ZF60_df)[[2]]

# 8 6324
ZF75_df <- select(schier_all_df, contains("ZF75"))
rownames(ZF75_df) <- all_rownames
colnames(ZF75_df) <- dimnames(ZF75_df)[[2]]

# 9 5626
ZF90_df <- select(schier_all_df, contains("ZF90"))
rownames(ZF90_df) <- all_rownames
colnames(ZF90_df) <- dimnames(ZF90_df)[[2]]

# 10 7162
ZFB_df <- select(schier_all_df, contains("ZFB"))
rownames(ZFB_df) <- all_rownames
colnames(ZFB_df) <- dimnames(ZFB_df)[[2]]

# 11 1631
ZF3S_df <- select(schier_all_df, contains("ZF3S"))
rownames(ZF3S_df) <- all_rownames
colnames(ZF3S_df) <- dimnames(ZF3S_df)[[2]]

# 12 4460
ZF6S_df <- select(schier_all_df, contains("ZF6S"))
rownames(ZF6S_df) <- all_rownames
colnames(ZF6S_df) <- dimnames(ZF6S_df)[[2]]
```


#########   CIONA   ######### 
# All 15269 x 737280
# iniG
```{r include=TRUE}
# 1
iniG1_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764764_iniG1_raw_gene_bc_matrices_h5.h5"
iniG1_matrix <- Read10X_h5(iniG1_dir)

# 2
iniG2_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764765_iniG2_raw_gene_bc_matrices_h5.h5"
iniG2_matrix <- Read10X_h5(iniG2_dir)
```

# midG
```{r include=TRUE}
# 3
midG1_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764766_midG1_raw_gene_bc_matrices_h5.h5"
midG1_matrix <- Read10X_h5(midG1_dir)

# 4
midG2_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764767_midG2_raw_gene_bc_matrices_h5.h5"
midG2_matrix <- Read10X_h5(midG2_dir)
```

# earN
```{r include=TRUE}
# 5
earN1_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764768_earN1_raw_gene_bc_matrices_h5.h5"
earN1_matrix <- Read10X_h5(earN1_dir)

# 6
earN2_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764769_earN2_raw_gene_bc_matrices_h5.h5"
earN2_matrix <- Read10X_h5(earN2_dir)
```

# latN
```{r include=TRUE}
# 7
latN1_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764770_latN1_raw_gene_bc_matrices_h5.h5"
latN1_matrix <- Read10X_h5(latN1_dir)

# 8
latN2_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764771_latN2_raw_gene_bc_matrices_h5.h5"
latN2_matrix <- Read10X_h5(latN2_dir)
```

# iniT1
```{r include=TRUE}
# 9
iniTI1_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764772_iniTI1_raw_gene_bc_matrices_h5.h5"
iniTI1_matrix <- Read10X_h5(iniTI1_dir)

# 10
iniTI2_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764773_iniTI2_raw_gene_bc_matrices_h5.h5"
iniTI2_matrix <- Read10X_h5(iniTI2_dir)
```

# earT1
```{r include=TRUE}
# 11
earTI1_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764774_earTI1_raw_gene_bc_matrices_h5.h5"
earTI1_matrix <- Read10X_h5(earTI1_dir)

# 12
earTI2_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764775_earTI2_raw_gene_bc_matrices_h5.h5"
earTI2_matrix <- Read10X_h5(earTI2_dir)
```

# midT2
```{r include=TRUE}
# 13
midTII1_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764776_midTII1_raw_gene_bc_matrices_h5.h5"
midTII1_matrix <- Read10X_h5(midTII1_dir)

# 14
midTII2_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764777_midTII2_raw_gene_bc_matrices_h5.h5"
midTII2_matrix <- Read10X_h5(midTII2_dir)
```

# latT1
```{r include=TRUE}
# 15
latTI1a_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764778_latTI1a_raw_gene_bc_matrices_h5.h5"
latTI1a_matrix <- Read10X_h5(latTI1a_dir)

# 16
latTI1b_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764782_latTII1b_raw_gene_bc_matrices_h5.h5"
latTI1b_matrix <- Read10X_h5(latTI1b_dir)

# 17
latTI2_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764780_latTI2_raw_gene_bc_matrices_h5.h5"
latTI2_matrix <- Read10X_h5(latTI2_dir)
```

GSM3764781_latTII1a_raw_gene_bc_matrices_h5.h5
GSM3764782_latTII1b_raw_gene_bc_matrices_h5.h5
GSM3764783_latTII2_raw_gene_bc_matrices_h5.h5

# latT2
```{r include=TRUE}
# 18
latTII1a_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764781_latTII1a_raw_gene_bc_matrices_h5.h5"
latTII1a_matrix <- Read10X_h5(latTII1a_dir)

# 19
latTII1b_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764782_latTII1b_raw_gene_bc_matrices_h5.h5"
latTII1b_matrix <- Read10X_h5(latTII1b_dir)

# 20
latTII2_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764783_latTII2_raw_gene_bc_matrices_h5.h5"
latTII2_matrix <- Read10X_h5(latTII2_dir)
```

# larva
```{r include=TRUE}
# 21
larva1_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764784_larva1_raw_gene_bc_matrices_h5.h5"
larva1_matrix <- Read10X_h5(larva1_dir)

# 22
larva2_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764785_larva2_raw_gene_bc_matrices_h5.h5"
larva2_matrix <- Read10X_h5(larva2_dir)

# 23
larva3_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/Raw_Data/4D_GSE131155_RAW/GSM3764786_larva3_raw_gene_bc_matrices_h5.h5"
larva3_matrix <- Read10X_h5(larva3_dir)
```


###################################

SCRATCH ZONE

###################################

# Let's get all the unique names for stages
```{r include=TRUE}
all_schier_colnames <- unique(unlist(strsplit(colnames(schier_all_df), "_")))
schier_stage_names <- all_schier_colnames[grepl("ZF", all_schier_colnames)]
```

# 12 stages Dataframes 
```{r include=TRUE}
all_rownames <- rownames(ZFHIGH_df)

# 311
ZFHIGH_df <- select(schier_all_df, contains("ZFHIGH"))
colnames(ZFHIGH_df) <- dimnames(ZFHIGH_df)[[2]]

# 200
ZFOBLONG_df <- select(schier_all_df, contains("ZFOBLONG"))
rownames(ZFOBLONG_df) <- all_rownames
colnames(ZFOBLONG_df) <- dimnames(ZFOBLONG_df)[[2]]

# 1174
ZFDOME_df <- select(schier_all_df, contains("ZFDOME"))
rownames(ZFDOME_df) <- all_rownames
colnames(ZFDOME_df) <- dimnames(ZFDOME_df)[[2]]

# 1506
ZF30_df <- select(schier_all_df, contains("ZF30"))
rownames(ZF30_df) <- all_rownames
colnames(ZF30_df) <- dimnames(ZF30_df)[[2]]

# 5864 
ZF50_df <- select(schier_all_df, contains("ZF50"))
rownames(ZF50_df) <- all_rownames
colnames(ZF50_df) <- dimnames(ZF50_df)[[2]]

# 1046
ZFS_df <- select(schier_all_df, contains("ZFS"))
rownames(ZFS_df) <- all_rownames
colnames(ZFS_df) <- dimnames(ZFS_df)[[2]]

# 4201
ZF60_df <- select(schier_all_df, contains("ZF60"))
rownames(ZF60_df) <- all_rownames
colnames(ZF60_df) <- dimnames(ZF60_df)[[2]]

# 6324
ZF75_df <- select(schier_all_df, contains("ZF75"))
rownames(ZF75_df) <- all_rownames
colnames(ZF75_df) <- dimnames(ZF75_df)[[2]]

# 5626
ZF90_df <- select(schier_all_df, contains("ZF90"))
rownames(ZF90_df) <- all_rownames
colnames(ZF90_df) <- dimnames(ZF90_df)[[2]]

# 7162
ZFB_df <- select(schier_all_df, contains("ZFB"))
rownames(ZFB_df) <- all_rownames
colnames(ZFB_df) <- dimnames(ZFB_df)[[2]]

# 1631
ZF3S_df <- select(schier_all_df, contains("ZF3S"))
rownames(ZF3S_df) <- all_rownames
colnames(ZF3S_df) <- dimnames(ZF3S_df)[[2]]

# 4460
ZF6S_df <- select(schier_all_df, contains("ZF6S"))
rownames(ZF6S_df) <- all_rownames
colnames(ZF6S_df) <- dimnames(ZF6S_df)[[2]]
```


