---
title: "notoXnoto"
output: html_document
---

# Point of this Script:
# (1) Get min_n_features for each timepoint. 
# (2) Save raw matrices in an Renv that will be used in gencomp.
# (3) Also explore outputs of gencomp = Ensure batch correction worked. 
# 
# "DONE 1" means that min_n_features for a timepoint was catalogued in gencomp Rscript
#        to make Seurat object 
#   e.g. anchor_features_num <- 13900notoX in noto_larva_script.R for
#   "notoXnoto_larva_seurat.rds"
#
# "DONE 2" means that Batch Correction was visually validated.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(Seurat)
library(dplyr)
library(ggplot2)
library(purrr)
library(Hmisc)
library(pvclust)
library(stringr)
library(cellranger)
library(Matrix)
```

################### PART 1: Get Chen's Raw 4D Data #######################

# Dims of all matrices 15269 x 737280
# iniG
```{r include=TRUE}
chen_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/Raw_Data/4D_GSE131155_RAW/"
# 1
iniG1_dir <- paste0(chen_dir, "GSM3764764_iniG1_raw_gene_bc_matrices_h5.h5")
iniG1_matrix <- Read10X_h5(iniG1_dir)

iniG2_dir <- paste0(chen_dir, "GSM3764765_iniG2_raw_gene_bc_matrices_h5.h5")
iniG2_matrix <- Read10X_h5(iniG2_dir)
```

# midG
```{r include=TRUE}
# 3
midG1_dir <- paste0(chen_dir, "GSM3764766_midG1_raw_gene_bc_matrices_h5.h5")
midG1_matrix <- Read10X_h5(midG1_dir)

# 4
midG2_dir <- paste0(chen_dir, "GSM3764767_midG2_raw_gene_bc_matrices_h5.h5")
midG2_matrix <- Read10X_h5(midG2_dir)
```

# earN
```{r include=TRUE}
# 5
earN1_dir <- paste0(chen_dir, "GSM3764768_earN1_raw_gene_bc_matrices_h5.h5")
earN1_matrix <- Read10X_h5(earN1_dir)

# 6
earN2_dir <- paste0(chen_dir, "GSM3764769_earN2_raw_gene_bc_matrices_h5.h5")
earN2_matrix <- Read10X_h5(earN2_dir)
```

# latN
```{r include=TRUE}
# 7
latN1_dir <- paste0(chen_dir, "GSM3764770_latN1_raw_gene_bc_matrices_h5.h5")
latN1_matrix <- Read10X_h5(latN1_dir)

# 8
latN2_dir <- paste0(chen_dir, "GSM3764771_latN2_raw_gene_bc_matrices_h5.h5")
latN2_matrix <- Read10X_h5(latN2_dir)
```

# iniT1
```{r include=TRUE}
# 9
iniTI1_dir <- paste0(chen_dir, "GSM3764772_iniTI1_raw_gene_bc_matrices_h5.h5")
iniTI1_matrix <- Read10X_h5(iniTI1_dir)

# 10
iniTI2_dir <- paste0(chen_dir, "GSM3764773_iniTI2_raw_gene_bc_matrices_h5.h5")
iniTI2_matrix <- Read10X_h5(iniTI2_dir)
```

# earT1
```{r include=TRUE}
# 11
earTI1_dir <- paste0(chen_dir, "GSM3764774_earTI1_raw_gene_bc_matrices_h5.h5")
earTI1_matrix <- Read10X_h5(earTI1_dir)

# 12
earTI2_dir <- paste0(chen_dir, "GSM3764775_earTI2_raw_gene_bc_matrices_h5.h5")
earTI2_matrix <- Read10X_h5(earTI2_dir)
```

# midT2
```{r include=TRUE}
# 13
midTII1_dir <- paste0(chen_dir, "GSM3764776_midTII1_raw_gene_bc_matrices_h5.h5")
midTII1_matrix <- Read10X_h5(midTII1_dir)

midTII2_dir <- paste0(chen_dir, "GSM3764777_midTII2_raw_gene_bc_matrices_h5.h5")
midTII2_matrix <- Read10X_h5(midTII2_dir)
```

# latT1
```{r include=TRUE}
# 15
latTI1a_dir <- paste0(chen_dir, "GSM3764778_latTI1a_raw_gene_bc_matrices_h5.h5")
latTI1a_matrix <- Read10X_h5(latTI1a_dir)

# 16
latTI1b_dir <- paste0("/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/Raw_Data/4D_GSE131155_RAW/GSM3764779_latTI1b_raw_gene_bc_matrices_h5.h5")
latTI1b_matrix <- Read10X_h5(latTI1b_dir)

# 17
latTI2_dir <- paste0(chen_dir, "GSM3764780_latTI2_raw_gene_bc_matrices_h5.h5")
latTI2_matrix <- Read10X_h5(latTI2_dir)
```

# latT2
```{r include=TRUE}
# 18
latTII1a_dir <- paste0(chen_dir, "GSM3764781_latTII1a_raw_gene_bc_matrices_h5.h5")
latTII1a_matrix <- Read10X_h5(latTII1a_dir)

# 19
latTII1b_dir <- paste0(chen_dir, "GSM3764782_latTII1b_raw_gene_bc_matrices_h5.h5")
latTII1b_matrix <- Read10X_h5(latTII1b_dir)

# 20
latTII2_dir <- paste0(chen_dir, "GSM3764783_latTII2_raw_gene_bc_matrices_h5.h5")
latTII2_matrix <- Read10X_h5(latTII2_dir)
```

# larva
```{r include=TRUE}
# 21
larva1_dir <- paste0(chen_dir, "GSM3764784_larva1_raw_gene_bc_matrices_h5.h5")
larva1_matrix <- Read10X_h5(larva1_dir)

# 22
larva2_dir <- paste0(chen_dir, "GSM3764785_larva2_raw_gene_bc_matrices_h5.h5")
larva2_matrix <- Read10X_h5(larva2_dir)

# 23
larva3_dir <- paste0(chen_dir, "GSM3764786_larva3_raw_gene_bc_matrices_h5.h5")
larva3_matrix <- Read10X_h5(larva3_dir)
```

"""
(2) Do filtering steps to get number of filtered genes- will be used to determine min_n_features -> anchor_features_num in RScript.
This will be the minimum of filtered genes from all Seurat Objects. 
"""

# Helper Function
```{r include=TRUE}
make_filtered_seurat <- function(raw_matrix, min_cells, min_features) {
  # Filters Seurat Object to get number of filtered features that will be used
  # as number of VariableFeatures for all Seurat Objects to be integrated.
  # e.g. 2 Seurat Objects have 14310 and 12837 filtered features respectively.
  # Downstream, both Seurat Objects will use 12830 n_features in FindVariableFeatures. 
  seurat_object <- CreateSeuratObject(counts = raw_matrix,  
                                    min.cells = min_cells,
                                    min.features =  min_features)
  return(seurat_object)
}
```

# iniG - DONE 1, 2 
```{r include=TRUE}
# 14310 x 68708
iniG1_matrix_seurat <- make_filtered_seurat(iniG1_matrix, 3, 200)
# 12830 x 1422
iniG2_matrix_seurat <- make_filtered_seurat(iniG2_matrix, 3, 200)

# min_n_features <- 12800
```

# midG - DONE 1, 2 
```{r include=TRUE}
# 12869 x 1348
midG1_matrix_seurat <- make_filtered_seurat(midG1_matrix, 3, 200)
# 13694 x 6586
midG2_matrix_seurat <- make_filtered_seurat(midG2_matrix, 3, 200)

# min_n_features <- 12860
```

# earN - DONE 1, 2
```{r include=TRUE}
# 13811 x 2306
earN1_matrix_seurat <- make_filtered_seurat(earN1_matrix, 3, 200)
# 13692 x 6025
earN2_matrix_seurat <- make_filtered_seurat(earN2_matrix, 3, 200)

# min_n_features <- 13690
```

# latN - DONE 1, 2
```{r include=TRUE}
# 14059 x 3941
latN1_matrix_seurat <- make_filtered_seurat(latN1_matrix, 3, 200)
# 13863 x 6117
latN2_matrix_seurat <- make_filtered_seurat(latN2_matrix, 3, 200)

# min_n_features <- 13860
```

# iniTI1
```{r include=TRUE}
# 13857 x 2998
iniTI1_matrix_seurat <- make_filtered_seurat(iniTI1_matrix, 3, 200)
# 13234 x 3957
iniTI2_matrix_seurat <- make_filtered_seurat(iniTI2_matrix, 3, 200)

# min_n_features <- 13230
```

# earT - DONE 1, 2
```{r include=TRUE}
# 13565 x 5578
earTI1_matrix_seurat <- make_filtered_seurat(earTI1_matrix, 3, 200)
# 14129 x 9559
earTI2_matrix_seurat <- make_filtered_seurat(earTI2_matrix, 3, 200)

# min_n_features <- 13560
```

# midT - DONE 1, 2
```{r include=TRUE}
# 14309 x 5398
midTII1_matrix_seurat <- make_filtered_seurat(midTII1_matrix, 3, 200)
# 14066 x 5062
midTII2_matrix_seurat <- make_filtered_seurat(midTII2_matrix, 3, 200)

# min_n_features <- 14060
```

# LTB1 ********* DONE 1, 2
# We want aggregate files for a and b.
```{r include=TRUE}
LTB1_matrix_path <- "/home/pprakriti/Desktop/vera_ciona_notoXnoto/notoXnoto_LTB1/LTB1-aggr"
# 15269 X 15745
LTB1_agg_matrix <- Read10X(LTB1_matrix_path)
```

```{r include=TRUE}
# 14064 x 10057
# latTI1a_matrix_seurat <- make_filtered_seurat(latTI1a_matrix, 3, 200)
# 13938 x 8792
# latTI1b_matrix_seurat <- make_filtered_seurat(latTI1b_matrix, 3, 200)

# 14328 x 5566
latTI2_matrix_seurat <- make_filtered_seurat(latTI2_matrix, 3, 200)

# 14356 x 15676
LTB1_agg_matrix_seurat <- make_filtered_seurat(LTB1_agg_matrix, 3, 200)

# min_n_features <- 14320
```


# LTB2 ********* DONE 1, 2
```{r include=TRUE}
LTB2_matrix_path <- "/home/pprakriti/Desktop/vera_ciona_notoXnoto/notoXnoto_LTB2/LTB2-aggr"
# 15269 x 6883
LTB2_agg_matrix <- Read10X(LTB2_matrix_path)
```

```{r include=TRUE}
# # 13776 x 2756
# latTII1a_matrix_seurat <- make_filtered_seurat(latTII1a_matrix, 3, 200)
# # 14152 x 5593
# latTII1b_matrix_seurat <- make_filtered_seurat(latTII1b_matrix, 3, 200)

# 14446 x 25491
latTII2_matrix_seurat <- make_filtered_seurat(latTII2_matrix, 3, 200)
# 14362 x 6883
LTB2_agg_matrix_seurat <- make_filtered_seurat(LTB2_agg_matrix, 3, 200)

# min_n_features <- 14360
```

# larva - DONE 1, 2
```{r include=TRUE}
# 13933 x 28234
larva1_matrix_seurat <- make_filtered_seurat(larva1_matrix, 3, 200)
# 13907 x 12405
larva2_matrix_seurat <- make_filtered_seurat(larva2_matrix, 3, 200)
# 14067 x 7143
larva3_matrix_seurat <- make_filtered_seurat(larva3_matrix, 3, 200)

# min_n_features <- 13900
```

"""
  Sanity check of RScript (noto_larva_script.R) for Larva 
"""
# RScript run on 11/7/20
```{r include=TRUE}
# 6.9/8.6GB (This is because PCA+UMAP was performed)
notoXnoto_larva_seurat <- readRDS("/home/pprakriti/Desktop/vera_ciona_notoXnoto/notoXnoto_larva.rds")
```

# Compare to Stuff from October (first gencomp batch correction)
```{r include=TRUE}
# 2/3.4GB
gencomp_ciona_batch_seurat <- readRDS("/home/pprakriti/Desktop/orthology_map_batch_correction/vera_batch_correction/ciona/gencomp_ciona_batch_correct_dir/gencomp_ciona_batch_seurat.rds")
```


#########  Test Batch Correction of All Seurat Objects.  ##########
###################  Identify Notochord Cells   #################### 

# List of directories 
```{r include=TRUE}

"/home/pprakriti/Desktop/vera_ciona_notoXnoto/notoXnoto_iniG_DONE/notoXnoto_iniG_seurat.rds"
"/home/pprakriti/Desktop/vera_ciona_notoXnoto/notoXnoto_midG_DONE/notoXnoto_midG_seurat.rds"
"/home/pprakriti/Desktop/vera_ciona_notoXnoto/notoXnoto_earN_DONE/notoXnoto_earN_seurat.rds"
"/home/pprakriti/Desktop/vera_ciona_notoXnoto/notoXnoto_latN_DONE/notoXnoto_latN_seurat.rds"
"/home/pprakriti/Desktop/vera_ciona_notoXnoto/notoXnoto_iniT_DONE/notoXnoto_iniT_seurat.rds"
"/home/pprakriti/Desktop/vera_ciona_notoXnoto/notoXnoto_earT_DONE/notoXnoto_earT_seurat.rds"
"/home/pprakriti/Desktop/vera_ciona_notoXnoto/notoXnoto_midT_DONE/notoXnoto_midT_seurat.rds"
"/home/pprakriti/Desktop/vera_ciona_notoXnoto/notoXnoto_LTB1_DONE/notoXnoto_LTB1_seurat.rds"
"/home/pprakriti/Desktop/vera_ciona_notoXnoto/notoXnoto_LTB2_DONE/notoXnoto_LTB2_seurat.rds"
"/home/pprakriti/Desktop/vera_ciona_notoXnoto/notoXnoto_larva_DONE/notoXnoto_larva_seurat.rds"

```

# (1) Load Seurat - CHANGE THIS!!!
```{r include=TRUE}
ciona_rds <- "/home/pprakriti/Desktop/vera_ciona_notoXnoto/notoXnoto_LTB2_DONE/notoXnoto_LTB2_seurat.rds"
notoXnoto_seurat <- readRDS(ciona_rds)
```

# (2) Check Batch Correction - All validated! 
```{r include=TRUE}
DimPlot(notoXnoto_seurat, 
        reduction = "umap",
        label = TRUE,
        group.by = "batch_name")

```

# (3) Cluster
```{r include=TRUE}
notoXnoto_seurat <- FindNeighbors(notoXnoto_seurat, dims = 1:15)
notoXnoto_seurat <- FindClusters(notoXnoto_seurat, resolution = 1)
```

# (*) Visualize the Clusters 
```{r include=TRUE}
DimPlot(notoXnoto_seurat, 
        reduction = "umap",
        label = TRUE)
```

# (4) Identify Notochord Cells
```{r include=TRUE}
# Early, Extended Data Fig3
# v. strong
bra <- "KH2012:KH.S1404.1"
foxAa <- "KH2012:KH.C11.313"
mnx <- "KH2012:KH.L128.12"

# Extended Data Fig2m
# FBCD1; FGL1; FGL2 v. strong
fibrinogen <- "KH2012:KH.C1.832"
# noto8 <- "KH2012:KH.C11.665"


C110_noto_markers <- c(bra, foxAa, mnx)
ltb_noto_markers <- c("KH2012:KH.C5.124", "KH2012:KH.C8.749")
test_noto_markers <- c("KH2012:KH.C8.293", "KH2012:KH.L18.22", "KH2012:KH.L116.66", "KH2012:KH.L18.117", "KH2012:KH.S643.6")

FeaturePlot(object = notoXnoto_seurat,
            features = c(C110_noto_markers, ltb_noto_markers),
            reduction = "umap",
            label = TRUE)
```
# (*) Validate Clusters using FindMarkers.
```{r include=TRUE}
# CHANGE!!!
notoXnoto_idents <- c(20)
# test_markers <- FindMarkers(notoXnoto_seurat, ident.1 = notoXnoto_idents)
```

"""
  Get relevant Seurat Objects and Data Matrices
"""

# (5) Set notoXnoto_seurat to timepoint Seurat, get data matrix
```{r include=TRUE}
# CHANGE!!!
LTB2_seurat <- notoXnoto_seurat
# CHANGE!!!
LTB2_mat <- notoXnoto_seurat@assays$integrated@data
# CHANGE!!!
LTB2_noto_cells <- WhichCells(notoXnoto_seurat, idents = notoXnoto_idents)
# CHANGE!!!
LTB2_noto_mat <- LTB2_mat[, LTB2_noto_cells]
```

# (6) Record Data in "notoXnoto Progress + Results".


















#######################   I GOT RID OF INIG_SEURAT -> INIG_SUBSET   ###################

```{r include=TRUE}
iniG_subset <- subset(iniG_seurat, ident = c(19, 17, 15, 16, 12, 13, 14, 18, 9, 10))
```

```{r include=TRUE}
DimPlot(iniG_subset, 
        reduction = "umap",
        label = TRUE)
```

######################### UNUSED: EXPLORE CHEN'S NOTOCHORD OBJECT ##########################

# Upload Chen's object.
```{r include=TRUE}
# cells.subcluster
load("/home/pprakriti/Desktop/ciona4D.10stage..noto.allstage.anno.Robj")
```

"""
  Get unique flags = timepoint labels.
  Note: I want to be working with metadata. 
"""

```{r include=TRUE}
get_flag <- function(flag_cell_name, flag=FALSE, cell_name=FALSE) {
  # Gets flag (timepoint of cell) or cell_name.
  #
  # Args: flag_cell. e.g. C110.1_AAAGATGCACCGCTAG
  # Returns: flag. e.g. C110.1 or AAAGATGCACCGCTAG
  output <- strsplit(flag_cell_name, "_")[[1]]
  
  if (flag==TRUE) {
    result <- output[[1]]
  }
  if (cell_name==TRUE) {
    result <- output[[2]]
  }
  return(result)
}
```

# Names of Cells and their Timepoints 
```{r include=TRUE}
ciona_noto_metadata <- cells.subcluster@meta.data
ciona_noto_cell_names <- rownames(ciona_noto_metadata)
# 21 vs 23 (number of input files). This makes sense because Chen combined technical replicates.
ciona_noto_unique_flags <- unique(sapply(ciona_noto_cell_names, FUN = get_flag, TRUE, FALSE))
# 3744 vs 3750 (metadata rownames)
ciona_noto_unique_cells <- unique(sapply(ciona_noto_cell_names, FUN = get_flag, FALSE, TRUE))
```

```{r include=TRUE}
ciona_noto_unique_flags
```
```{r include=TRUE}
test_ciona_cells <- ciona_noto_cell_names[1:10]
test_ciona_cells
```
################### UNUSED CODE #######################
# https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE131155
# General dims: 15269 x 737280

################### START ENTIRE PIPELINE FOR INIG ####################

# (iniG/C110) https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSM3764764
```{r include=TRUE}
chen_4D_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/Raw_Data/4D_GSE131155_RAW/"
```

```{r include=TRUE}
iniG1_name <- "GSM3764764_iniG1_raw_gene_bc_matrices_h5.h5"
iniG2_name <- "GSM3764765_iniG2_raw_gene_bc_matrices_h5.h5" 
```

# Validate with larva
```{r include=TRUE}
larva1_name <- "GSM3764784_larva1_raw_gene_bc_matrices_h5.h5"
larva2_name <- "GSM3764785_larva2_raw_gene_bc_matrices_h5.h5"
larva3_name <- "GSM3764786_larva3_raw_gene_bc_matrices_h5.h5"
```

# Helper Function
```{r include=TRUE}
get_raw_matrix <- function(h5_dir, stage_name) {
  # Extracts raw matrix from h5 file.
  #
  # Args:
  #   h5_dir: Directory containing all h5 files. 
  #           e.g. "Orthology-Maps/.../Chen_4D/"
  #   stage_dir: Name of h5 file. 
  #           e.g. "GSM3764764_iniG1_raw_gene_bc_matrices_h5.h5"
  #
  # Returns:
  #   raw_matrix
  h5 <- paste(h5_dir, stage_name, sep = "")
  raw_matrix <- Read10X_h5(h5)
  return(raw_matrix)
}
```

#####################################################################################

# (1) Get raw matrices. 
# iniG
# 15269 x 737281
```{r include=TRUE}
iniG1_raw_matrix <- get_raw_matrix(chen_4D_dir, iniG1_name)
iniG2_raw_matrix <- get_raw_matrix(chen_4D_dir, iniG2_name)
```

# Larva 
# 15269 x 737281
```{r include=TRUE}
larva1_raw_matrix <- get_raw_matrix(chen_4D_dir, larva1_name)
larva2_raw_matrix <- get_raw_matrix(chen_4D_dir, larva2_name)
larva3_raw_matrix <- get_raw_matrix(chen_4D_dir, larva3_name)
```

#####################################################################################

# iniG
```{r include=TRUE}
test_raw_matrix <- iniG1_raw_matrix
test_raw_matrix_2 <- iniG2_raw_matrix
```

# Larva
```{r include=TRUE}
test_raw_matrix_l1 <- larva1_raw_matrix
test_raw_matrix_l2 <- larva2_raw_matrix
test_raw_matrix_l3 <- larva3_raw_matrix
```

#####################################################################################

# (2) Helper Function: Do filtering steps to get number of filtered Variable Features.

#####################################################################################
```{r include=TRUE}
make_filtered_seurat <- function(raw_matrix, min_cells, min_features) {
  # Filters Seurat Object to get number of filtered features that will be used
  # as number of VariableFeatures for all Seurat Objects to be integrated.
  # e.g. 2 Seurat Objects have 14310 and 12837 filtered features respectively.
  # Downstream, both Seurat Objects will use 12830 n_features in FindVariableFeatures. 
  seurat_object <- CreateSeuratObject(counts = raw_matrix,  
                                    min.cells = min_cells,
                                    min.features =  min_features)
  return(seurat_object)
}
```

# iniG
```{r include=TRUE}
# 14310 x 68708
test_seurat <- make_filtered_seurat(test_raw_matrix, 3, 200)
# 12830 x 1422
test_seurat_2 <- make_filtered_seurat(test_raw_matrix_2, 3, 200)
```

# Larva
```{r include=TRUE}
# 13933 x 28234
test_seurat_l1 <- make_filtered_seurat(test_raw_matrix_l1, 3, 200)
# 13907 x 12405
test_seurat_l2 <- make_filtered_seurat(test_raw_matrix_l2, 3, 200)
# 14067 x 7143
test_seurat_l3 <- make_filtered_seurat(test_raw_matrix_l3, 3, 200)

```

#####################################################################################
# (3) Add Metadata 
#####################################################################################
```{r include=TRUE}
add_metadata <- function(seurat_object, flag) {
  # Adds batch_name metadata for seurat_object.
  # e.g. "iniG1" is a flag.
  metadata_len <- length(colnames(x = seurat_object))
  metadata <- rep(flag, metadata_len)
  seurat_object$batch_name <- metadata
  
  return(seurat_object)
}
```

# iniG
```{r include=TRUE}
test_seurat <- add_metadata(test_seurat, "iniG1")
test_seurat_2 <- add_metadata(test_seurat_2, "iniG2")
```

# Larva
```{r include=TRUE}
test_seurat_l1 <- add_metadata(test_seurat_l1, "larva1")
test_seurat_l2 <- add_metadata(test_seurat_l2, "larva2")
test_seurat_l3 <- add_metadata(test_seurat_l3, "larva3")
```

#####################################################################################

# (4) Helper Function: Get the min of filtered features.

#####################################################################################

```{r include=TRUE}
get_n_features <- function(seurat_object) {
  n_features <- seurat_object@assays$RNA@counts@Dim[[1]]
  return(n_features)
}

get_min_n_features <- function(seurat_object_list) {
  n_features <- sapply(X = seurat_object_list, FUN = get_n_features)
  min_n_features_1 <- min(n_features)
  min_n_features <- floor(min_n_features_1/10)*10 
  return(min_n_features)
}
```

# List of Seurat Objects
# iniG
```{r include=TRUE}
test_seurat_object_list <- list(test_seurat, test_seurat_2)
```

# Larva
```{r include=TRUE}
test_seurat_object_list_2 <- list(test_seurat_l1, test_seurat_l2, test_seurat_l3)
```

#####################################################################################

# iniG
```{r include=TRUE}
# 12830
test_min_n_features <- get_min_n_features(test_seurat_object_list)
```

# Larva
```{r include=TRUE}
test_min_n_features_2 <- get_min_n_features(test_seurat_object_list_2)
```

#####################################################################################

# (5) Continue making Seurat Objects using test_min_features as nFeatures.

```{r include=TRUE}
continue_make_seurat <- function(seurat_object, min_features) {
  seurat_object <- NormalizeData(object = seurat_object)
  seurat_object <- FindVariableFeatures(seurat_object, 
                                      selection.method = "vst",
                                      nfeatures = min_features)
  return(seurat_object)
}
```

# Use above function to test_seurat_object_list -> test_seurat_object_list_cont.
# These will be used for integration in gencomp.
```{r include=TRUE}
test_seurat_object_list_cont_2 <- lapply(test_seurat_object_list_2, FUN = continue_make_seurat, test_min_n_features_2)
```

#####################################################################################

Test Integration on Larva

#####################################################################################

# Testing rest of pipeline on larva
```{r include=TRUE}
make_integrated_seurat <- function(object_list_cont, dims, n_anchor_features){
  # Args:
  #   object_list_cont: list of Seurat objects. e.g. zeb_seurat_list.
  #   dims: input dimensions for FindIntegrationAnchors and IntegrateData.
  #         Ciona=20, Zeb=50
  #   n_anchor_features: min_n_features. 
  
  # Routine: Do integration. 
  
  # Returns:
  #   integrated_seurat: output of above routine.
  
  anchors <- FindIntegrationAnchors(object.list = object_list_cont,
                                    dims = 1:dims,
                                    anchor.features = n_anchor_features)
  
  integrated_seurat <- IntegrateData(anchorset = anchors, dims = 1:dims)
  
  DefaultAssay(integrated_seurat) <- "integrated"
  
  return(integrated_seurat)
}
```

# Testing rest of pipeline on Larva
```{r include=TRUE}
test_integrated_seurat_2 <- make_integrated_seurat(test_seurat_object_list_cont_2,
                                                 dims = 20,
                                                 n_anchor_features = test_min_n_features_2)
```
