---
title: "notoXnoto_pipeline_average"
output: html_document
---
# Purpose of Script: Make ciona timepoint x zeb timepoint Heatmap.
# Also: 12/18/20: Gene List Analyses are also performed here. (Adapted from "one2one_orthology_map_generator.Rmd")

(1) ciona_list {key:iniG, value:3765 x num_cells} -> ciona_av_cols_list {key:iniG, value:average vector of length 3765}
(2) ciona_av_cols_list -> ciona_av_col_df (3765 x 10 df- one for each timepoint)
-Note: I check if there are any 0 cells or genes- no! 
(3) ciona_av_col_df -> ciona_timepoint_gsm
-ciona_timepoint_gsm has same structure as ciona_av_col_df. 
-Note: ciona_timepoint_gsm uses make_gsm function which test_ciona_gsm uses make_gene_specificity_matrix- outputs are the same. This was to validate that the newer implementation (make_gsm) was correct- it is! 
(4) ciona_timepoint_gsm -> timepoint_corr_output (output of corr.test. Only 1 item.) 

(5) Downstream Plot (p)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
library(stringr)
library(Seurat)
library(ggplot2)
library(Matrix)
library(ggcorrplot)
library(psych)
```

############ STEP 1 #############
# Make the appropriate test variables.
# REAL: "ortho_mapping"
```{r include=TRUE}
ortho_dict <- read.table("/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/1_CURRENT/notoXnoto/pipeline_related/pipeline_csvs/export_qualified_one2one_many_notoxnoto_dict.csv",
                         sep = ",",
                         header = FALSE,
                         stringsAsFactors = FALSE)
colnames(ortho_dict) <- c("khid", "zeb_gene")

ortho_mapping <- ortho_dict %>%
   separate_rows(zeb_gene, sep = " ")
```

##########   RESOLVED: WE NEED TO UNDERSTAND HOW TO DEAL WITH ZEB DUPLICATES  #########

# Ortho khids and zeb_genes.
```{r include=TRUE}
# 4363 (correct, as expected).
ortho_khids <- unique(ortho_mapping$khid)

# 8548 -> 6490 => There are many-1 orthologs (ciona -> zeb).
ortho_zeb_genes <- ortho_mapping$zeb_gene
```

################ DO NOT TOUCH ##################

```{r include=TRUE}
# This is a dataframe with zeb_genes that have 1-1 and 1-many orthologs. (U)
# 6490 
unique_zeb_gene_df <- ortho_mapping %>% group_by(zeb_gene) %>% summarise(num = n()) %>% dplyr::filter(num==1)
colnames(unique_zeb_gene_df)
```
################ DO NOT TOUCH ##################

```{r include=TRUE}
# 5490
unique_ortho_zeb_genes <- unique_zeb_gene_df$zeb_gene
```

################ DO NOT TOUCH ##################

```{r include=TRUE}
# I know I am doing something very hacky, but... 8hpf doesn't have 3 genes
# so I'm going to remove them...
noto_genes_8hpf <- rownames(zeb_8hpf_noto_mat)
# 3
not_in_genes_8hpf <- setdiff(unique_ortho_zeb_genes, noto_genes_8hpf)
# 5487
unique_ortho_zeb_genes <- intersect(unique_ortho_zeb_genes, noto_genes_8hpf)
```

```{r include=TRUE}
# These are the khids that correspond to zeb_genes in U. 
# There will be repeats because there are 1 KHID -> multiple zeb_genes cases.   
# 5487
corr_khid_U <- ortho_mapping %>% dplyr::filter(zeb_gene %in% unique_ortho_zeb_genes)
# 3765
corr_khids <- unique(corr_khid_U$khid)
```

############ MAKE AND MUNGE iniG_noto_mat/zeb_8hpf_noto_mat -> subset_iniG/subset_8hpf ############

# Helper Function. 
```{r include=TRUE}
modify_mat <- function(mat, subset_genes, col_rowname) {
  # Munges Matrix of batch-corrected values from noto_mats (mat) into a dataframe with 
  # rownames of khids/zeb_genes (mod_mat). Its column name is col_rowname = khid/zeb_gene.
  # subset_genes = corr_khids/unique_ortho_zeb_genes.
  mod_mat <- as.data.frame(mat[subset_genes, ])
  mod_mat[[col_rowname]] <- rownames(mod_mat)
  return(mod_mat)
}
```

# Do for Ciona.
```{r include=TRUE}
# Has khid column- NOT alpha'ly ordered.
# 3765 x 202 
subset_iniG <- modify_mat(iniG_noto_mat, corr_khids, "khid")
subset_midG <- modify_mat(midG_noto_mat, corr_khids, "khid")
subset_earN <- modify_mat(earN_noto_mat, corr_khids, "khid")
subset_latN <- modify_mat(latN_noto_mat, corr_khids, "khid")
subset_iniT <- modify_mat(iniT_noto_mat, corr_khids, "khid")
subset_earT <- modify_mat(earT_noto_mat, corr_khids, "khid")
subset_midT <- modify_mat(midT_noto_mat, corr_khids, "khid")
subset_LTB1 <- modify_mat(LTB1_noto_mat, corr_khids, "khid")
subset_LTB2 <- modify_mat(LTB2_noto_mat, corr_khids, "khid")
subset_larva <- modify_mat(larva_noto_mat, corr_khids, "khid")
```

# Do for Zeb.
```{r include=TRUE}
# Has zeb_gene column- YES alpha'ly ordered.
# 5487 x 104
subset_8hpf <- modify_mat(zeb_8hpf_noto_mat, unique_ortho_zeb_genes, "zeb_gene")
subset_10hpf <- modify_mat(zeb_10hpf_noto_mat, unique_ortho_zeb_genes, "zeb_gene")
subset_14hpf <- modify_mat(zeb_14hpf_noto_mat, unique_ortho_zeb_genes, "zeb_gene")
subset_18hpf <- modify_mat(zeb_18hpf_noto_mat, unique_ortho_zeb_genes, "zeb_gene")
subset_24hpf <- modify_mat(zeb_24hpf_noto_mat, unique_ortho_zeb_genes, "zeb_gene")
```

############# COLLAPSE ZEB MATS subset_8hpf -> subset_8hpf_collapse (no khid col, only expression matrix) #############

# Helper Function.  
```{r include=TRUE}
collapse_zeb_mat <- function(zeb_mat, ortho_mapping) {
  # Example of zeb_mat: subset_8hpf 4 x 4 
  # zeb_mat (n_zeb_genes x cells + zeb_gene) + ortho_mapping -> 
  # zeb_collapse (n_khids, cells). "Collapse" refers to summing zeb_orthos.
  
  # 4 x 5 (you gain a khid column)
  zeb_collapse <- zeb_mat %>% left_join(ortho_mapping)
  rownames(zeb_collapse) <- rownames(zeb_mat)
  
  # For each cell, add up orthologs. 
  # 3 X 4 (you add up orthologs (4 -> 3) and lose zeb_gene column (5 -> 4)) 
  # KHIDS ARE ALPHA'LY ORDERED!
  zeb_collapse_2 <- zeb_collapse %>% dplyr::group_by(khid) %>%
    dplyr::summarize(across(starts_with("DEW"), sum))
  
  zeb_rownames <- zeb_collapse_2$khid
  
  # 3 x 3 (get rid of the khid column)
  zeb_collapse_3 <- zeb_collapse_2 %>% select(-khid)
  # Retain the khid names! These ARE alpha'ly ordered!!!   
  zeb_collapse_3 <- as.data.frame(zeb_collapse_3)
  rownames(zeb_collapse_3) <- zeb_rownames

return(zeb_collapse_3)
}
```

```{r include=TRUE}
test_fn <- collapse_zeb_mat(subset_8hpf, ortho_mapping)
```

# Real 
```{r include=TRUE}
# Collapses to 3765- perfect! 
# 3765 x 103 
subset_8hpf_collapse <- collapse_zeb_mat(subset_8hpf, ortho_mapping)
subset_10hpf_collapse <- collapse_zeb_mat(subset_10hpf, ortho_mapping)
subset_14hpf_collapse <- collapse_zeb_mat(subset_14hpf, ortho_mapping)
subset_18hpf_collapse <- collapse_zeb_mat(subset_18hpf, ortho_mapping)
subset_24hpf_collapse <- collapse_zeb_mat(subset_24hpf, ortho_mapping)
```


############ GET RID OF KHID COLUMNS (no longer has khid col) ##############

# Helper Function. 
```{r include=TRUE}
remove_khid_column <- function(ciona_matrix) {
  # Example: ciona_matrix = subset_iniG
  # First sort rows alphabetically. Then remove khid column. 
  ciona_matrix_sorted <- ciona_matrix %>% arrange(khid)
  clean_ciona_matrix <- ciona_matrix_sorted %>% select(-khid)
  return(clean_ciona_matrix)
}
```

# Debugging
# test_iniG_clean ~ subset_iniG_clean 
```{r include=TRUE}
test_rem_fn <- remove_khid_column(subset_iniG)
```

```{r include=TRUE}
# 3765 x 201 
subset_iniG_clean <- remove_khid_column(subset_iniG)
subset_midG_clean <- remove_khid_column(subset_midG)
subset_earN_clean <- remove_khid_column(subset_earN)
subset_latN_clean <- remove_khid_column(subset_latN)
subset_iniT_clean <- remove_khid_column(subset_iniT)
subset_earT_clean <- remove_khid_column(subset_earT)
subset_midT_clean <- remove_khid_column(subset_midT)
subset_LTB1_clean <- remove_khid_column(subset_LTB1)
subset_LTB2_clean <- remove_khid_column(subset_LTB2)
subset_larva_clean <- remove_khid_column(subset_larva)
```

############# MAKE LISTS (genes x cells) ciona/zeb_list#############

# Helper Function. 
```{r include=TRUE}
# REAL: ciona_list = {subset_iniG...}
ciona_list = list(iniG = subset_iniG_clean,
                  midG = subset_midG_clean,
                  earN = subset_earN_clean,
                  latN = subset_latN_clean,
                  iniT = subset_iniT_clean,
                  earT = subset_earT_clean,
                  midT = subset_midT_clean,
                  LTB1 = subset_LTB1_clean,
                  LTB2 = subset_LTB2_clean,
                  larva = subset_larva_clean)
```

```{r include=TRUE}
# REAL: zeb_list = {subset_10hpf...}
zeb_list = list(zeb_8hpf = subset_8hpf_collapse,
                zeb_10hpf = subset_10hpf_collapse,
                zeb_14hpf = subset_14hpf_collapse,
                zeb_18hpf = subset_18hpf_collapse,
                zeb_24hpf = subset_24hpf_collapse)
```

####### GET AVERAGE EXPRESSION MATRICES -> DF FOR EACH SPECIES/TIMEPOINT ciona/zeb_list -> ciona/zeb_av_cols_list -> ciona/zeb_av_col_df #######

# Helper Function. 
```{r include=TRUE}
get_av_col <- function(timepoint_expression_mat) {
  # Get the average expression for each gene. 
  # genes x iniG cells (3766 x 10k df) -> genes x av_exp (3766 vector)
  # Each timepoint_av_col will be a column in *_all_timepoint_av_mat 
  timepoint_av <- timepoint_expression_mat %>% mutate(av_exp = rowMeans(.))
  timepoint_av_col <- timepoint_av$av_exp
  return(timepoint_av_col)
}
```

# Do for Ciona and Zeb. Each column is an average vector for timepoint.
```{r include=TRUE}
ciona_av_cols_list <- map(ciona_list, get_av_col)
zeb_av_cols_list <- map(zeb_list, get_av_col)
```

# Make Average Matrices by binding columns from above. 
```{r include=TRUE}
ciona_av_col_df <- as.data.frame(do.call(cbind, ciona_av_cols_list))
zeb_av_col_df <- as.data.frame(do.call(cbind, zeb_av_cols_list))
```

# Are there any 0's here?
```{r include=TRUE}
your_df <- ciona_av_col_df
```

# Are there any rows with all 0's?
# Check if there are any 0's
```{r include=TRUE}
all_num <- function(your_row, your_num) {
  # Either find all or any of a number in a row. Returns logical.
  ifelse (all(your_row == your_num), TRUE, FALSE)
}

any_num <- function(your_row, your_num) {
  # Either find all or any of a number in a row. Returns logical.
  ifelse (any(your_row == your_num), TRUE, FALSE)
}
```

```{r include=TRUE}
test <- apply(ciona_timepoint_gsm, MARGIN=2, FUN=any_num, your_num=0)
```

```{r include=TRUE}
# Gets logical that describes all the cols with all 0s.
all_0_cols <- apply(your_df, MARGIN=2, FUN=all_num, your_num=0)
# Number of cols 
all_num_0_sum <- sum(all_0_cols)
all_num_0_sum
```

############ MAKE GSM MATRICES ciona_av_col_df -> ciona_timepoint_gsm ###########

```{r include=TRUE}
ciona_timepoint_gsm <- make_gsm(ciona_av_col_df)
zeb_timepoint_gsm <- make_gsm(zeb_av_col_df)
```

# Try other gsm function (from batch_on2many_orthology_map_generator.Rmd)- The 2 are identical. 
```{r include=TRUE}
test_ciona_gsm <- make_gene_specificity_matrix(ciona_av_col_df)
```


########## GET CORRELATIONS BETWEEN MATRICES ciona/zeb_gsm, zeb/ciona_gsm -> timpepoint_corr_output ###########
```{r include=TRUE}
do_correlation <- function(ciona_gsm, zeb_gsm) {
  corr_output <- corr.test(x= ciona_gsm,
                           y = zeb_gsm,
                           method = "spearman",
                           adjust = "fdr")
  return(corr_output)
}
```

```{r include=TRUE}
timepoint_corr_output <- do_correlation(ciona_timepoint_gsm, zeb_timepoint_gsm)
```

############ VISUALIZE #############
# SPECIFY #
```{r include=TRUE}
timepoint_r <- timepoint_corr_output$r
timepoint_pval <- timepoint_corr_output$p
```

```{r include=TRUE}
your_corr_mat <- timepoint_r
your_pval_mat <- timepoint_pval
```

# Parameters.
```{r include=TRUE}
# Corr legend range. 

min.index <- min(your_corr_mat)
# max(corR.mat)
max.index <- max(your_corr_mat)
leeway <- 0.01
limits <- c(min.index-leeway, max.index+leeway)

# Aesthetics and labels. 
your.title <- "Notochord Time-course Similarity"
your.xlab <- "Ciona"
your.ylab <- "Zeb"
your.fill <- "Corr"
#4388F0, 42B5DD
your.color <- "#56B273"
your.face <- "bold"
```

```{r include=TRUE}
p <- ggcorrplot(corr = your_corr_mat,
           p.mat = your_pval_mat)
```

```{r include=TRUE}
# angle=45, 90/0

p + scale_fill_gradient2(limit = limits,
                          low = "#4C7CC4", mid = "white", high = "#BE1E0B") +
  
  ggplot2::labs(x = your.xlab, y = your.ylab, title = your.title, fill = your.fill) +
  
  ggplot2::theme(plot.title = element_text(size = 10, color = your.color, face = your.face),
                 axis.title.x = element_text(angle = 0, color = your.color, face = your.face),
                 axis.title.y = element_text(angle = 90, color = your.color, face = your.face),
                 axis.text.x = element_text(angle=45, color="black", size=10),
                 axis.text.y = element_text(angle=45, color="black", size=10),
                 legend.title = element_text(color = your.color, size = 9),
                 legend.text = element_text(size = 9)
  )
```
############# FURTHER ANALYSES ##############

 (a) Get # Significant Correlations. 
 (b) Get Significance between zeb_CT and ciona_CT

```{r include=TRUE}
num_sig <- sum(your_pval_mat < 0.05)
num_sig

num_CTs <- ncol(ciona_timepoint_gsm)*ncol(zeb_timepoint_gsm)
num_CTs
perc_sig <- num_sig/num_CTs*100
perc_sig
```

#####################  GET NAMES OF GENES THAT ARE EXPRESSED IN PAIRS OF CELL TYPES  ####################

# Helper Functions.
```{r include=TRUE}
get_non_0s <- function(df) {
  # Given 2 gsme'ed columns turned into a dataframe (col_1 ciona, col_2 zeb), 
  # get indices of both that are non-0 in both (genes expressed).
  col_1 <- as.numeric(df[, 1])
  col_2<- as.numeric((df[, 2]))
  non0_indices <- which(col_1 != 0 & col_2 !=0)
  return(non0_indices)
}

get_indexed_khids_zeb_strings <- function(index_vector, corr_khids) {
  # When you know the indices of genes that are expressed in both
  # get their khids and zeb_names. 
  # I'm using corr_khids, khids with only 1-many zeb orthologs. 
  
  indexed_khids <- corr_khids[index_vector]
  indexed_zeb_strings <- ortho_dict_zeb_strings[index_vector]
  
  ans_list <- list(indexed_khids, indexed_zeb_strings)
  
  return(ans_list)
}
```

# Now apply this to Ciona and Zeb GSMs
```{r include=TRUE}
ciona_tp_list <- as.list(ciona_timepoint_gsm)
zeb_tp_list <- as.list(zeb_timepoint_gsm)
test_gsm <- data.frame("dum_1"=rep(0, nrow(ciona_timepoint_gsm)), "dum_2"=rep(1, nrow(ciona_timepoint_gsm)))
test_tp_list <- as.list(test_gsm)

your_list <- zeb_tp_list

# Make a list in which each element is a 2-size list with each as a column
cz_cross <- cross2(ciona_tp_list, your_list)

## USE ##
# Get indices of both non-0 elements in col_1 and col_2 
cz_map <- map(cz_cross, as.data.frame) %>% map(get_non_0s)

cz_map_2 <- map(cz_map, get_indexed_khids_zeb_strings, ortho_dict)
```












###################    GENE LIST MUNGING    ####################
"""
Various lists for TF and SMG filtering
"""

# TF List 1: Nitta 2019 (SELEX Project)- 964 ciona_tfs
# TO DO: Clean up the dataframe, not just get gene names. 
```{r include=TRUE}
ciona_tf_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/ciona_regulatory_regions/unmunged_ciona_TFs.csv"

ciona_tf_df <- read.table(ciona_tf_dir,
                          sep = ",",
                          stringsAsFactors = FALSE,
                          header = TRUE)

# Important Variable (964 Nitta TFs)
ciona_tfs <- ciona_tf_df$KH.model.ID
ciona_tfs <- ciona_tfs[!ciona_tfs == ""]
ciona_tfs <- paste("KH2012:", ciona_tfs, sep = "")
```

# List 2: Aniseed Human Ortholog File (This is a df)
```{r include=TRUE}
khid_human_ortho_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/lifechanging_aniseed_files/ANISEED-Cirobu-GeneName-3bestBlastHitHuman.rnames"

# Gene.ID, Gene.Name: 26426
khid_human_ortho_df <- read.table(khid_human_ortho_dir,
                                  sep = "\t",
                                  stringsAsFactors = FALSE,
                                  header = TRUE)
```

# List 3: Kai Ghost Curation: TF and SMG List 1023 (all_kai_genes)
```{r include=TRUE}
kai_tf_smg_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/ciona_regulatory_regions/kai_tf_smg_list.csv"

kai_tf_smg_df <- read.table(kai_tf_smg_dir,
                            sep = ",",
                            header = TRUE,
                            stringsAsFactors = FALSE)
```

# Munge KHIDs.
```{r include=TRUE}
add_kh_tag <- function(kh_name) {
  full_kh_name <- paste0("KH2012:", kh_name)
  return(full_kh_name)
}

new_col <- as.data.frame(sapply(kai_tf_smg_df[, 1], add_kh_tag))
colnames(new_col) <- "KH.gene.model"
kai_tf_smg_df[, 1] <- new_col 

# Important Variable (1023 Kai TF/SMGs)
all_kai_genes <- as.vector(kai_tf_smg_df$KH_gene_model)
```

"""
How many of these 1-1 DEG Orthologs are TFs?
"""

# KHID and Zeb Names
```{r include=TRUE}
ciona.tf.indices <- which(qualified_ciona_khids %in% ciona.tfs)

# What are their names?
qual.ciona.tfs <- qualified_ciona_khids[ciona.tf.indices]
qual.zeb.tfs <- qualified_zeb_genes[ciona.tf.indices]

cat(qual.ciona.tfs, sep="\n")
cat("\n")
cat(qual.zeb.tfs, sep="\n")
```

# Human Orthologs 
```{r include=TRUE}
qual.human.tfs <- khid.human.ortho.df[khid.human.ortho.df$Gene.ID %in% qual.ciona.tfs, ]
qual.human.tfs
```
# Print Results. 
```{r include=TRUE}
khid.names <- qual.human.tfs$Gene.ID
khid.human.names <- qual.human.tfs$Gene.Name

for (i in 1:length(khid.names)) {
  my.name <- khid.names[i]
  my.human.name <- khid.human.names[i]
  
  cat(my.name, "=", my.human.name, "\n")
}
```

"""
Analyses using Kai's files.
"""
# TF and SMG List: Kai (Ghost Curation)
```{r include=TRUE}
kai.tf.smg.dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/ciona_regulatory_regions/kai_tf_smg_list.csv"

kai.tf.smg.df <- read.table(kai.tf.smg.dir,
                            sep = ",",
                            header = TRUE,
                            stringsAsFactors = FALSE)
```

# Munge KHIDs.
```{r include=TRUE}
add.kh.tag <- function(kh.name) {
  full.kh.name <- paste0("KH2012:", kh.name)
  return(full.kh.name)
}

new.col <- as.data.frame(sapply(kai.tf.smg.df[, 1], add.kh.tag))
colnames(new.col) <- "KH.gene.model"
kai.tf.smg.df[, 1] <- new.col 

# Important Variable (1023 Kai TF/SMGs)
all.kai.genes <- as.vector(kai.tf.smg.df$KH.gene.model)
```

# Which 1-1 DEG Orthologs are TF/SMGs?
```{r include=TRUE}
kai.filtered.df <- kai.tf.smg.df %>% filter(KH.gene.model %in% qualified_ciona_khids)
```

# Print Results 
```{r include=TRUE}
# Kai genes are filtered (within 1-1 DEG Ortholog List) NOT ALL KAI GENES
kai.genes <- as.vector(kai.filtered.df$KH.gene.model)
kai.gene.names <- kai.filtered.df$Ghost.Name
kai.class <- kai.filtered.df$Ghost.class

for (i in 1:length(kai.genes)) {
  my.gene <- kai.genes[i]
  my.gene.name <- kai.gene.names[i]
  my.class <- kai.class[i]
  
  cat(my.gene, "=", my.gene.name, "(", my.class, ")","\n")
}
```

# Quick Utility to get ciona khid and zeb gene names for kai.genes
```{r include=TRUE}
# Tells you INDICES of 1-1 ciona khids that are kai genes.
kai.gene.indices <- which(qualified_ciona_khids %in% kai.genes)

# These tell you which 1-1 ciona khids are kai genes. 
kai.ciona.genes <- qualified_ciona_khids[kai.gene.indices]
kai.zeb.genes <- qualified_zeb_genes[kai.gene.indices]
```

##### Part 3: GENE LIST ANALYSES #####
"""
Start For Individual CT Analyses (Re-Analyses)
"""
# CHANGE directories for individual CTs.
```{r include=TRUE}
ciona.CT.dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/1_CURRENT/one2one_larva_24hpf/logFC_0/24hpf_2hearts_gene_analyses/2CT_analyses/larva_noto_24hpf_noto_analyses/larva_noto_24hpf_noto_DEG_logFC0_khids.csv"

zeb.CT.dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/1_CURRENT/one2one_larva_24hpf/logFC_0/24hpf_2hearts_gene_analyses/2CT_analyses/larva_noto_24hpf_noto_analyses/larva_noto_24hpf_noto_DEG_logFC0_zebgenes.csv"

ciona.CT.df <- read.table(ciona.CT.dir,
                          sep =",",
                          header = FALSE,
                          stringsAsFactors = FALSE)

zeb.CT.df <- read.table(zeb.CT.dir,
                          sep =",",
                          header = FALSE,
                          stringsAsFactors = FALSE)

ciona.CT.genes <- ciona.CT.df$V1
zeb.CT.genes <- zeb.CT.df$V1

length(ciona.CT.genes)
```

# Nitta and Kai Filtering for individual CTs. 
(Can use below in Visualizations as ciona_genes and zeb_genes)
```{r include=TRUE}
# Which of these are Nitta TFs?
ciona.CT.nitta.indices <- which(ciona.CT.genes %in% ciona.tfs)
ciona.CT.nitta <- ciona.CT.genes[ciona.CT.nitta.indices]
length(ciona.CT.nitta)

# Which of these are Kai TF SMGs?
ciona.CT.kai.indices <- which(ciona.CT.genes %in% kai.genes)
ciona.CT.kai <- ciona.CT.genes[ciona.CT.kai.indices]
length(ciona.CT.kai)
```

# Get Human Orthologs for individual CTs.
# CHANGE filtered.genes = ciona.CT.nitta/kai
```{r include=TRUE}
filtered.genes <- ciona.CT.kai
filtered.genes
cat("\n\n")
  
# Dataframe: KHID, Human Ortholog
filtered.human.khids <- khid.human.ortho.df[khid.human.ortho.df$Gene.ID %in% filtered.genes, ]
filtered.names <- filtered.human.khids$Gene.Name

filtered.names
cat("\n\n")

filtered.human.khids
```


"""
End For Individual CT Analyses (Re-Analyses)
"""

"""""""
Part 3: What are the highly expressed genes here?
Note: All Analyses below pertain to logFC>0. 

(1) Pick Genes:
a) all 1-1 DEG Orthologs (2466)
qualified_ciona_khids, qualified_zeb_genes
Correlation of 2466 1-1 DEG Orthologs

b) Nitta filtering (235) 
qual.ciona.tfs, qual.zeb.tfs
Correlation of Nitta TFs

c) Kai filtering (197)
kai.ciona.genes, kai.zeb.genes
Correlation of Kai TF and SMGs

d) For individual CTs
ciona.CT.genes, zeb.CT.genes
(would have been defined before) filtered.genes <- ciona.CT.nitta, ciona.CT.kai

(2) Pick pairs of CTs
ciona.CT, zeb.CT

""""""""

# Specify Genes and CTs.
```{r include=TRUE}
# Change
ciona.CT <- "noto"
zeb.CT <- "noto"
ciona_genes <- ciona.CT.genes
zeb_genes <- zeb.CT.genes

ciona.CT.av.exp <- ciona_gsm_v4[ciona_genes, ciona.CT]
zeb.CT.av.exp <- zeb_gsm_v4[zeb_genes, zeb.CT]

scatter.df <- data.frame(ciona.CT = ciona.CT.av.exp,
                         zeb.CT = zeb.CT.av.exp,
                         khid = ciona_genes,
                         zeb.genes = zeb_genes)

zeb.noto <- "zeb_noto"
colnames(scatter.df)[1:2] <- c(ciona.CT, zeb.noto)
```

(3) Visualize
```{r include=TRUE}
# Change
your.title <- "Correlation of CT 1-1 DEG Orthologs"
your.av.exp.cutoff.ciona <- 1
your.av.exp.cutoff.zeb <- 1

new.labels <- gsub("KH2012:KH.", "", ciona_genes)
 
scatter.plot <- ggplot(scatter.df,
                       aes(x = ciona.CT.av.exp, y = zeb.CT.av.exp)) +
                       geom_point() + 
  
                       geom_text(size=2.5, hjust=0, vjust=0, angle=0, aes(label = ifelse(ciona.CT.av.exp>your.av.exp.cutoff.ciona & zeb.CT.av.exp>your.av.exp.cutoff.zeb, as.character(new.labels), ""))) +
  
  ggtitle(your.title) +
  xlab(ciona.CT) +
  ylab(zeb.CT) +
  geom_abline()

scatter.plot
```

(4) Get the Human Orthologs of above KHIDs. (Manually Curated from Scatter Plot)
```{r include=TRUE}
res.ciona.khids <- c("C5.525", "C5.1", "L171.10", "C3.308")

res.ciona.khids <- paste0("KH2012:KH.", res.ciona.khids)

# Dataframe: KHID, Human Ortholog
res.human.khids <- khid.human.ortho.df[khid.human.ortho.df$Gene.ID %in% res.ciona.khids, ]

res.names <- res.human.khids$Gene.Name
res.names
```

# Interactive Scatter Plot
```{r include=TRUE}
# x = ciona.CT.av.exp, y = zeb.CT.av.exp
fig <- plot_ly(type = "scatter", scatter.df, x = ~noto, y = ~zeb_noto, text = ~khid)

fig
```

(4) Get the Human Orthologs of above KHIDs. (Manually Curated from Interactive Scatter Plot)
```{r include=TRUE}
my.genes <- c("KH2012:KH.C14.310")
my.genes
cat("\n\n")
  
# Dataframe: KHID, Human Ortholog
my.human.khids <- khid.human.ortho.df[khid.human.ortho.df$Gene.ID %in% my.genes, ]
my.names <- my.human.khids$Gene.Name

my.names
cat("\n\n")

my.human.khids
```
















############ UNUSED ##############

# TEST GSM'ED STUFF
```{r include=TRUE}
df_3 <- data.frame("h"=c(0, 0, 0, 5, 6), "i"=c(1, 2, 2, 5, 6), "j"=c(3, 4, 6, 5, 6))
df_4 <- data.frame("k"=c(0, 2, 3, 5, 6), "l"=c(1, 3, 0, 0, 0), "m"=c(3, 8, 6, 7, 9))

df_list_1 <- list(df_1, df_2)
df_list_2 <- list(df_3, df_4)
```

```{r include=TRUE}
# , "b"=c(4, 0, 5), "b"=c(4, 0, 5), "c"=c(4, 0, 5)
test_df_1 <- data.frame("a"=c(1, 2, 3, 6, 6), "b"=c(4, 0, 5, 6, 7))
# "e"=c(0, 1, 2), "f"=c(0, 0, 2), "g"=c(0, 9, 1)
test_df_2 <- data.frame("d"=c(0, 9, 1, 0, 0), "l"=c(1, 2, 3, 5, 6), "g"=c(0, 9, 1, 1, 0))

test_rownames <- c("llama", "alpaca", "yousuck")

test_df_list_1 <- as.list(test_df_1)
test_df_list_2 <- as.list(test_df_2)

## USE ##
get_non_0s <- function(df) {
  # Given 2 gsme'ed columns turned into a dataframe (col_1 ciona, col_2 zeb), 
  # get indices of both that are non-0 in both (genes expressed).
  col_1 <- as.numeric(df[, 1])
  col_2<- as.numeric((df[, 2]))
  non0_indices <- which(col_1 != 0 & col_2 !=0)
  return(non0_indices)
}

## USE ##
# Make a list in which each element is a 2-size list with each as a column
test_cross <- cross2(test_df_list_1, test_df_list_2)

## USE ##
# Get indices of both non-0 elements in col_1 and col_2 
test_map <- map(test_cross, as.data.frame) %>% map(get_non_0s)
```

```{r include=TRUE}
## USE ##
# Now get the names of those genes. 
# get_indexed_khids_zeb_strings <- function(index_vector, corr_khids) {
#   ortho_dict_khids <- corr_khids[index_vector]
#   ortho_dict_zeb_strings <- ortho_dict %>% filter(khid %in% ortho_dict_khids)
#   ortho_dict_zeb_strings <- as.vector(ortho_dict_zeb_strings$zeb_gene)
#                                                   
#   indexed_khids <- ortho_dict_khids[index_vector]
#   indexed_zeb_strings <- ortho_dict_zeb_strings[index_vector]
#   
#   ans_list <- list(indexed_khids, indexed_zeb_strings)
#   
#   return(ans_list)
# }
# 
# ## USE ##
# test_map_2 <- map(test_map, get_indexed_khids_zeb_strings, ortho_dict)

test_corr_khids <- corr_khids[1:10]
test_corr_khids
cat("\n\n")

test_index_vector <- c(1, 2, 5)

test_ortho_dict_khids <- test_corr_khids[test_index_vector] 
test_ortho_dict_khids
```

```{r include=TRUE}
test_ortho_dict_zeb_strings <- ortho_dict %>% filter(khid %in% test_ortho_dict_khids)


```


### TESTING NEW collapse_zeb_mat function BECAUSE KHIDS ARE IN ALPHA'LY ORDER! 
```{r include=TRUE}
test_fn <- collapse_zeb_mat(subset_8hpf, ortho_mapping)
```

# Debugging -> Collapse 8hpf Zeb
# test_collapse_3 ~ subset_8hpf_collapse
```{r include=TRUE}
test_subset <- subset_8hpf
test_collapse <- test_subset %>% left_join(ortho_mapping)
# ADD THIS LINE LATER
rownames(test_collapse) <- rownames(test_subset)

test_collapse_2 <- test_collapse %>% dplyr::group_by(khid) %>%
  dplyr::summarize(across(starts_with("DEW"), sum))

# ADD THIS LINE LATER! 
test_rownames <- test_collapse_2$khid

# 3 x 3 (you get rid of the khid column)
test_collapse_3 <- test_collapse_2 %>% select(-khid)
# LINE BELOW IS VIMP! ADD.  
test_collapse_3 <- as.data.frame(test_collapse_3)
rownames(test_collapse_3) <- test_rownames
```

# Debugging -> Collapse Zeb (small)
```{r include=TRUE}
# 4 X 4 (you have a zeb_gene column)
test_small_subset <- data.frame(cell_1 = c(1, 2, 3, 4), cell_2 = c(1, 3, 5, 3), cell_3 = c(5, 6, 7, 4))
rownames(test_small_subset) <- c("zic1", "ddit4", "foxa2", "foxa")
test_small_subset$zeb_gene <- rownames(test_small_subset) 

# 4 X 5 (you gain a khid column)
test_small_collapse <- test_small_subset %>% left_join(ortho_mapping)
# ADD THIS LINE LATER
rownames(test_small_collapse) <- rownames(test_small_subset)

# 3 X 4 (you lose the zeb_column, and you get new values where orthologs are added up)
test_small_collapse_2 <- test_small_collapse %>% dplyr::group_by(khid) %>%
  dplyr::summarize(across(starts_with("cell"), sum))

# ADD THIS LINE LATER! 
test_small_rownames <- test_small_collapse_2$khid

# 3 x 3 (you get rid of the khid column)
test_small_collapse_3 <- test_small_collapse_2 %>% select(-khid)
rownames(test_small_collapse_3) <- test_small_rownames
```


# Debugging -> Collapse Zeb 10hpf- same order of genes- good. 
```{r include=TRUE}
test_subset_10 <- subset_10hpf
test_collapse_10 <- test_subset_10 %>% left_join(ortho_mapping)
# ADD THIS LINE LATER
rownames(test_collapse_10) <- rownames(test_subset_10)

test_collapse_2_10 <- test_collapse_10 %>% dplyr::group_by(khid) %>%
  dplyr::summarize(across(starts_with("DEW"), sum))

# ADD THIS LINE LATER! 
test_rownames_10 <- test_collapse_2_10$khid

# 3 x 3 (you get rid of the khid column)
test_collapse_3_10 <- test_collapse_2_10 %>% select(-khid)
# LINE BELOW IS VIMP! ADD.  
test_collapse_3_10 <- as.data.frame(test_collapse_3_10)
rownames(test_collapse_3_10) <- test_rownames_10
```

########### TESTS ################
# Input: Expression Matrix (Species/Timepoint)
# Output: Average Matrix

```{r include=TRUE}
test_df <- data.frame(a = c(1, 2, 3, 4), b = c(4, 5, 6, 4), d = c(2.5, 3, 5, 4))
test_df

test_df_2 <- data.frame(a = c(1, 2, 5, 6), b = c(4, 5, 3, 4), d = c(2, 6, 7, 3))
test_df_2

test_df_3 <- data.frame(a = c(1, 2, 3, 4), b = c(5, 6, 7, 8), c = c(9, 10, 11, 12))
test_df_3

test_df_4 <- data.frame(a = c(1, 5, 6, 4), b = c(10, 1, 3, 8), c = c(9, 1, 2, 3))
test_df_4

test_df_5 <- data.frame(a = c(1, 5, 10, 5), b = c(10, 1, 2, 8), c = c(9, 1, 2, 4))
test_df_5
```

# CORRECT: # Make a column with average expression
```{r include=TRUE}
test_list <- list(test_df = test_df,
                  test_df_2 = test_df_2)

test_list_2 <- list(test_df_3 = test_df_3,
                    test_df_4 = test_df_4,
                    test_df_5 = test_df_5)

test_map_ans <- map(test_list, get_av_col)
test_map_ans_2 <- map(test_list_2, get_av_col)
```

```{r include=TRUE}
test_map_ans$test_df
test_map_ans$test_df_2

test_map_ans_2$test_df_3
test_map_ans_2$test_df_4
test_map_ans_2$test_df_5
```
"""
# test_map_ans -> ciona_av_cols_list
# test_map_ans_2 -> zeb_av_cols_list
"""
####### NOW GET PAIRWISE SPEARMANS ########
 ###########  IMPLEMENTATION 2  #######

```{r include=TRUE}
do_correlation <- function(ciona_gsm, zeb_gsm) {
  corr_output <- corr.test(x= ciona_gsm,
                           y = zeb_gsm,
                           method = "spearman",
                           adjust = "fdr")
  return(corr_output)
}
```


####### NOW GET PAIRWISE SPEARMANS #######
 ###########  IMPLEMENTATION 1  #######
# (1) Make pairwise vectors.
```{r include=TRUE}
test_pairwise_list <- cross2(test_map_ans, test_map_ans_2)
```

# REAL 
```{r include=TRUE}
pairwise_list <- cross2(ciona_av_cols_list, zeb_av_cols_list)
```

# (2) Give informative key names.
# Helper Function.
```{r include=TRUE}

give_names <- function(your_list) {
  name_1 <- your_list[[1]]
  name_2 <- your_list[[2]]
  name_flag <- paste0("pair_", name_1, "/", name_2)
  return(name_flag)
}
```

# Get the names
# CODE TO DO: How to add argument to map...
```{r include=TRUE}
test_pairwise_names <- cross2(names(test_list), names(test_list_2))
test_pairwise_names <- test_pairwise_names %>% map(give_names)

names(test_pairwise_list) <- test_pairwise_names
```

# REAL 
```{r include=TRUE}
pairwise_names <- cross2(names(ciona_list), names(zeb_list))
pairwise_names <- pairwise_names %>% map(give_names)

names(pairwise_list) <- pairwise_names
```

# (3) Do Spearman correlations- we want both r and p-value.
```{r include=TRUE}
test_av <- test_map_ans$test_df
test_av_3 <- test_map_ans_2$test_df_3
test_av_4 <- test_map_ans_2$test_df_4
```

```{r include=TRUE}
test_cor_13 <- corr(test_av, test_av_3, method=)
```

########### TESTS ################
# Input: Expression Matrix (Species/Timepoint)
# Output: Average Matrix

```{r include=TRUE}
test_df <- data.frame(a = c(1, 2, 3, 4), b = c(4, 5, 6, 4), d = c(2.5, 3, 5, 4))
test_df

test_df_2 <- data.frame(a = c(1, 2, 5, 6), b = c(4, 5, 3, 4), d = c(2, 6, 7, 3))
test_df_2
```

# CORRECT: # Make a column with average expression
```{r include=TRUE}
# Make a column with average expression
test_df_av <- test_df %>% mutate(av_exp = rowMeans(.))
test_df_av

test_df_av_2 <- test_df_2 %>% mutate(av_exp = rowMeans(.))
test_df_av_2
```

# CORRECT: # Divide all other columns with this average -> get the column
```{r include=TRUE}
# Divide all other columns with this average 
test_df_av_col <- test_df_av$av_exp
test_df_av_col

test_df_av_col_2 <- test_df_av_2$av_exp
test_df_av_col_2
```

# WANT THIS: Helper Function
```{r include=TRUE}
get_av_col <- function(timepoint_expression_mat) {
  # Get the average expression for each gene. 
  # genes x iniG cells (3766 x 10k df) -> genes x av_exp (3766 vector)
  # Each timepoint_av_col will be a column in *_all_timepoint_av_mat 
  timepoint_av <- timepoint_expression_mat %>% mutate(av_exp = rowMeans(.))
  timepoint_av_col <- timepoint_av$av_exp
  return(timepoint_av_col)
}
```

```{r include=TRUE}
get_av_col(test_df)
get_av_col(test_df_2)
```

# Test list
```{r include=TRUE}
test_list <- list(test_df = test_df,
             test_df_2 = test_df_2)

test_map_ans <- map(test_list, get_av_col)
```

# Real Test: iniG
```{r include=TRUE}
# 201
test_iniG <- subset_iniG_clean
# 202
test_iniG_2 <- test_iniG %>% mutate(av_expression = rowMeans(.)) %>%
  select(av_expression)

test_ans <- test_iniG_2$av_expression
# test_ans
```

```{r include=TRUE}
av_col_test <- get_av_col(test_iniG)
# av_col_test
```

```{r include=TRUE}
sum(test_ans == av_col_test)
```
# Do for all. 
```{r include=TRUE}
ciona_av_cols_list <- map(ciona_list, get_av_col)
zeb_av_cols_list <- map(zeb_list, get_av_col)
```

############### UNUSED #################

# The last column (has averages), rest has the numbers.
```{r include=TRUE}
# 3766 x 1
test_last <- test_iniG_2 %>% select(last_col())
# Smarter way to do this? 
# 201
test_all <- test_iniG_2 %>% select(!last_col())

test_last
test_all

test_divided <- test_all/test_last
test_divided
```
# Make sure that the mean of the row in test_all == test_last
```{r include=TRUE}
test_row <- as.numeric(test_all[1, ])
mean(test_row)
as.numeric(test_last[1, ])

mean(as.numeric(test_iniG[1, ]))
```


```{r include=TRUE}
test_df <- data.frame(a = c(1, 2, 3, 4), b = c(4, 5, 6, 4), d = c(2.5, 3, 5, 4))
test_df
```

# CORRECT: # Make a column with average expression
```{r include=TRUE}
# Make a column with average expression
test_df_av <- test_df %>% mutate(av_exp = rowMeans(.))
test_df_av
```
# CORRECT: # Divide all other columns with this average -> GSM
```{r include=TRUE}
# Divide all other columns with this average 
test_num_timepoints <- ncol(test_df_av)-1
test_gsm <- test_df_av[, 1:test_num_timepoints]/test_df_av[, test_num_timepoints+1]
test_gsm

```
```{r include=TRUE}
test_df_check <- make_gsm(test_df)
test_df_check
```


# Try for 1 row
```{r include=TRUE}
check_same(test_iniG[200, ])
```

# Check for all rows.
```{r include=TRUE}
sapply(test_df, check_same(test_df))
```

############# TRYING TO UNDERSTAND WHY MEAN AND MEDIAN NUMBERS ARE SO DIFFERENT ################

# Doing for iniG 
```{r include=TRUE}
test_iniG_average <- ciona_av_col_df$iniG
test_iniG_all_cells <- ciona_removed_list$iniG

# Sanity check that my cell expression inputs is correct. 
test_iniG_average_removed <- apply(test_iniG_all_cells, FUN = mean, MARGIN = 1)
```

```{r include=TRUE}
# In the average case, I get the average and then gsm it.
test_iniG_gsm <- ciona_timepoint_gsm$iniG

# Is this the same as gsm(all cells), then take average? No! 
test_iniG_all_gsm <- make_gsm(test_iniG_all_cells) 
test_iniG_all_gsm_mean <- apply(test_iniG_all_gsm, FUN = mean, MARGIN = 1)

test_8hpf_all_cells <- zeb_removed_list$zeb_8hpf
test_8hpf_all_gsm <- make_gsm(test_8hpf_all_cells) 
test_8hpf_all_gsm_mean <- apply(test_8hpf_all_gsm, FUN = mean, MARGIN = 1)
```
