---
title: "notoXnoto_pipeline"
output: html_document
---
-Here, the presence of many-1 ciona -> zeb orthologs were detected. 
-ortho_khids -> corr_khids, unique_ortho_zeb_genes updated.
(1) subset_iniG <- modify_mat(iniG_noto_mat, corr_khids, "khid")
(2) subset_8hpf <- modify_mat(zeb_8hpf_noto_mat, unique_ortho_zeb_genes, "zeb_gene")

(1) subset_iniG_clean = iniG_noto_mat, corr_khids, "khid"
(2) ciona_list {key:iniG, value:subset_iniG_clean}
(3) ciona_list -> ciona_removed list 
-Each value of ciona_removed_list is a dataframe with khids that are not expressed in any of the cells across all timepoints in both species. 
-ciona_removed_list is the same as ciona_list_gsm {key:iniG, value:df of khid x cells}
(4) ciona_removed_list -> ciona_list_gsm {key:iniG, value:df (2897 x num_cells)}
-ciona_list_gsm has the same list structure as ciona_removed_list
(5) cross_gsm <- cross2(ciona_list_gsm, zeb_list_gsm)
cross_gsm: {key:gsm_iniG/zeb_8hpf, value:gsm_ciona_df and gsm_zeb_df}
(6) cross_gsm -> gsm_corrs -> sig_corrs -> medians
-gsm_corrs and sig_corrs have the same list structure as cross_gsm
-medians is a numeric with sig_corrs.


-gsm_corrs <- map(cross_gsm, do_correlation)
-I also get sig_corrs (significant median values) 

(6) Downstream Plots
-Medians with (heatmap_mat) and without (m) significant correlations. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(Seurat)
library(tidyverse)
library(stringr)
library(ggplot2)
library(Matrix)
library(ggcorrplot)
library(psych)
```

############ STEP 1 #############
# Make the appropriate test variables.
# REAL: "ortho_mapping"
```{r include=TRUE}
ortho_dict <- read.table("/home/pprakriti/Desktop/export_qualified_one2one_many_notoxnoto_dict.csv",
                         sep = ",",
                         header = FALSE,
                         stringsAsFactors = FALSE)
colnames(ortho_dict) <- c("khid", "zeb_gene")

ortho_mapping <- ortho_dict %>%
   separate_rows(zeb_gene, sep = " ")
```


##########   RESOLVED: WE NEED TO UNDERSTAND HOW TO DEAL WITH ZEB DUPLICATES  #########

# Ortho khids and zeb_genes.
```{r include=TRUE}
# 4363 (correct, as expected).
ortho_khids <- unique(ortho_mapping$khid)

# 8548 -> 6490 => There are many-1 orthologs (ciona -> zeb).
ortho_zeb_genes <- ortho_mapping$zeb_gene
```

```{r include=TRUE}
# This is a dataframe with zeb_genes that have 1-1 and 1-many orthologs. (U)
# 5490 
unique_zeb_gene_df <- ortho_mapping %>% group_by(zeb_gene) %>% summarise(num = n()) %>%
  filter(num == 1)
# 5490
unique_ortho_zeb_genes <- unique_zeb_gene_df$zeb_gene
```

```{r include=TRUE}
# I know I am doing something very hacky, but... 8hpf doesn't have 3 genes
# So I'm going to remove them...
noto_genes_8hpf <- rownames(zeb_8hpf_noto_mat)
# 3
not_in_genes_8hpf <- setdiff(unique_ortho_zeb_genes, noto_genes_8hpf)
# 5487
unique_ortho_zeb_genes <- intersect(unique_ortho_zeb_genes, noto_genes_8hpf)
```

```{r include=TRUE}
# These are the khids that correspond to zeb_genes in U. 
# There will be repeats because there are 1 KHID -> multiple zeb_genes cases.   
# 5487
corr_khid_U <- ortho_mapping %>% filter(zeb_gene %in% unique_ortho_zeb_genes)
# 3765
corr_khids <- unique(corr_khid_U$khid)
```

############ MAKE AND MUNGE iniG_noto_mat/zeb_8hpf_noto_mat -> subset_iniG/subset_8hpf ############

# Helper Function.
```{r include=TRUE}
modify_mat <- function(mat, subset_genes, col_rowname) {
  # Munges Matrix of batch-corrected values from noto_mats (mat) into a dataframe with 
  # rownames of khids/zeb_genes (mod_mat). Its column name is col_rowname = khid/zeb_gene.
  # subset_genes = ortho_khids/ortho_zeb_genes.
  mod_mat <- as.data.frame(mat[subset_genes, ])
  mod_mat[[col_rowname]] <- rownames(mod_mat)
  return(mod_mat)
}
```

# Do for Ciona.
```{r include=TRUE}
# REAL: subset_iniG <- modify_mat(iniG_noto_mat, ortho_khids, "khid")
subset_iniG <- modify_mat(iniG_noto_mat, corr_khids, "khid")
subset_midG <- modify_mat(midG_noto_mat, corr_khids, "khid")
subset_earN <- modify_mat(earN_noto_mat, corr_khids, "khid")
subset_latN <- modify_mat(latN_noto_mat, corr_khids, "khid")
subset_iniT <- modify_mat(iniT_noto_mat, corr_khids, "khid")
subset_earT <- modify_mat(earT_noto_mat, corr_khids, "khid")
subset_midT <- modify_mat(midT_noto_mat, corr_khids, "khid")
subset_LTB1 <- modify_mat(LTB1_noto_mat, corr_khids, "khid")
subset_LTB2 <- modify_mat(LTB2_noto_mat, corr_khids, "khid")
subset_larva <- modify_mat(larva_noto_mat, corr_khids, "khid")
```

# Do for Zeb.
```{r include=TRUE}
# REAL: subset_10hpf <- modify_mat(zeb_10hpf_noto_mat, ortho_zeb_genes, "zeb_gene")
subset_8hpf <- modify_mat(zeb_8hpf_noto_mat, unique_ortho_zeb_genes, "zeb_gene")
subset_10hpf <- modify_mat(zeb_10hpf_noto_mat, unique_ortho_zeb_genes, "zeb_gene")
subset_14hpf <- modify_mat(zeb_14hpf_noto_mat, unique_ortho_zeb_genes, "zeb_gene")
subset_18hpf <- modify_mat(zeb_18hpf_noto_mat, unique_ortho_zeb_genes, "zeb_gene")
subset_24hpf <- modify_mat(zeb_24hpf_noto_mat, unique_ortho_zeb_genes, "zeb_gene")
```


############# COLLAPSE ZEB MATS subset_8hpf -> subset_8hpf_collapse (no khid col, only expression matrix) #############
 
# Helper Function.  
# I turn the tibble into a dataframe. 
```{r include=TRUE}
collapse_zeb_mat <- function(zeb_mat, ortho_mapping) {
  # zeb_mat (n_zeb_genes x cells + zeb_gene) + ortho_mapping -> 
  # zeb_collapse (n_khids, cells). "Collapse" refers to summing zeb_orthos.
  zeb_collapse <- zeb_mat %>% left_join(ortho_mapping)
  zeb_collapse <- zeb_collapse %>% group_by(khid) %>%
  summarize((across(starts_with("DEW"), sum))) %>%
  select(-khid)
  zeb_collapse <- as.data.frame(zeb_collapse)
return(zeb_collapse)
}
```

```{r include=TRUE}
# Collapses to 3765- perfect! 
subset_8hpf_collapse <- collapse_zeb_mat(subset_8hpf, ortho_mapping)
subset_10hpf_collapse <- collapse_zeb_mat(subset_10hpf, ortho_mapping)
subset_14hpf_collapse <- collapse_zeb_mat(subset_14hpf, ortho_mapping)
subset_18hpf_collapse <- collapse_zeb_mat(subset_18hpf, ortho_mapping)
subset_24hpf_collapse <- collapse_zeb_mat(subset_24hpf, ortho_mapping)
```

############ GET RID OF KHID COLUMNS (no longer has khid col) ##############

```{r include=TRUE}
remove_khid_column <- function(ciona_matrix) {
  clean_ciona_matrix <- ciona_matrix %>% select(-khid)
  return(clean_ciona_matrix)
}
```

```{r include=TRUE}
subset_iniG_clean <- remove_khid_column(subset_iniG)
subset_midG_clean <- remove_khid_column(subset_midG)
subset_earN_clean <- remove_khid_column(subset_earN)
subset_latN_clean <- remove_khid_column(subset_latN)
subset_iniT_clean <- remove_khid_column(subset_iniT)
subset_earT_clean <- remove_khid_column(subset_earT)
subset_midT_clean <- remove_khid_column(subset_midT)
subset_LTB1_clean <- remove_khid_column(subset_LTB1)
subset_LTB2_clean <- remove_khid_column(subset_LTB2)
subset_larva_clean <- remove_khid_column(subset_larva)
```

############# MAKE LISTS (genes x cells) ciona/zeb_list #############
```{r include=TRUE}
# Note: Rownames have khids. 
ciona_list = list(iniG = subset_iniG_clean,
                  midG = subset_midG_clean,
                  earN = subset_earN_clean,
                  latN = subset_latN_clean,
                  iniT = subset_iniT_clean,
                  earT = subset_earT_clean,
                  midT = subset_midT_clean,
                  LTB1 = subset_LTB1_clean,
                  LTB2 = subset_LTB2_clean,
                  larva = subset_larva_clean)
```

```{r include=TRUE}
# Note: Rownames do not have names (makes sense).
zeb_list = list(zeb_8hpf = subset_8hpf_collapse,
                zeb_10hpf = subset_10hpf_collapse,
                zeb_14hpf = subset_14hpf_collapse,
                zeb_18hpf = subset_18hpf_collapse,
                zeb_24hpf = subset_24hpf_collapse)
```


################# FIND INDICES OF GENES THAT ARE NOT EXPRESSED IN ANY CELLS (all_genes_0) #################

### Exploratory: Check if there are any 0's ###
```{r include=TRUE}
all_num <- function(your_row, your_num) {
  # Do you see your_num in all entries of your_row?
  # Function can be used to check this in a column- just change MARGIN.
  # Retursn logical.
  ifelse (all(your_row == your_num), TRUE, FALSE)
}

any_num <- function(your_row, your_num) {
  # As above. 
  ifelse (any(your_row == your_num), TRUE, FALSE)
}
```

### Exploratory: Check if there are any 0's ###
```{r include=TRUE}
# Input needs to be a dataframe, not a row of the dataframe! 
# if col = 0 (MARGIN=2), cell isn't expressing anything; if row = 0, gene is not expressed in any cells (MARGIN=1) 
all_num_logical <- apply(zeb_list$zeb_8hpf, MARGIN=1, FUN=all_num, your_num=0)
all_num_sum <- sum(all_num_logical)
all_num_sum

# Where are these rows? Eventually we want to take the UNION of these and eliminate them from the analyses- just like Tosches! 
where_0 <- as.numeric(which(all_num_logical))
where_0

```

# Helper Function.
```{r include=TRUE}
get_0_indices <- function(your_dataframe) {
  all_num_logical <- apply(your_dataframe, MARGIN=1, FUN=all_num, your_num=0)
  where_0 <- as.numeric(which(all_num_logical))
  return(where_0)
}
```

# Get indices of all genes that are not expressed in any cells. 
```{r include=TRUE}
# Get indices in Ciona. 59
genes_0_ciona <- unique(unlist(map(ciona_list, get_0_indices)))
# Get indices in Zeb. 841
genes_0_zeb <- unique(unlist(map(zeb_list, get_0_indices)))
# Take the union of these. Make sure to unique them! 886
all_genes_0 <- unique(union(genes_0_ciona, genes_0_zeb))
```   

################### REMOVE GENES THAT ARE NOT EXPRESSED IN ANY CELLS -> ciona/zeb_removed_list ###################

```{r include=TRUE}
remove_0_genes <- function(your_dataframe, remove_indices) {
  # After getting the indices (remove_indices) for which there is 0 expression of genes,
  # remove these genes from dataframe.
  removed_df <- your_dataframe[-remove_indices, ]
  return(removed_df)
}
```

# Get rid of the genes.
```{r include=TRUE}
# 2897 x num_cells
ciona_removed_list <- map(ciona_list, remove_0_genes, all_genes_0)
# 2897 x num_cells
zeb_removed_list <- map(zeb_list, remove_0_genes, all_genes_0)
```

############# GSM THEM ciona_removed_list -> ciona_list_gsm ############ 

# Helper Function. 
```{r include=TRUE}
make_gsm <- function(expression_matrix) {
  # Makes Gene Specificity Matrix, Tosches 2018.
  #
  # Args: 
  #   expression_matrix: genes x cells. 
  #   e.g. test_10hpf_collapse (nrow=n_khids x Zeb Noto Cells)
  #
  # Returns:
  #   gsm: Expression of each gene is normalized to its mean expression in all cells.
  gsm <- expression_matrix
  gsm <- gsm %>% mutate(gene_avexp = rowMeans(.)) %>% 
    mutate_at(vars(-gene_avexp), ~.x/gene_avexp) %>% 
    select(-gene_avexp)
  
  return(gsm)
}
```

# Now you have the gsm'ed expression value matrices.
```{r include=TRUE}
ciona_list_gsm <- map(ciona_removed_list, make_gsm)
```

```{r include=TRUE}
zeb_list_gsm <- map(zeb_removed_list, make_gsm)
```

# TEST ALL DFS #
```{r include=TRUE}
test_df <- zeb_list_gsm$zeb_24hpf
```

# (1) Check that there aren't any 0's in any direction.
```{r include=TRUE}
# Input needs to be a dataframe, not a row of the dataframe! 
# if col = 0 (MARGIN=2), cell isn't expressing anything; if row = 0, gene is not expressed in any cells (MARGIN=1) 
all_num_logical <- apply(test_df, MARGIN=1, FUN=all_num, your_num=0)
all_num_sum <- sum(all_num_logical)
all_num_sum
```

# (2) Check that there aren't any NAs anywhere in the dataframe.
```{r include=TRUE}
sum(is.na(test_df))
```
####### CROSS CIONA_LIST_GSM AND ZEB_LIST_GSM TO MAKE PAIRS OF GSM'ED NOTO MATRICES = cross_gsm (c x z) ###### 

```{r include=TRUE}
# Here I want to get pairwise key names. # zeb_list_gsm
cross_gsm <- cross2(ciona_list_gsm, zeb_list_gsm)
```

# Give informative key names.
# CODE REC: These are a lot of lines of code to achieve this...

# Helper Function.
```{r include=TRUE}
give_names <- function(your_list) {
  name_1 <- your_list[[1]]
  name_2 <- your_list[[2]]
  name_flag <- paste0("gsm_", name_1, "/", name_2)
  return(name_flag)
}
```

# REAL
# Get the names
```{r include=TRUE}
cross_gsm_names <- cross2(names(ciona_list_gsm), names(zeb_list_gsm))
cross_gsm_names <- cross_gsm_names %>% map(give_names)

names(cross_gsm) <- cross_gsm_names
```

# REAL
# I want to do a function on each of these pairs- present in [[1]] and [[2]].
```{r include=TRUE}
do_correlation <- function(pairwise_gsm_mats) {
  cat("Starting \n\n")
  ciona_gsm <- pairwise_gsm_mats[[1]]
  zeb_gsm <- pairwise_gsm_mats[[2]]
  corr_output <- corr.test(x= ciona_gsm,
                           y = zeb_gsm,
                           method = "spearman",
                           adjust = "fdr")
  corr_r <- as.numeric(corr_output$r)
  corr_p <- as.numeric(corr_output$p)
  
  ans_list = list(corr_output = corr_output,
                  corr_r = corr_r,
                  corr_p = corr_p)
  
  return(ans_list)
}
```

# TEST
# Try on a small part of gsm_corrs.
```{r include=TRUE}
# Note: this cross_gsm was defined below in the code with test cases and variables. 
test_cross_gsm <- cross_gsm[1]
```

# TEST
# Manually using base -> correlation function in do_correlation (corr.test) is correct.
# Thus, I trust the p_val and r_mat. 
```{r include=TRUE}
test_pairwise <- test_cross_gsm$`gsm_iniG/zeb_8hpf`
test_pair_1 <- test_pairwise[[1]]
test_pair_2 <- test_pairwise[[2]]

test_base_cor <- cor(test_pair_1, test_pair_2, method = "spearman")
```

# TEST
# Using do_correlation function.
```{r include=TRUE}
test_gsm_corrs <- map(test_cross_gsm, do_correlation)
test_gsm_r <- test_gsm_corrs$`gsm_iniG/zeb_8hpf`$r
test_gsm_p <- test_gsm_corrs$`gsm_iniG/zeb_8hpf`$p
```

# TEST
# What is the distribution of these p and r scores?
```{r include=TRUE}
test_gsm_r_dist <- as.numeric(test_gsm_r)
hist(test_gsm_r_dist)
mean(test_gsm_r_dist)
median(test_gsm_r_dist)

test_gsm_p_dist <- as.numeric(test_gsm_p)
hist(test_gsm_p_dist)
mean(test_gsm_p_dist)
median(test_gsm_p_dist)
```

# REAL
```{r include=TRUE}
# List of length 4. 
gsm_corrs <- map(cross_gsm, do_correlation)
names(gsm_corrs) <- cross_gsm_names
```

# REAL:
# Get significant correlations. 
```{r include=TRUE}
get_sig_corrs <- function(corr_output) {
  # corr_output e.g. gsm_test_iniG/test_10hpf (item in test_gsm_corrs list)
  corr_r <- corr_output$r
  corr_p <- corr_output$p
  
  which_p <- which(corr_p < 0.05)
  sig_corr <- corr_r[which_p]
  return(sig_corr)
}
```

# Do for all and give informative names.
```{r include=TRUE}
sig_corrs <- map(gsm_corrs, get_sig_corrs)
sig_corrs_names <- str_remove(names(gsm_corrs), "gsm_")
names(sig_corrs) <- sig_corrs_names
```

# Now take the median!
```{r include=TRUE}
medians <- map_dbl(sig_corrs, median)
medians
```
# Make a matrix -> heatmap
```{r include=TRUE}
heatmap_mat <- as.data.frame(matrix(medians, nrow=length(ciona_list), ncol=length(zeb_list)))

rownames(heatmap_mat) <- names(ciona_list)
colnames(heatmap_mat) <- names(zeb_list)
```

```{r include=TRUE}
ggcorrplot(heatmap_mat)
```
# What if we didn't filter for significant correlations?
```{r include=TRUE}
get_r <- function(corr_output) {
  corr_r <- corr_output$r
  return(corr_r)
}
```

# Get median of all correlations. 
```{r include=TRUE}
test_cor_rs <- map(gsm_corrs, get_r) %>% map_dbl(median)
```

# Turn it into a matrix that you can visualize.
```{r include=TRUE}
test_corr_mat <- as.data.frame(matrix(test_cor_rs, nrow=length(ciona_list), ncol=length(zeb_list)))
rownames(test_corr_mat) <- names(ciona_list)
colnames(test_corr_mat) <- names(zeb_list)
```

```{r include=TRUE}
# c(-0.003, 0.0041) , midpoint = 0.00055, low = "blue", high =  "red", mid = "white"
m <- ggcorrplot(1000*test_corr_mat)
m + scale_fill_gradient2(limit = c(-3, 2), low = "blue", high =  "red", mid = "white")
```

```{r include=TRUE}
hist(test_cor_rs)
```
############### TESTS #################

```{r include=TRUE}
test_df <- data.frame(a = c(NA, 0, 0, 0, 0, 0, 0), b = c(1, 0, 1, 4, 1, 2, 3), d = c(1, 0, 1, 3, 4, 7, 2))
test_df

test_df_2 <- data.frame(a = c(1, 2, 5, 6), b = c(4, 5, 3, 4), d = c(2, 6, 7, 3))
test_df_2

test_df_3 <- data.frame(a = c(1, 2, 3, 4), b = c(5, 6, 7, 8), c = c(9, 10, 11, 12))
test_df_3

test_df_4 <- data.frame(a = c(1, 5, 6, 4), b = c(10, 1, 3, 8), c = c(9, 1, 2, 3))
test_df_4

test_df_5 <- data.frame(a = c(1, 5, 10, 5), b = c(10, 1, 2, 8), c = c(9, 1, 2, 4))
test_df_5
```
```{r include=TRUE}
test_list <- list(test_df = test_df,
                  test_df_2 = test_df_2,
                  test_df_3 = test_df_3)
```

# Are there any NAs?
```{r include=TRUE}
test_df <- test_list$test_df
sum(is.na(test_df))
```

# Remove rows given indices. 
```{r include=TRUE}
test_remove <- c(1, 2, 3)
test_df_remove <- test_df[-test_remove, ]
test_df_remove
```

```{r include=TRUE}
remove_0_genes <- function(your_dataframe, remove_indices) {
  # After getting the indices (remove_indices) for which there is 0 expression of genes,
  # remove these genes from dataframe.
  removed_df <- your_dataframe[-remove_indices, ]
  return(removed_df)
}
```

```{r include=TRUE}
test_df
test_remove <- c(1, 2, 3)
test_2 <- remove_0_genes(test_df, test_remove)
test_2
```


```{r include=TRUE}
test_ans <- map(test_list, remove_0_genes, test_remove)
```

# Check if there are any 0's
```{r include=TRUE}
all_num <- function(your_row, your_num) {
  # Either find all or any of a number in a row. Returns logical.
  ifelse (all(your_row == your_num), TRUE, FALSE)
}

any_num <- function(your_row, your_num) {
  # Either find all or any of a number in a row. Returns logical.
  ifelse (any(your_row == your_num), TRUE, FALSE)
}
```

# Check if you have any and all 0's
```{r include=TRUE}
test_test_df <- test_df
any_num_logical <- apply(test_test_df, MARGIN=2, FUN=any_num, your_num=0)
any_num_sum <- sum(any_num_logical)
any_num_sum

all_num_logical <- apply(test_test_df, MARGIN=2, FUN=all_num, your_num=0)
all_num_sum <- sum(all_num_logical)
all_num_sum

```

#### THERE IS SOMETHING WRONG IN CALLINGT THIS FUNCTION ####

# I want to do a function on each of these pairs- present in [[1]] and [[2]].
```{r include=TRUE}
do_correlation <- function(pairwise_gsm_mats) {
  cat("Starting \n\n")
  ciona_gsm <- pairwise_gsm_mats[[1]]
  zeb_gsm <- pairwise_gsm_mats[[2]]
  corr_output <- corr.test(x= ciona_gsm,
                           y = zeb_gsm,
                           method = "spearman",
                           adjust = "fdr")
  corr_r <- as.numeric(corr_output$r)
  corr_p <- as.numeric(corr_output$p)
  
  ans_list = list(corr_output = corr_output,
                  corr_r = corr_r,
                  corr_p = corr_p)
  
  return(ans_list)
}
```

# Apply cor to all the pairs and get results = gsm_corrs. 
# TEST: Try on a small part of gsm_corrs.

```{r include=TRUE}
# cross_gsm[1:2]
test_cross_gsm <- list(
  list(test_df_2 = test_df_2, test_df_3 = test_df_3),
  list(test_df_4 = test_df_4, test_df_5 = test_df_5))
```

# Give them names
```{r include=TRUE}
names(test_cross_gsm) <- c("2_3", "4_5")
```

```{r include=TRUE}
test_gsm_corrs <- map(test_cross_gsm, do_correlation)
```

