---
title: "test_notoXnoto_pipeline"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r include=FALSE}
library(Seurat)
library(tidyverse)
library(stringr)
library(ggplot2)
library(Matrix)
library(ggcorrplot)
library(psych)
library(reshape2)
```


##########   WE NEED TO UNDERSTAND HOW TO DEAL WITH ZEB DUPLICATES  #########

# Ortho khids and zeb_genes.
```{r include=TRUE}
# 4363 (correct, as expected).
ortho_khids <- unique(ortho_mapping$khid)

# 8548 -> 6490 => There are 1-1 AND many-1 orthologs (ciona -> zeb).
ortho_zeb_genes <- ortho_mapping$zeb_gene
```

```{r include=TRUE}
# This is a dataframe with zeb_genes that have 1-1 and 1-many orthologs. (U)
# 5490 
unique_zeb_gene_df <- ortho_mapping %>% group_by(zeb_gene) %>% summarise(num = n()) %>%
  filter(num == 1)

unique_ortho_zeb_genes <- unique_zeb_gene_df$zeb_gene

# This dataframe has many-1 orthologs. (NU)
# 1000
not_unique_zeb_gene_df <- ortho_mapping %>% group_by(zeb_gene) %>% summarise(num = n()) %>%
  filter(!num == 1)

```
```{r include=TRUE}
# These are the khids that correspond to zeb_genes in U. 
# There will be repeats because there are 1 KHID -> multiple zeb_genes cases.   
# 5490
corr_khid_U <- ortho_mapping %>% filter(zeb_gene %in% unique_ortho_zeb_genes)
# 3766
corr_khids <- unique(corr_khid_U$khid)

# When we use these khids in ortho_dict, we should see the number of zeb_genes is 1 or > 1. Yes!
# 3766
corr_khid_string_df <- ortho_dict %>% filter(khid %in% corr_khids)
corr_khid_strings <- corr_khid_string_df$khid
```







############ STEP 1 #############

# Make the appropriate test variables.
# REAL: "ortho_mapping"
```{r include=TRUE}
ortho_dict <- read.table("/home/pprakriti/Desktop/export_qualified_one2one_many_notoxnoto_dict.csv",
                         sep = ",",
                         header = FALSE,
                         stringsAsFactors = FALSE)
colnames(ortho_dict) <- c("khid", "zeb_gene")

ortho_mapping <- ortho_dict %>%
   separate_rows(zeb_gene, sep = " ")
```

# TEST: Get a subset of khids and corresponding zeb_genes to subset our test matrices with - CORRECT
```{r include=TRUE}
# 4 (Will not need)
test_ortho_khids <- c("KH2012:KH.C4.635", "KH2012:KH.C11.313", "KH2012:KH.C1.571", "KH2012:KH.C5.566") 

# casq2, [foxa, foxa], [plod2, plod1a, plod3], copa
# (Will not need)
# 6
test_ortho_mapping <- ortho_mapping %>% filter(khid %in% test_ortho_khids)
# 6
test_ortho_zeb_genes <- test_ortho_mapping$zeb_gene
```

############ MAKE AND MUNGE test_mats ############

# Helper Function. 
```{r include=TRUE}
modify_mat <- function(mat, subset_genes, col_rowname) {
  # Munges Matrix of batch-corrected values from noto_mats (mat) into a dataframe with 
  # rownames of khids/zeb_genes (mod_mat). Its column name is col_rowname = khid/zeb_gene.
  # subset_genes = ortho_khids/ortho_zeb_genes.
  mod_mat <- as.data.frame(mat[subset_genes, ])
  mod_mat[[col_rowname]] <- rownames(mod_mat)
  return(mod_mat)
}
```

# Do for Ciona.
```{r include=TRUE}
# REAL: subset_iniG <- modify_mat(iniG_noto_mat, ortho_khids, "khid")
test_iniG <- modify_mat(iniG_noto_mat[, 1:5], test_ortho_khids, "khid")
test_earN <- modify_mat(earN_noto_mat[, 1:5], test_ortho_khids, "khid")
test_latN <- modify_mat(latN_noto_mat[, 1:5], test_ortho_khids, "khid")
```

# Do for Zeb.
```{r include=TRUE}
# REAL: subset_10hpf <- modify_mat(zeb_10hpf_noto_mat, ortho_zeb_genes, "zeb_gene")
test_10hpf <- modify_mat(zeb_10hpf_noto_mat[, 1:5], test_ortho_zeb_genes, "zeb_gene")
test_14hpf <- modify_mat(zeb_14hpf_noto_mat[, 1:5], test_ortho_zeb_genes, "zeb_gene")
```

############# COLLAPSE ZEB MATS -> timepoint*_collapse #############
 
# Helper Function.  
```{r include=TRUE}
collapse_zeb_mat <- function(zeb_mat, ortho_mapping) {
  # zeb_mat (n_zeb_genes x cells + zeb_gene) + ortho_mapping -> 
  # zeb_collapse (n_khids, cells). "Collapse" refers to summing zeb_orthos.
  zeb_collapse <- zeb_mat %>% left_join(ortho_mapping)
  zeb_collapse <- zeb_collapse %>% group_by(khid) %>%
  summarize((across(starts_with("DEW"), sum))) %>%
  select(-khid)
return(zeb_collapse)
}
```

```{r include=TRUE}
test_10hpf_collapse <- collapse_zeb_mat(test_10hpf, test_ortho_mapping)
test_14hpf_collapse <- collapse_zeb_mat(test_14hpf, test_ortho_mapping)
```

############ GET RID OF KHID COLUMNS IN ciona_matrices -> ##############
# You also want to get rid of the khid columns in the Ciona Matrices.

```{r include=TRUE}
remove_khid_column <- function(ciona_matrix) {
  clean_ciona_matrix <- ciona_matrix %>% select(-khid)
  return(clean_ciona_matrix)
}
```

```{r include=TRUE}
test_iniG_clean <- remove_khid_column(test_iniG)
test_earN_clean <- remove_khid_column(test_earN)
test_latN_clean <- remove_khid_column(test_latN)
```

############# PART 5 #############
# TEST: Make list of test_mats (clean and collapsed). They have same nrows.

```{r include=TRUE}
# REAL: ciona_list = {subset_iniG...}
test_ciona_list = list(test_iniG = test_iniG_clean,
                       test_earN = test_earN_clean,
                       test_latN = test_latN_clean)
```

```{r include=TRUE}
# REAL: zeb_list = {subset_10hpf...}
test_zeb_list = list(test_10hpf = test_10hpf_collapse,
                     test_14hpf = test_14hpf_collapse)
```

##############  PART 6  #############
# GSM them. 

# Helper Function. 
```{r include=TRUE}
make_gsm <- function(expression_matrix) {
  # Makes Gene Specificity Matrix, Tosches 2018.
  #
  # Args: 
  #   expression_matrix: genes x cells. 
  #   e.g. test_10hpf_collapse (nrow=n_khids x Zeb Noto Cells)
  #
  # Returns:
  #   gsm: Expression of each gene is normalized to its mean expression in all cells.
  gsm <- expression_matrix
  gsm <- gsm %>% mutate(gene_avexp = rowMeans(.)) %>% 
    mutate_at(vars(-gene_avexp), ~.x/gene_avexp) %>% 
    select(-gene_avexp)
  
  return(gsm)
}
```

# Now you have the gsm'ed expression value matrices.
```{r include=TRUE}
test_ciona_list_gsm <- map(test_ciona_list, make_gsm)
test_zeb_list_gsm <- map(test_zeb_list, make_gsm)
```

###### 
# Cross test_ciona_list_gsm and test_zeb_list_gsm to make pairs of gsm'ed noto matrices (c x z) = test_cross_gsm. 
```{r include=TRUE}
# Here I want to get pairwise key names. 
test_cross_gsm <- cross2(test_ciona_list_gsm, test_zeb_list_gsm)
```

# Give informative key names.
# CODE REC: These are a lot of lines of code to achieve this...

# Helper Function.
```{r include=TRUE}
give_names <- function(your_list) {
  name_1 <- your_list[[1]]
  name_2 <- your_list[[2]]
  name_flag <- paste0("gsm_", name_1, "/", name_2)
  return(name_flag)
}
```

# Get the names - CORRECT 
```{r include=TRUE}
test_cross_gsm_names <- cross2(names(test_ciona_list_gsm), names(test_zeb_list_gsm))
test_cross_gsm_names <- test_cross_gsm_names %>% map(give_names)

names(test_cross_gsm) <- test_cross_gsm_names
```

# I want to do a function on each of these pairs- present in [[1]] and [[2]].
```{r include=TRUE}
do_correlation <- function(pairwise_gsm_mats) {
  ciona_gsm <- pairwise_gsm_mats[[1]]
  zeb_gsm <- pairwise_gsm_mats[[2]]
  corr_output <- corr.test(x= ciona_gsm,
                           y = zeb_gsm,
                           method = "spearman",
                           adjust = "fdr")
  return(corr_output)
}
```

# Apply cor to all the pairs and get results = test_gsm_corrs. 
```{r include=TRUE}
# List of length 4. 
test_gsm_corrs <- map(test_cross_gsm, do_correlation)
names(test_gsm_corrs) <- test_cross_gsm_names
```

# Get significant correlations. 
```{r include=TRUE}
get_sig_corrs <- function(corr_output) {
  # corr_output e.g. gsm_test_iniG/test_10hpf (item in test_gsm_corrs list)
  corr_r <- corr_output$r
  corr_p <- corr_output$p
  
  which_p <- which(corr_p < 0.05)
  sig_corr <- corr_r[which_p]
  return(sig_corr)
}
```

# Do for all and give informative names.
```{r include=TRUE}
test_sig_corrs <- map(test_gsm_corrs, get_sig_corrs)
test_sig_corrs_names <- str_remove(names(test_gsm_corrs), "gsm_")
names(test_sig_corrs) <- test_sig_corrs_names
```

# Now take the median!
```{r include=TRUE}
test_medians <- map_dbl(test_sig_corrs, median)
test_medians
```

# Make a matrix -> heatmap
```{r include=TRUE}
test_heatmap_mat <- as.data.frame(matrix(test_medians, nrow=length(test_ciona_list), ncol=length(test_zeb_list)))

rownames(test_heatmap_mat) <- names(test_ciona_list)
colnames(test_heatmap_mat) <- names(test_zeb_list)
```

# Just for testing
```{r include=TRUE}
test_NA_indices <- is.na(test_heatmap_mat)
test_heatmap_mat[test_NA_indices] <- c(0.4, 0.1, 0.8, 0.2)
```

```{r include=TRUE}
ggcorrplot(test_heatmap_mat)
```

############# TESTS ###############
# Helper Function works as expected. 
```{r include=TRUE}
test_sig_cor_fn <- get_sig_corrs(test_gsm_corrs$`test_earN/test_10hpf`)
```

# Individual testing
```{r include=TRUE}
test_pair_output <- test_gsm_corrs$`gsm_test_latN/test_10hpf`
test_corr_r <- test_pair_output$r
test_corr_p <- test_pair_output$p
  
test_which_p <- which(test_corr_p < 0.05)
test_sig_corr <- test_corr_r[test_which_p]
```

# Note: Make sure you get the list names. 
# "corr" + original name. 

# Each key of test_gsm_corrs is an output of corr.test. 
# pairwise correlation of all cells in ciona_noto (t_c = 10) and zeb_noto (t_z = 5)
# I want to take the median of all the entries in the dataframe. (1 number -> 50 numbers)
# The medians are the entries of test_mat. test_mat is named! 
```{r include=TRUE}
# vector of length 4.
test_mat <- test_gsm_corrs %>% map(as.matrix) %>% map_dbl(median)
```

# Make the dataframe with row and col names.
# (1) Make a matrix. Then convert. nrow = c; ncol = z.
```{r include=TRUE}
test_mat_2 <- matrix(test_mat, nrow = length(test_list_1), ncol = length(test_list_2))
test_df <- as.data.frame(test_mat_2)
# give them nice col and row names. (You can do this manually).
```



##########################

TESTS

```{r include=TRUE}
testing_mod <- modify_mat(test_ortho_zeb_genes, zeb_10hpf_noto_mat[, 1:5], "zeb_gene")
```

