---
title: "test_4D_file_read"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# PURPOSE OF PIPELINE: To have/use Chen's raw 4D matrices in Vera
#                      because Seurat in Vera can't read in h5 files
#                      so I'm doing h5 reading in Mac and then exporting
#                      the sparse matrix and its dimnames to Vera.

```{r pressure, echo=FALSE}
library(Seurat)
library(Matrix)
```

########################## START DO ON MAC: Write out h5_matrix ##########################
iniG1 -> midG2: Did manually
earN2 -> midG1: Done in code chunks below

##########################################################################################

#### earN2 #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764769_earN2_raw_gene_bc_matrices_h5.h5"
stage_name <- "earN2"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

#### latN1 #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764770_latN1_raw_gene_bc_matrices_h5.h5"
stage_name <- "latN1"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

#### latN2 #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764771_latN2_raw_gene_bc_matrices_h5.h5"
stage_name <- "latN2"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

#### iniTI1 #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764772_iniTI1_raw_gene_bc_matrices_h5.h5"
stage_name <- "iniTI1"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

#### iniTI2 #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764773_iniTI2_raw_gene_bc_matrices_h5.h5"
stage_name <- "iniTI2"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

#### earTI1 #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764774_earTI1_raw_gene_bc_matrices_h5.h5"
stage_name <- "earTI1"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

#### earTI2 #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764775_earTI2_raw_gene_bc_matrices_h5.h5"
stage_name <- "earTI2"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

#### midTII1 #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764776_midTII1_raw_gene_bc_matrices_h5.h5"
stage_name <- "midTII1"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

#### midTII2 #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764777_midTII2_raw_gene_bc_matrices_h5.h5"
stage_name <- "midTII2"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

#### latTI1a #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764778_latTI1a_raw_gene_bc_matrices_h5.h5"
stage_name <- "latTI1a"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

#### latTI1b #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764779_latTI1b_raw_gene_bc_matrices_h5.h5"
stage_name <- "latTI1b"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

#### latTI2 #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764780_latTI2_raw_gene_bc_matrices_h5.h5"
stage_name <- "latTI2"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

#### latTII1a #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764781_latTII1a_raw_gene_bc_matrices_h5.h5"
stage_name <- "latTII1a"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

#### latTII1b #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764782_latTII1b_raw_gene_bc_matrices_h5.h5"
stage_name <- "latTII1b"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

#### latTII2 #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764783_latTII2_raw_gene_bc_matrices_h5.h5"
stage_name <- "latTII2"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

#### larva1 #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764784_larva1_raw_gene_bc_matrices_h5.h5"
stage_name <- "larva1"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```


#### larva2 #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764785_larva2_raw_gene_bc_matrices_h5.h5"
stage_name <- "larva2"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

#### larva3 #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764786_larva3_raw_gene_bc_matrices_h5.h5"
stage_name <- "larva3"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

#### midG1 #####
```{r include=TRUE}

####################################
# SET THESE

stage_file_name <- "GSM3764766_midG1_raw_gene_bc_matrices_h5.h5"
stage_name <- "midG1"

####################################

# Directory from where I will access raw matrix.
mac_dir <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/4D_GSE131155_RAW/"
# Directory where I will place output files.
mac_dir_2 <- "~/Google Drive (ppaul@princeton.edu)/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_dir <- paste0(mac_dir, stage_file_name)

h5_matrix_out_name <- paste0(mac_dir_2, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(mac_dir_2, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(mac_dir_2, stage_name, "_colnames.csv")

####################################

### Export h5_matrix + dimnames ### 
h5_matrix <- Read10X_h5(h5_matrix_dir)

writeMM(h5_matrix, h5_matrix_out_name)

write.table(rownames(h5_matrix),
            h5_matrix_rownames_csv,
            row.names = FALSE,
            col.names = FALSE)

write.table(colnames(h5_matrix), 
            h5_matrix_colnames_csv,
            row.names = FALSE,
            col.names = FALSE)
```

############################### END ON MAC ###################################

FINISHED earN1 -> midG1 

############################### START ON VERA ##################################

Manually updated stage_name and final_matrix_name variables

###############################################################################

## Make h5_matrix_in
```{r include=TRUE}

######################################

stage_name <- "iniG1"

#######################################

# same as mac_dir_2 (where the output files are)
vera_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology Maps/h5_munging/h5_munging_output_files/"

h5_matrix_out_name <- paste0(vera_dir, stage_name, "_out.txt")

h5_matrix_rownames_csv <- paste0(vera_dir, stage_name, "_rownames.csv")

h5_matrix_colnames_csv <- paste0(vera_dir, stage_name, "_colnames.csv")

###

h5_matrix_in <- readMM(h5_matrix_out_name)

h5_matrix_rownames <- read.table(h5_matrix_rownames_csv,
                             header = FALSE,
                             stringsAsFactors = FALSE)$V1

h5_matrix_colnames <- read.table(h5_matrix_colnames_csv,
                             header = FALSE,
                             stringsAsFactors = FALSE)$V1

rownames(h5_matrix_in) <- h5_matrix_rownames

colnames(h5_matrix_in) <- h5_matrix_colnames
```

# Rename h5_matrix_in
```{r include=TRUE}
final_matrix_name <- h5_matrix_in
```

