---
title: "ciona_larvae_clustering"
output: html_document
---
## 10/2020: Make Integrated Seurat Object that has all batch-corrected values.

## (Failed) 9/21/20: More fine-grained Clustering.

# Follows from: orthology_maps_data_inputs.Rmd.

# (Can) work in parallel with: zeb_degs_heatmaps.Rmd.

# General Description: Maps all tissues using previous markers in clean_chen_larva_integrated_20.
# Also gets cell names from ClusterIDs.

# Env Used: env_ciona_larvae_clustering.RData.

# Complete Pipeline:

# (1) For each larva dataset, makes larva*_seurat. These are unscaled!
# (2) Each larva*_seurat is subsetted based on chen_min_features (1000) and chen_max_features (5000). This ensures that every cell has between 1000 and 5000 genes.  
# These create chen_larva*_seurat.

# (3) chen_larva*_seurats are scaled -> chen_larva*_seurat_scaled. 
# These then undergo PCA -> ... -> Cluster.
# (4) Maps tissues. 
# (5) Records unmapped clusters.
# !!! (6) chen_larva*_seurat (unscaled) is subsetted -> clean_chen_larva*_seurat (unscaled).

# Note: We found unmapped clusters using SCALED seurats for each dataset,
# but will subset UNSCALED seurats for use in Integration. 

## Make Integrated Seurat Object
# (7) clean_chen_larva*_seurats -> Integration -> clean_chen_larva_integrated_20.
# (8) integrated_seurat is Scaled -> ... -> Cluster.
# (9) Tissues are mapped. Unmapped tissues are also recorded .

## Need to specifically identify Heart + Muscle
# (10) Clusters 19, 32, and 29 from clean_chen_larva_integrated_20 are isolated.
# (11) DEGs + Aniseed expression patterns are validated.
# (12) They are subclustered into putative_hm_seurat.
# (13) Heart + Muscle are cleanly identified.

## Makes lists of cells 
# They are called (ciona_larva_*).

# Segways into: get_pairwise_zeb_ciona_degs.Rmd.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(Seurat)
library(dplyr)
library(ggplot2)
library(purrr)
library(Hmisc)
library(pvclust)
library(URD)
library(harmony)
```

# Late Stage Markers 
```{r include=TRUE}
dopa_markers = c("KH2012:KH.C10.200", "KH2012:KH.C3.666")
cns_markers = c("KH2012:KH.C14.4", "KH2012:KH.C1.127", "KH2012:KH.C7.59", "KH2012:KH.C6.224")
noto_markers = c("KH2012:KH.C5.124", "KH2012:KH.C8.749")
epi_markers = c("KH2012:KH.C1.611", "KH2012:KH.C8.844")
mes_markers = c("KH2012:KH.C5.228", "KH2012:KH.C5.202", "KH2012:KH.C1.222")
endo_markers = c("KH2012:KH.C5.227", "KH2012:KH.S1012.1")
mus_markers = c("KH2012:KH.S423.6", "KH2012:KH.L116.38", "KH2012:KH.C7.504")
# last 2 are HAND2s
heart_markers = c("KH2012:KH.C7.205", "KH2012:KH.C1.1116", "KH2012:KH.C14.604")
```

############# START: Make Seurat Objects with all Batch-Corrected Values (11/2020) ############

# Harmony Test 
```{r include=TRUE}
data(cell_lines)
V <- cell_lines$scaled_pcs
meta_data <- cell_lines$meta_data
```

# (1) Make Larva Seurats (...FindVariableFeatures)
```{r include=TRUE}
# 13933 x 28234
batch_larva1_seurat <- make_ciona_seurat(larva1_matrix, 3, 200, 15269)
# 13907 x 12406 
batch_larva2_seurat <- make_ciona_seurat(larva2_matrix, 3, 200, 15269)
# 14067 x 7143
batch_larva3_seurat <- make_ciona_seurat(larva3_matrix, 3, 200, 15269)
```
"""
Let's now proceed with Batch Correction Procedure
"""

```{r include=TRUE}
batch_clean_chen_larva_list <- list(batch_larva1_seurat, batch_larva2_seurat, batch_larva3_seurat)
```

```{r include=TRUE}
batch_chen_larva_integrated_20 <- make_integrated_seurat(batch_clean_chen_larva_list, 20)
```

"""
Helper Function for Integration 
"""
```{r include=TRUE}
# ~30 mins
make_integrated_seurat <- function(object_list, dims){
  # Args:
    # object_list: list of Seurat objects. e.g. zeb_seurat_list.
    # dims: input dimensions for FindIntegrationAnchors and IntegrateData. 
    # npcs: # pcs for PCA and TSNE.
  
  # Routine: Do integration. Scale.
  
  # Returns:
    # integrated_seurat: output of above routine.
  
  zeb_anchors <- FindIntegrationAnchors(object.list = object_list,
                                      dims = 1:dims)
  zeb_integrated <- IntegrateData(anchorset = zeb_anchors, dims = 1:dims)
  
  DefaultAssay(zeb_integrated) <- "integrated"
  
  zeb_integrated <- ScaleData(zeb_integrated, verbose = FALSE)
  
  return(zeb_integrated)
}
```

"""
Pick #Anchors (20)
"""
```{r include=TRUE}
# ~6 mins
clean_chen_larva_integrated_20 <- make_integrated_seurat(clean_chen_larva_list, 20)
```


############# END: Make Seurat Objects with all Batch-Corrected Values (11/2020) ############

















############# PREVIOUS PIPELINES TO GENERATE CLEAN_CHEN_INTEGRATED_20 ###############
"""
Helper Function: Make Seurat Object and Find n_features Variable Genes
"""
```{r include=TRUE}
make_ciona_seurat <- function(ciona_df, min_cells, min_features, n_features){
  ciona_seurat <- CreateSeuratObject(counts = ciona_df,
                                     min.cells = min_cells, 
                                     
                                     min.features = min_features)
  
  ciona_seurat <- NormalizeData(object = ciona_seurat)
  ciona_seurat <- FindVariableFeatures(ciona_seurat, 
                                       selection.method = "vst",
                                       nfeatures = n_features)
  return(ciona_seurat)
}
```

"""
-First 3 variables were used to make larva*_seurats
-chen_ciona_min_cells, chen_min/max_features same for chen_larva*_seurats
-chen_max_features_ depend on nGene distributions for each larva*_seurat_1/2 
came from mean and sd of corresponding larva seurats 
"""
```{r include=TRUE}
ciona_min_cells <- 3
ciona_min_features <- 200
ciona_n_features <- 2000

chen_ciona_min_cells <- 3
chen_min_features <- 1000
chen_max_features <- 5000

# unused 
chen_max_features_1 <- 528+5*705
chen_max_features_2 <- 1002+5*1012
```

# (1) Make Larva Seurats
```{r include=TRUE}
# 28234
larva1_seurat <- make_ciona_seurat(larva1_matrix, ciona_min_cells, ciona_min_features, ciona_n_features)
# 12406
larva2_seurat <- make_ciona_seurat(larva2_matrix, ciona_min_cells, ciona_min_features, ciona_n_features)
# 7144
larva3_seurat <- make_ciona_seurat(larva3_matrix, ciona_min_cells, ciona_min_features, ciona_n_features)
```

"""
Look at Larva* Distributions 
"""
```{r include=TRUE}
density_testing_seurat <- chen_larva3_seurat_scaled
var_features <- chen_larva3_seurat_scaled@assays$RNA@var.features

# var_features[1:10]
VlnPlot(object = density_testing_seurat, features = c("nFeature_RNA", "nCount_RNA"))
```

```{r include=TRUE}
n_count_density <- density(density_testing_seurat$nCount_RNA)
n_feats <- density_testing_seurat$nFeature_RNA
n_feat_density <- density(n_feats)

n_feat_density
plot(n_feat_density)

cat("mean = ", mean(n_feats), "\n\n")
cat("sd = ", sd(n_feats), "\n\n")
cat("5 sd's above mean = ", mean(n_feats)+sd(n_feats)*5)
```

"""
Now subset based on chen_max_features -> chen_larva_seurat
"""

```{r include=TRUE}
chen_larva1_seurat <- subset(larva1_seurat, subset = nFeature_RNA > chen_min_features & nFeature_RNA < chen_max_features)
```

```{r include=TRUE}
chen_larva2_seurat <- subset(larva2_seurat, subset = nFeature_RNA > chen_min_features & nFeature_RNA < chen_max_features)
```

```{r include=TRUE}
chen_larva3_seurat <- subset(larva3_seurat, subset = nFeature_RNA > chen_min_features & nFeature_RNA < chen_max_features)
```

"""
Add MetaData that reflects batch #
"""
```{r include=TRUE}
chen_len_1 <- length(colnames(x = chen_larva1_seurat))
metadata_1 <- rep("larva1", chen_len_1)

chen_larva1_seurat$larva_batch <- metadata_1
chen_larva1_seurat_scaled$larva_batch <- metadata_1

# 2
chen_len_2 <- length(colnames(x = chen_larva2_seurat))
metadata_2 <- rep("larva2", chen_len_2)

chen_larva2_seurat$larva_batch <- metadata_2
chen_larva2_seurat_scaled$larva_batch <- metadata_2

# 3
chen_len_3 <- length(colnames(x = chen_larva3_seurat))
metadata_3 <- rep("larva3", chen_len_3)

chen_larva3_seurat$larva_batch <- metadata_3
chen_larva3_seurat_scaled$larva_batch <- metadata_3

```

"""
Scale, PCA, TSNE 
"""
```{r include=TRUE}
ElbowPlot(chen_larva3_seurat_scaled)
```

```{r include=TRUE}
chen_larva1_seurat_scaled <- chen_larva1_seurat

chen_larva1_seurat_scaled <- ScaleData(chen_larva1_seurat_scaled)

chen_larva1_seurat_scaled <- RunPCA(chen_larva1_seurat_scaled, npcs = 10, verbose = FALSE)
chen_larva1_seurat_scaled <- RunTSNE(chen_larva1_seurat_scaled, npcs = 10, verbose = FALSE)
```

```{r include=TRUE}
chen_larva2_seurat_scaled <- chen_larva2_seurat

chen_larva2_seurat_scaled <- ScaleData(chen_larva2_seurat_scaled)

chen_larva2_seurat_scaled <- RunPCA(chen_larva2_seurat_scaled, npcs = 10, verbose = FALSE)
chen_larva2_seurat_scaled <- RunTSNE(chen_larva2_seurat_scaled, npcs = 10, verbose = FALSE)
```

```{r include=TRUE}
chen_larva3_seurat_scaled <- chen_larva3_seurat

chen_larva3_seurat_scaled <- ScaleData(chen_larva3_seurat_scaled)

chen_larva3_seurat_scaled <- RunPCA(chen_larva3_seurat_scaled, npcs = 10, verbose = FALSE)
chen_larva3_seurat_scaled <- RunTSNE(chen_larva3_seurat_scaled, npcs = 10, verbose = FALSE)
```

"""
Cluster + Map Tissues
"""
```{r include=TRUE}
chen_larva1_seurat_scaled <- FindNeighbors(chen_larva1_seurat_scaled, dims = 1:10)
chen_larva1_seurat_scaled <- FindClusters(chen_larva1_seurat_scaled, resolution = 1)
```

```{r include=TRUE}
chen_larva2_seurat_scaled <- FindNeighbors(chen_larva2_seurat_scaled, dims = 1:10)
chen_larva2_seurat_scaled <- FindClusters(chen_larva2_seurat_scaled, resolution = 0.5)
```

```{r include=TRUE}
chen_larva3_seurat_scaled <- FindNeighbors(chen_larva3_seurat_scaled, dims = 1:10)
chen_larva3_seurat_scaled <- FindClusters(chen_larva3_seurat_scaled, resolution = 0.5)
```

"""
Visualize + Map Tissues
"""
```{r include=TRUE}
DimPlot(chen_larva2_seurat_scaled, 
        reduction = "tsne",
        label = TRUE)
```

```{r include=TRUE}

FeaturePlot(object = chen_larva3_seurat_scaled,
            features = endo_markers,
            reduction = "tsne",
            label = TRUE)
```

"""
Figure out which clusters you will throw away
"""
```{r include=TRUE}
table(Idents(chen_larva1_seurat_scaled))
```

"""
Create "Clean Seurat Objects" from chen_larva*_seurats (Not scaled!) that lack above clusters
"""
# 1
```{r include=TRUE}
cells_to_remove_1 <- WhichCells(chen_larva1_seurat_scaled,
                                idents = 3)

cells_to_keep_1 <- setdiff(colnames(chen_larva1_seurat_scaled), cells_to_remove_1)

clean_chen_larva1_seurat <- subset(chen_larva1_seurat,
                                   cells = cells_to_keep_1)
```

# 2
```{r include=TRUE}
cells_to_remove_2 <- WhichCells(chen_larva2_seurat_scaled,
                                idents = c(6, 13))

cells_to_keep_2 <- setdiff(colnames(chen_larva2_seurat_scaled), cells_to_remove_2)

clean_chen_larva2_seurat <- subset(chen_larva2_seurat,
                                   cells = cells_to_keep_2)
```

# 3
```{r include=TRUE}
cells_to_remove_3 <- WhichCells(chen_larva3_seurat_scaled,
                                idents = c(12, 14, 15, 16, 18))

cells_to_keep_3 <- setdiff(colnames(chen_larva3_seurat_scaled), cells_to_remove_3)

clean_chen_larva3_seurat <- subset(chen_larva3_seurat,
                                   cells = cells_to_keep_3)
```

"""
Let's now proceed with Batch Correction Procedure
"""

```{r include=TRUE}
clean_chen_larva_list <- list(clean_chen_larva1_seurat, clean_chen_larva2_seurat, clean_chen_larva3_seurat)
```

"""
Helper Function for Integration 
"""
```{r include=TRUE}
# ~30 mins
make_integrated_seurat <- function(object_list, dims){
  # Args:
    # object_list: list of Seurat objects. e.g. zeb_seurat_list.
    # dims: input dimensions for FindIntegrationAnchors and IntegrateData. 
    # npcs: # pcs for PCA and TSNE.
  
  # Routine: Do integration. Scale.
  
  # Returns:
    # integrated_seurat: output of above routine.
  
  zeb_anchors <- FindIntegrationAnchors(object.list = object_list,
                                      dims = 1:dims)
  zeb_integrated <- IntegrateData(anchorset = zeb_anchors, dims = 1:dims)
  
  DefaultAssay(zeb_integrated) <- "integrated"
  
  zeb_integrated <- ScaleData(zeb_integrated, verbose = FALSE)
  
  return(zeb_integrated)
}
```

"""
Pick #Anchors (20)
"""
```{r include=TRUE}
# ~6 mins
clean_chen_larva_integrated_20 <- make_integrated_seurat(clean_chen_larva_list, 20)
```

"""
Perform PCA, TSNE
"""
```{r include=TRUE}
npcs <- 15
clean_chen_larva_integrated_20 <- RunPCA(clean_chen_larva_integrated_20, npcs = npcs, verbose = FALSE)
clean_chen_larva_integrated_20 <- RunTSNE(clean_chen_larva_integrated_20, dims = 1:npcs)
```

```{r include=TRUE}
ElbowPlot(clean_chen_larva_integrated_20)
```

"""
Ensure that Batch Correction worked
"""
```{r include=TRUE}
# Beautiful!
DimPlot(clean_chen_larva_integrated_20, 
        reduction = "tsne",
        label = TRUE,
        group.by = "larva_batch")
```

"""
Visualize + Map Tissues
"""
```{r include=TRUE}
clean_chen_larva_integrated_20 <- FindNeighbors(clean_chen_larva_integrated_20, dims = 1:15)
clean_chen_larva_integrated_20 <- FindClusters(clean_chen_larva_integrated_20, resolution = 1)
```

```{r include=TRUE}
# SMYD1, ATP2A1, CSMD1; ASB15
DimPlot(clean_chen_larva_integrated_20, 
        reduction = "tsne",
        label = TRUE)
```

```{r include=TRUE}
FeaturePlot(object = clean_chen_larva_integrated_20,
            features = heart_markers,
            reduction = "tsne",
            label = TRUE)
```
"""
Let us identify heart + muscle
"""

"""
Helper Functions to get Munged Markers
"""
```{r include=TRUE}
munge_markers <- function(markers){
  # Given the output of FindMarkers, we get genes whose avg_logFC > 0.5.
  # These genes are ordered in nondecreasing order of avg_logFC.
  # We also check that p_val_adj < 0.05
  #
  # Args:
  #   markers: Output of FindMarkers (dataframe)
  #
  # Returns:
  #   munged_markers: munged dataframe of KHIDs
  munged_markers <- markers
  munged_markers <- munged_markers[order(-munged_markers$avg_logFC), ]
  munged_markers <- munged_markers[munged_markers$p_val_adj < 0.05, ]

  return(munged_markers)
}
```

# Helper Function to get dataframe top50 genes 
```{r include=TRUE}
get_top_n_df <- function(cell_type, seurat_object, test_use, n_top) {
  # Given a cell type (output of WhichCells), get n_top DEGs using FindMarkers
  # with test of preference and custom munge_markers function 
  # (ref docstring with details)
  #
  # Args and Returns: Self-explanatory
  cell_type_markers <- FindMarkers(object = seurat_object,
                                     ident.1 = cell_type,
                                     test.use = test_use)
  
  munged_cell_type_markers <- munge_markers(cell_type_markers)[1:n_top, ]
  
  return(munged_cell_type_markers)
}
```

"""
Get marker genes of Cluster 17 (putative heart), compare to in situ data in Aniseed
"""
# Top 10 genes- heart+muscles, expressed in tail muscles!  
```{r include=TRUE}
cluster_17_cells <- WhichCells(clean_chen_larva_integrated_20,
                               idents = 17)

cluster_17_top50_markers <- get_top_n_df(cluster_17_cells, clean_chen_larva_integrated_20, "MAST", 50)

write.csv(rownames(cluster_17_top50_markers), "cluster_17_putative_heart_top50_markers.csv")
```

"""
Try above for Cluster 32
"""
# Epi, neuronal, and tail muscles- I think there might be something here.
```{r include=TRUE}
cluster_32_cells <- WhichCells(clean_chen_larva_integrated_20,
                               idents = 32)

cluster_32_top50_markers <- get_top_n_df(cluster_32_cells, clean_chen_larva_integrated_20, "MAST", 50)

write.csv(rownames(cluster_32_top50_markers), "cluster_32_putative_heart_top50_markers.csv")
```

"""
Try above for Cluster 29
"""
# There might be something in here too.
```{r include=TRUE}
cluster_29_cells <- WhichCells(clean_chen_larva_integrated_20,
                               idents = 29)

cluster_29_top50_markers <- get_top_n_df(cluster_29_cells, clean_chen_larva_integrated_20, "MAST", 50)

write.csv(rownames(cluster_29_top50_markers), "cluster_29_putative_heart_top50_markers.csv")
```

"""
Subcluster 17, 32, 29 ->
putative_hm_seurat
"""
```{r include=TRUE}
cells_to_keep_hm <- WhichCells(clean_chen_larva_integrated_20,
                               idents = c(17, 32, 29))

putative_hm_seurat <- subset(clean_chen_larva_integrated_20,
                             cells = cells_to_keep_hm)
```

# Pool all cells and re-cluster
```{r include=TRUE}
putative_hm_seurat <- putative_hm_seurat

putative_hm_seurat <- ScaleData(putative_hm_seurat)

putative_hm_seurat <- RunPCA(putative_hm_seurat, npcs = 7, verbose = FALSE)
putative_hm_seurat <- RunTSNE(putative_hm_seurat, npcs = 7, verbose = FALSE)
```
```{r include=TRUE}
# Done for 10 PCs
ElbowPlot(putative_hm_seurat)
```
"""
Cluster + Map Tissues
"""
```{r include=TRUE}
putative_hm_seurat <- FindNeighbors(putative_hm_seurat, dims = 1:7)
putative_hm_seurat <- FindClusters(putative_hm_seurat, resolution = 1)
```
```{r include=TRUE}
# HAND2's c("KH2012:KH.C1.1116", "KH2012:KH.C14.604")
DimPlot(object = putative_hm_seurat,
        reduction = "tsne",
        label = TRUE)
```

```{r include=TRUE}
# HAND2's c("KH2012:KH.C1.1116", "KH2012:KH.C14.604")
# trunk ventral cells! 
FeaturePlot(object = clean_chen_larva_integrated_20,
            features = cns_markers,
            reduction = "tsne",
            label = FALSE)
```

"""
Let us now make lists of cells
"""
```{r include=TRUE}
# 3274
ciona_larva_endo <- WhichCells(clean_chen_larva_integrated_20,
                               idents = c(12, 2, 20, 3, 0))
# 1959
ciona_larva_epi <- WhichCells(clean_chen_larva_integrated_20,
                              idents = c(28, 5, 25, 4, 18, 19))
# 4203
ciona_larva_mes <- WhichCells(clean_chen_larva_integrated_20,
                              idents = c(7, 30, 13, 21, 23, 1, 11, 22, 8, 10, 35, 14, 6))
# 159
ciona_larva_mus <- WhichCells(putative_hm_seurat,
                              idents = c(7, 4, 3, 6, 8))
# 207
ciona_larva_heart <- WhichCells(putative_hm_seurat,
                                idents = c(2, 1, 0))
# 1033
ciona_larva_cns <- WhichCells(clean_chen_larva_integrated_20,
                              idents = c(26, 9, 15, 24))
# 550
ciona_larva_noto <- WhichCells(clean_chen_larva_integrated_20,
                               idents = 27)

```


##############               Chen's generosity            ############### 
```{r include=TRUE}
plotTree(mesen.k250s6w4.tree.built.name, "stage", title="Developmental Stage")
```
```{r include=TRUE}
plotTree(mesen.k250s6w4.tree.built.name, "segment", title="URD tree segment")
plotDim(mesen.k250s6w4.tree.built.name, "segment", plot.title="URD tree segment")
plotDists(mesen.k250s6w4.tree.built.name, "pseudotime", "stage", plot.title="Pseudotime by stage")
```







##################### UNUSED ######################
############### FAIL: START IDENTIFY ALL TISSUES IN LARVA START 9/21/20 ##################

# 110-Cell Markers for Unambiguous Tissue ID 
```{r include=TRUE}
# CNS-A, CNS-b, CNA-a, muscle, germ, notochord, epi-a, heart, nodal 
chen_features <- c("KH2012:KH.C6.122", "KH2012:KH.C2.957", "KH2012:KH.S544.3",
                   "KH2012:KH.S423.6", "KH2012:KH.C1.755", "KH2012:KH.S1404.1",
                   "KH2012:KH.C12.323", "KH2012:KH.C3.100")

####################################################################################################
# Additional Chen's 4D paper Markers

# a-epi 
emc <- "KH2012:KH.C7.692"
ci_zf041 <- "KH2012:KH.C4.378"
emc2 <- "KH2012:KH.C7.157"
rar <- "KH2012:KH.C9.580"

# b-epi 
ci_zf264 <- "KH2012:KH.C9.561"
orphan_bhlh1 <- "KH2012:KH.C7.269"
not <- "KH2012:KH.L172.23"
sp8 <- "KH2012:KH.C13.22"
soxb2 <- "KH2012:KH.S164.12"

# A/B-noto
brachury <- "KH2012:KH.S1404.1"
mnx <- "KH2012:KH.L128.12"

# A-noto
ephrinA_a <- "KH2012:KH.C3.762"
socs1_2_3_cis <- "KH2012:KH.L71.9"

# B-noto
hes_a <- "KH2012:KH.C1.159"
# find these below first red block in heatmap 
lefty <- "KH2012:KH.C3.411"
noggin <- "KH2012:KH.C12.562"

# germ cells
macho_1 <- "KH2012:KH.C1.727"
ci_zf262 <- "KH2012:KH.C1.1016"
ci_zf114 <- "KH2012:KH.L154.37"

# heart
mesp <- "KH2012:KH.C3.100"
ci_zf571 <- "KH2012:KH.C12.493"

# muscle : very clear 
tbx6c <- "KH2012:KH.S654.2"
myod <- "KH2012:KH.C14.307"

# B-mesench : very clear
twist_like_1a <- "KH2012:KH.C5.416"
twist_like_1b <- "KH2012:KH.C5.554"

# A-mesench
myt1 <- "KH2012:KH.C1.274"
pinhead <- "KH2012:KH.C2.1069"
fgf_8_17_18 <- "KH2012:KH.C5.5"

# a-NS 
dmrt1 <- "KH2012:KH.S544.3"
ci_zf249 <- "KH2012:KH.C4.182"
ephrinA_c <- "KH2012:KH.C3.52"
elk <- "KH2012:KH.C8.247"
a_ns_markers <- c(dmrt1, ci_zf249, ephrinA_c, elk)

# b-NS
msxb <- "KH2012:KH.C2.957"
delta_like <- "KH2012:KH.L50.6"
nodal <- "KH2012:KH.L106.16"
b_ns_markers <- c(msxb, delta_like, nodal)

# A-NS
fgf_9_16_20 <- "KH2012:KH.C2.125"
ci_zf064 <- "KH2012:KH.C11.318"
# this is super specific 
strong_A <- "KH2012:KH.C6.122"
A_ns_markers <- c(fgf_9_16_20, ci_zf064, strong_A)

# A-endo 
sfrp2 <- "KH2012:KH.C2.469"
eph4 <- "KH2012:KH.C1.146"

# to distinguish A from B-endoderm 
# should be: + A-endo, + A-mesench, - B-endo 
noTrl <- "KH2012:KH.C1.1116"
```

# a-NS
```{r include=TRUE}
FeaturePlot(clean_chen_larva_integrated_20,
            features = a_ns_markers)
```
# b-NS
```{r include=TRUE}
FeaturePlot(clean_chen_larva_integrated_20,
            features = b_ns_markers)
```
# A-NS
```{r include=TRUE}
FeaturePlot(clean_chen_larva_integrated_20,
            features = A_ns_markers)
```

# Noto-A/B
```{r include=TRUE}
# Hard to distinguish
FeaturePlot(clean_chen_larva_integrated_20,
            features = c(brachury,"KH2012:KH.C12.72", mnx, hes_a, noto_markers))
```

############### FAIL: END IDENTIFY ALL TISSUES IN LARVA 9/21/20 ##################
