---
title: "cz_CT_dict_helper"
output: html_document
---

# Follows from: "zeb_degs_heatmaps.Rmd"

# Works in parallel with: code in "get_all_orthologs" directory in Git.
# Above is part of Cocktail project, in which orthologous genes are used to infer
# orthologous Cell Types.

# General Description
# 1) Calculates top50 DEGs for Ciona Tissues. Present in ciona_marker_df_list.
# 2) Uses top50 DEGs calculated for Zeb Tissues from "zeb_degs_heatmaps.Rmd".
#    Present in zeb_marker_df_list.
# 3) Creates .csv files that have "num_DEG" (10) DEGs for each CT. 
#    for munging in "make_cocktail_dicts.py" -> creates ciona/zeb_cocktail_dicts.

# Uses env_get_pairwise_zeb_ciona_degs/get_geneset_troubleshooting.RData.

# TO DO Segways into <insert name>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=TRUE}
library(Seurat)
```

"""
Top50 Ciona DEGs
"""

```{r include=TRUE}
# I can use cell names for heart and muscle that came from putative_hm_seurat
# because these cells come from clean_chen_larva_integrated_20.
ciona_marker_df_list = list()

ciona_cell_type_flags <- c("endo", "epi", "mes", "mus", "heart", "cns", "noto")

for (i in 1:length(ciona_cell_type_list)) {
  cat("Now doing ", i, "=", ciona_cell_type_flags[i], "\n\n")
  
  ciona_marker_df <- get_top_n_df(ciona_cell_type_list[[i]], clean_chen_larva_integrated_20, "MAST", 50)
  
  ciona_marker_df_list[[ciona_cell_type_flags[i]]] <- ciona_marker_df
}

```

"""
Write out top10 DEGs as .csv
"""

```{r include=TRUE}
make_topN_df <- function(marker_df_list, num_DEGs) {
  # Given a marker_df_list of top50 DEG dataframes, make a dataframe with 
  # num_DEGs DEGs for every CT in the marker_df_list.
  # 
  # This df will be used to generate a .csv file of e.g. this structure: 
  # "endo", KHID_1... KHID_(num_DEGs)...
  #
  # Args:
  #   marker_df_list: e.g. ciona_marker_df_list ["endo": top50_df]
  #   num_DEGs: the number of DEGs you want to export.
  #
  # Returns:
  #   topN_df: Each row is a CT name.
  #            Each column (num_DEG) is the name of a DEG. 
  topN_matrix <- matrix(ncol=num_DEGs, nrow=length(marker_df_list))
  
  for(i in 1:length(marker_df_list)) {
    CT_df <- marker_df_list[[i]]
    topN_row <- rownames(CT_df)[1:num_DEGs]
    topN_matrix[i, ] <- topN_row
  }
  rownames(topN_matrix) <- names(marker_df_list)
  topN_df <- data.frame(topN_matrix)
  return(topN_df)
}
```

# Ciona 
```{r include=TRUE}
ciona_top10_df <- make_topN_df(ciona_marker_df_list, 10)

write.table(ciona_top10_df, 
            "ciona_top10_df.csv",
            col.names = FALSE,
            sep = ",")
```

# Zeb 1
# 1st need to make a list of df's that I want.
```{r include=TRUE}
# This list consists of the CTs present in "get_geneset_troubleshooting.Rmd"
zeb_marker_df_list = list()

zeb_marker_df_list$noto <- marker_df_list_1$noto
zeb_marker_df_list$heart_52 <- marker_df_list_1$heart_52
zeb_marker_df_list$heart_51_56 <- marker_df_list_1$heart_51_56
zeb_marker_df_list$muscles <- marker_df_list_1$muscles
zeb_marker_df_list$epi_1 <- marker_df_list_1$epi_1
zeb_marker_df_list$epi_2 <- marker_df_list_1$epi_2
zeb_marker_df_list$panc_prim_endo <- marker_df_list_1$panc_prim_endo
zeb_marker_df_list$ph_arch_ndnf <- marker_df_list_1$ph_arch_ndnf

zeb_marker_df_list$diff_neus <- marker_df_list_2$diff_neus
zeb_marker_df_list$nc_grem2 <- marker_df_list_2$nc_grem2

zeb_marker_df_list$meso <- marker_df_list_4$meso
zeb_marker_df_list$pec_fin_bud <- marker_df_list_4$pec_fin_bud
zeb_marker_df_list$iono <- marker_df_list_4$iono
zeb_marker_df_list$leuko <- marker_df_list_4$leuko
zeb_marker_df_list$lens <- marker_df_list_4$lens
zeb_marker_df_list$optic_cup <- marker_df_list_4$optic_cup
```

# Zeb 2
```{r include=TRUE}
zeb_top10_df <- make_topN_df(zeb_marker_df_list, 10)

write.table(zeb_top10_df, 
            "zeb_top10_df.csv",
            col.names = FALSE,
            sep = ",")
```



"""
Old 
"""
# Testing expression patterns of DEGs 
```{r include=TRUE}
test_cns <- rownames(ciona_marker_df_list$cns)

FeaturePlot(clean_chen_larva_integrated_20,
            features = c(test_cns[1:6], cns_markers[1:3]))
```

```
```

