---
title: "get_geneset_v4"
output: html_document
---

# Follows from: "get_geneset_troubleshooting.Rmd".

# Works in parallel with: None.

# General Description: Implements module v4:
# Run Tosches workflow (NEW IMPLEMENTATION) from "get_geneset_troubleshooting.Rmd" on all unflitered 1-1 orthologs. 

# khid_list and zeb_genes <- "make_one_to_one_khid_zeb_gene_dict.py" <- Ensembl 1-1 mapped orthologs.   
# Note: Some functions will need to be repurposed to get matrices of interest.

# They have new names: one2one2_khid_list and one2one_zeb_genes in "validate_get_geneset_v4.Rmd"
# because they become "generalized" variables. 

# Segways into: "validate_get_geneset_v4.Rmd"

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(Seurat)
library(dplyr)
library(ggplot2)
```

```{r include=TRUE}
'%notin%' <- Negate('%in%')
```

"""
Helper Function to make Gene Specificity Matrix (Tosches)
"""
```{r include=TRUE}
make_gene_specificity_matrix <- function(average_expression_matrix) {
  # Given an average expression matrix, convert to a gene specificity matrix (Tosches)
  # Args:
  #   average_expression_matrix: 
  #       e.g. ciona_average_expression_matrix <- cbind(ciona_df_1, ciona_df_2)
  #
  # Routine:
  #     g_c/(1/N)sum(i in C)g_i
  #
  # Returns:
  #   gsm: Output of above routine.
  gsm_1 <- average_expression_matrix
  # makes new column with  mean of the row (average expression of gene across all cell types)
  gsm_1 <- gsm_1 %>% mutate(gene_CTs_avexp = rowMeans(.))
  num_cell_types <- ncol(gsm_1)-1
  gsm <- gsm_1[, 1:num_cell_types]/gsm_1[, num_cell_types+1]
  
  return(gsm)
}
```


""""""""""""""""""""""""""""""""
Workflow
""""""""""""""""""""""""""""""""

"""
Get data matrices using all qualified genes (2600).
These are unique unfiltered 1-1 orthologs.
"""

# Get all unfiltered genes.
```{r include=TRUE}
# 30677 x 34750
zeb_data <- zeb_integrated_50[["RNA"]]@data
zeb_rownames <- rownames(zeb_data)
# 2600
common_zeb_genes <- intersect(zeb_rownames, zeb_genes)

# 14433 x 12005
ciona_data <- clean_chen_larva_integrated_20[["RNA"]]@data
ciona_rownames <- rownames(ciona_data)
# 2956
common_ciona_khids <- intersect(ciona_rownames, khid_list)
```

# Get their indices.
# Zeb 
```{r include=TRUE}
# 2602
qualified_zeb_indices <- which(zeb_genes %in% zeb_rownames)

dup_zeb_genes <- duplicated(zeb_genes)
# Duplicated indices: 2186, 2287
dup_zeb_indices <- which(dup_zeb_genes == TRUE)
validate_dup_zeb_genes <- zeb_genes[dup_zeb_indices]

# 2600
qualified_zeb_indices <- qualified_zeb_indices[qualified_zeb_indices %notin% dup_zeb_indices]
```

# Ciona 
```{r include=TRUE}
# 2965
qualified_ciona_indices <- which(khid_list %in% ciona_rownames)

dup_ciona_genes <- duplicated(khid_list)
# Duplicated indices: None.
dup_ciona_indices <- which(dup_ciona_genes == TRUE)
validate_dup_ciona_genes <- khid_list[dup_ciona_indices]

# 2956
qualified_ciona_indices <- qualified_ciona_indices[qualified_ciona_indices %notin% dup_ciona_indices]
```

# Which indices are in common?
```{r include=TRUE}
# 2592
common_indices <- intersect(qualified_zeb_indices, qualified_ciona_indices)
```

# Get qualified genes.
```{r include=TRUE}
qualified_zeb_genes <- zeb_genes[common_indices]
qualified_ciona_khids <- khid_list[common_indices]
```

"""
Ciona: Make Average Expression Dataframes for Ciona CTs (7).
ciona_avexp_df_v4 = ciona_df
"""

```{r include=TRUE}
ciona_dummy_col <- rep(0, length(qualified_ciona_khids))
ciona_df <- data.frame(ciona_dummy=ciona_dummy_col)

for (i in 1:length(ciona_cell_type_list)) {
  cat("i = ", i, "\n")
  ciona_cells <- ciona_cell_type_list[[i]]
  # Get gene exp values for all cells in a CT.
  ciona_data_pre <- ciona_data[qualified_ciona_khids, ciona_cells]
  ciona_data_df <- as.data.frame(ciona_data_pre)
  # Get av exp for each gene for all CTs.
  ciona_row <- rowMeans(ciona_data_df)
  ciona_df <- cbind(ciona_df, ciona_row)
}

# Remove ciona_dummy column.
ciona_df <- subset(ciona_df, select=-(ciona_dummy))

ciona_colnames <- names(ciona_cell_type_list)
colnames(ciona_df) <- ciona_colnames

# The Average Expression Dataframe 
ciona_avexp_df_v4 <- ciona_df
```

"""
Zeb: Make Average Expression Dataframes for Zeb CTs (16).
zeb_avexp_df_v4 = zeb_df

These are the same CTs used in Module v3 in "get_geneset_troubleshooting.Rmd"
"""
```{r include=TRUE}
zeb_cell_type_list_v4 <- list(noto = noto,
                             heart_52 = heart_52,
                             heart_51_56 = heart_51_56,
                             muscles = muscles,
                             epi_1 = epi_1,
                             epi_2 = epi_2,
                             panc_prim_endo = panc_prim_endo,
                             meso = meso,
                             pec_fin_bud = pec_fin_bud,
                             ph_arch_ndnf = ph_arch_ndnf,
                             iono = iono,
                             leuko = leuko,
                             lens = lens,
                             optic_cup = optic_cup,
                             diff_neus = diff_neus,
                             nc_grem2 = nc_grem2)
```
                             
```{r include=TRUE}
zeb_dummy_col <- rep(0, length(qualified_zeb_genes))
zeb_df <- data.frame(zeb_dummy=zeb_dummy_col)

####

for (i in 1:length(zeb_cell_type_list_v4)) {
  cat("i = ", i, "\n")
  zeb_cells <- zeb_cell_type_list_v4[[i]]
  # Get gene exp values for all cells in a CT.
  zeb_data_pre <- zeb_data[qualified_zeb_genes, zeb_cells]
  zeb_data_df <- as.data.frame(zeb_data_pre)
  # Get av exp for each gene for all CTs.
  zeb_row <- rowMeans(zeb_data_df)
  zeb_df <- cbind(zeb_df, zeb_row)
}

# Remove ciona_dummy column.
zeb_df <- subset(zeb_df, select=-(zeb_dummy))

zeb_colnames <- names(zeb_cell_type_list_v4)
colnames(zeb_df) <- zeb_colnames

# The Average Expression Dataframe
zeb_avexp_df_v4 <- zeb_df
```

"""
Make the GSM Dataframes, Cor Df 
"""
```{r include=TRUE}
ciona_gsm_v4 <- make_gene_specificity_matrix(ciona_avexp_df_v4)
zeb_gsm_v4 <- make_gene_specificity_matrix(zeb_avexp_df_v4)

cor_df_v4 <- make_cor_df(ciona_gsm_v4, zeb_gsm_v4)
```

```{r include=TRUE}
cor_df_v4 <- cor_df_v4 %>% transform(cor = as.numeric(cor))
```

# Visualize
```{r include=TRUE}
# "RdYlBu", "PiYG"
test_X = c("llama", "llama", "llama")
test_Y = c("duck", "alpaca", "swan")
test_vals <- c(1, 2, 3) 
test_df <- data.frame(x=test_X, y=test_Y, vals=test_vals)
  
test_heatmap <- ggplot(data=test_df,
                       aes(x=test_X, y=test_Y, fill=test_vals)) +
                       geom_tile() +
                       scale_fill_distiller(palette = "RdBu")

# test_heatmap
cor_df_v4_heatmap <- ggplot(data = cor_df_v4,
                         aes(x=ciona_CTs, y=zeb_CTs, fill=cor)) +
                         geom_tile() +
                         scale_fill_distiller(palette = "RdBu")
              

cor_df_v4_heatmap
```














## Vary profile, Seurat Object ##
```{r include=TRUE}
ciona_txnptomic_profile <- final_khids

# All tissues except for heart + muscle
ciona_seurat_1 <- clean_chen_larva_integrated_20
ciona_cluster_sizes_1 <- table(Idents(ciona_seurat_1))
ciona_av_exp_matrix_1 <- make_av_exp_matrix(ciona_seurat_1, ciona_txnptomic_profile)

# Heart + Muscle
ciona_seurat_2 <- putative_hm_seurat
ciona_cluster_sizes_2 <- table(Idents(ciona_seurat_2))
ciona_av_exp_matrix_2 <- make_av_exp_matrix(ciona_seurat_2, ciona_txnptomic_profile)

```
"""
All Tissues
(ciona_cluster_num_list_1, ciona_CT_vec_list1)
"""

## This will vary depending on the Seurat Object used ##
```{r include=TRUE}
# 3274
ciona_endo_cluster_nums <- c(12, 2, 20, 3, 0)
# 1959
ciona_epi_cluster_nums <- c(28, 5, 25, 4, 18, 19)
# 4203
ciona_mes_cluster_nums <- c(7, 30, 13, 21, 23, 1, 11, 22, 8, 10, 35, 14, 6)
# 1033
ciona_cns_cluster_nums <- c(26, 9, 15, 24)
# 550
ciona_noto_cluster_nums <- c(27)

# Make this manually.
ciona_cluster_num_list_1 <- list(endo = ciona_endo_cluster_nums,
                               epi = ciona_epi_cluster_nums,
                               mes = ciona_mes_cluster_nums,
                               cns = ciona_cns_cluster_nums,
                               noto = ciona_noto_cluster_nums)
```

```{r include=TRUE}
ciona_CT_vec_list1 <- make_CT_vec_list(ciona_cluster_num_list_1, ciona_av_exp_matrix_1, ciona_cluster_sizes_1)
```

"""
Heart + Muscle
(ciona_cluster_num_list_2, ciona_CT_vec_list2)
"""
```{r include=TRUE}
# 207
ciona_heart_cluster_nums <- c(2, 1, 0)
# 159
ciona_mus_cluster_nums <- c(7, 4, 3, 6, 8)

ciona_cluster_num_list_2 <- list(heart = ciona_heart_cluster_nums,
                                 mus = ciona_mus_cluster_nums)
```

```{r include=TRUE}
ciona_CT_vec_list2 <- make_CT_vec_list(ciona_cluster_num_list_2, ciona_av_exp_matrix_2, ciona_cluster_sizes_2)
```

"""
Ciona Average Expression Matrix
(ciona_average_expression_matrix)
"""
# Do manually.
```{r include=TRUE}
ciona_df_1 <- as.data.frame(do.call(cbind, ciona_CT_vec_list1))
ciona_df_2 <- as.data.frame(do.call(cbind, ciona_CT_vec_list2))

ciona_average_expression_matrix <- cbind(ciona_df_1, ciona_df_2)
```

"""
Ciona Gene Specificity Matrix
(ciona_gsm)
"""
```{r include=TRUE}
ciona_gsm <- make_gene_specificity_matrix(ciona_average_expression_matrix)
rownames(ciona_gsm) <- rownames(ciona_average_expression_matrix)
```


""""""""""""""""""""""""""""""""
     ** DO FOR ZEBRAFISH ** 
""""""""""""""""""""""""""""""""

"""
Common Zeb Variables
"""
## Vary profile ##
```{r include=TRUE}
zeb_txnptomic_profile <- final_zeb_genes

# All tissues except for heart + muscle
zeb_seurat <- zeb_integrated_50
zeb_cluster_sizes <- table(Idents(zeb_seurat))
zeb_av_exp_matrix <- make_av_exp_matrix(zeb_seurat, zeb_txnptomic_profile)
```
"""
Select Zeb Tissues
(zeb_cluster_num_list, zeb_CT_vec_list)
"""
## Can Vary Cell Types ##
```{r include=TRUE}
# Sanity Checks (4)
zeb_noto_cluster_nums <- 7

zeb_heart_52_cluster_nums <- 74 
zeb_heart_51_56_cluster_nums <- 17 

zeb_muscles_cluster_nums <- 37

# Bulk tissue (2)
zeb_epi_1_cluster_nums <- c(52, 31, 65, 14)
zeb_epi_2_cluster_nums <- c(44, 45, 51) 
zeb_panc_prim_endo_cluster_nums <- 73
zeb_meso_cluster_names <- 46

# Should have low correlation with Ciona tissues... (2)
zeb_pec_fin_bud_cluster_nums <- 38
zeb_ph_arch_ndnf_cluster_nums <- 33 

# For fun (2)
zeb_iono_cluster_nums <- 64 
zeb_leuko_cluster_nums <- 67 

# Neural and Optic Cell Types (4)
zeb_lens_cluster_nums <- 57 
zeb_optic_cup_cluster_nums <- c(12, 7, 3, 43)
# Should be a "CNS Sanity Check"
zeb_diff_neus_cluster_nums <- c(9, 47, 59, 27, 16, 68, 41)
zeb_nc_grem2_cluster_nums <- 23

# make this yourself 
zeb_cluster_num_list <- list(noto = zeb_noto_cluster_nums,
                             heart_52 = zeb_heart_52_cluster_nums,
                             heart_51_56 = zeb_heart_51_56_cluster_nums,
                             muscles = zeb_muscles_cluster_nums,
                             epi_1 = zeb_epi_1_cluster_nums,
                             epi_2 = zeb_epi_2_cluster_nums,
                             panc_prim_endo = zeb_panc_prim_endo_cluster_nums,
                             meso = zeb_meso_cluster_names,
                             pec_fin_bud = zeb_pec_fin_bud_cluster_nums,
                             ph_arch_ndnf = zeb_ph_arch_ndnf_cluster_nums,
                             iono = zeb_iono_cluster_nums,
                             leuko = zeb_leuko_cluster_nums,
                             lens = zeb_lens_cluster_nums,
                             optic_cup = zeb_optic_cup_cluster_nums,
                             diff_neus = zeb_diff_neus_cluster_nums,
                             nc_grem2 = zeb_nc_grem2_cluster_nums)
```

```{r include=TRUE}
zeb_CT_vec_list <- make_CT_vec_list(zeb_cluster_num_list, zeb_av_exp_matrix, zeb_cluster_sizes)
```

"""
Zeb Average Expression Matrix
(zeb_average_expression_matrix)
"""

# Do manually.
```{r include=TRUE}
zeb_average_expression_matrix <- as.data.frame(do.call(cbind, zeb_CT_vec_list))
```

"""
Zeb Gene Specificity Matrix
(zeb_gsm)
"""
```{r include=TRUE}
zeb_gsm <- make_gene_specificity_matrix(zeb_average_expression_matrix)
rownames(zeb_gsm) <- rownames(zeb_average_expression_matrix)
```

"""""""""""""""""""""""""""
Do Spearman Correlations!
"""""""""""""""""""""""""""
# Helper Function 
```{r include=TRUE}
make_cor_df <- function(ciona_gsm, zeb_gsm) {
  cz_cor_df <- data.frame(ciona_CTs = 0,
                             zeb_CTs = 0,
                             cor = 0)
  
  for (i in 1:ncol(ciona_gsm)) {
    for (j in 1:ncol(zeb_gsm)) {
      # CT expression vectors 
      ciona_CT_col <- ciona_gsm[, i]
      zeb_CT_col <- zeb_gsm[, j]
      # CT name
      ciona_CT <- colnames(ciona_gsm)[i]
      zeb_CT <- colnames(zeb_gsm)[j]
      cat("i= ", i, "j= ", j, "ciona_CT= ", ciona_CT, "zeb_CT= ", zeb_CT, "\n")
      cz_cor <- cor(ciona_CT_col, zeb_CT_col, method = "spearman")
      cat("cor = ", cz_cor, "\n\n")
      cz_row <- c(ciona_CT, zeb_CT, cz_cor)
      cat("row = ", cz_row)
      cz_cor_df <- rbind(cz_cor_df, cz_row)
    }
  }
  cz_cor_df <- cz_cor_df[-1, ]
  return(cz_cor_df)
}
```

```{r include=TRUE}
cz_cor_df <- make_cor_df(ciona_gsm, zeb_gsm)
```

```{r include=TRUE}
cz_cor_df <- cz_cor_df %>% transform(cor = as.numeric(cor))
```

# Visualize
```{r include=TRUE}
# "RdYlBu", "PiYG"
cz_cor_heatmap <- ggplot(data = cz_cor_df,
                         aes(x=ciona_CTs, y=zeb_CTs, fill=cor)) + 
                         scale_fill_distiller(palette = "RdBu")

cz_cor_heatmap
```

















"""
Just in case tests (Also present in Journal "get_geneset_v4.Rmd")
"""

# USE THIS TEST
```{r include=TRUE}
test_index <- 20
dummy_col <- rep(0, 20)
test_ciona_df <- data.frame(dummy=dummy_col)

for (i in 1:length(ciona_cell_type_list)) {
  cat("i = ", i, "\n")
  test_ciona_cells <- ciona_cell_type_list[[i]]
  test_ciona_data <- ciona_data[qualified_ciona_khids, test_ciona_cells]
  
  test_ciona_data_df <- as.data.frame(test_ciona_data[1:test_index, 1:test_index])
  test_ciona_row <- rowMeans(test_ciona_data_df)
  test_ciona_df <- cbind(test_ciona_df, test_ciona_row)
}
test_ciona_colnames <- c("dummy", names(ciona_cell_type_list))
colnames(test_ciona_df) <- test_ciona_colnames

test_ciona_df

```
