---
title: "temp_more_VarGenes"
output: html_document
---

# Increase zeb_n_features - increase upper bound of DEGs that can be found # # dims=50, n_anchor_feats=8000, npcs=70. Note: n_anchor_feats=10000 crashed on Vera.   

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(Seurat)
library(dplyr)
library(ggplot2)
library(purrr)
library(Hmisc)
library(pvclust)
library(edgeR)
```

"""
Helper Functions
"""

(1) Make raw matrix data frames
```{r include=TRUE}
make_zeb_df <- function(zeb_dir) {
  zeb_df <- read.table(zeb_dir,
                       sep = ",",
                       header = TRUE,
                       stringsAsFactors = FALSE)
  
  rownames(zeb_df) <- zeb_df$Row
  zeb_df$Row <- NULL
  
  return(zeb_df)
}
```

(2) Make Individual Seurat Objects. 
```{r include=TRUE}
make_zeb_seurat <- function(zeb_df, min_cells, min_features, n_features){
  zeb_seurat <- CreateSeuratObject(counts = zeb_df,
                                   min.cells = min_cells, 
                                   min.features = min_features)
  
  zeb_seurat <- NormalizeData(object = zeb_seurat)
  
  zeb_seurat <- FindVariableFeatures(zeb_seurat, 
                                     selection.method = "vst",
                                     nfeatures = n_features)
  return(zeb_seurat)
  }
```


"""
Make Raw Matrix Dataframes.
"""
# T = 34750 (exactly what is reported in Fig S2B)
```{r include=TRUE}
zeb_24hpf_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/Raw_Data/Klein_2018/GSM3067195_24hpf.csv" 

# 7970
zeb_24hpf_df <- read.table(zeb_24hpf_dir,
                          sep = ",",
                          header = TRUE,
                          stringsAsFactors = FALSE)

# Clean up the dataframe
rownames(zeb_24hpf_df) <- zeb_24hpf_df$Row
zeb_24hpf_df$Row <- NULL
```

https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSM3067196,  
```{r include=TRUE}
zeb_t1_dir <- "~/princeton_google_drive/Levine Lab/Orthology-Maps/Raw_Data/Klein_2018/GSM3067196_TracerSeq1.csv"
# 5752
zeb_t1_24hpf_df <- make_zeb_df(zeb_t1_dir)
```

https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSM3067197,
```{r include=TRUE}
zeb_t2_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/Raw_Data/Klein_2018/GSM3067197_TracerSeq2.csv"
# 8874
zeb_t2_24hpf_df <- make_zeb_df(zeb_t2_dir)
```

https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSM3067198,
```{r include=TRUE}
zeb_t3_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/Raw_Data/Klein_2018/GSM3067198_TracerSeq3.csv"
# 2861
zeb_t3_24hpf_df <- make_zeb_df(zeb_t3_dir)
```

https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSM3067199,
```{r include=TRUE}
zeb_t4_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/Raw_Data/Klein_2018/GSM3067199_TracerSeq4.csv"
# 6495
zeb_t4_24hpf_df <- make_zeb_df(zeb_t4_dir)
```

https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSM3067200
```{r include=TRUE}
zeb_t5_dir <- "/home/pprakriti/princeton_google_drive/Levine Lab/Orthology-Maps/Raw_Data/Klein_2018/GSM3067200_TracerSeq5.csv"
# 2844
zeb_t5_24hpf_df <- make_zeb_df(zeb_t5_dir)
```


"""
Perform standard pre-processing steps on each Seurat object.

https://satijalab.org/seurat/v3.1/integration.html
"""

```{r include=TRUE}
zeb_min_cells <- 3
zeb_min_features <- 200
zeb_n_features <- 8000
```

```{r include=TRUE}
zeb_24hpf_seurat <- make_zeb_seurat(zeb_24hpf_df,
                                    zeb_min_cells,
                                    zeb_min_features,
                                    zeb_n_features)
```

```{r include=TRUE}

zeb_t1_24hpf_seurat <- make_zeb_seurat(zeb_t1_24hpf_df,
                                    zeb_min_cells,
                                    zeb_min_features,
                                    zeb_n_features)

zeb_t2_24hpf_seurat <- make_zeb_seurat(zeb_t2_24hpf_df,
                                    zeb_min_cells,
                                    zeb_min_features,
                                    zeb_n_features)

zeb_t3_24hpf_seurat <- make_zeb_seurat(zeb_t3_24hpf_df,
                                    zeb_min_cells,
                                    zeb_min_features,
                                    zeb_n_features)

zeb_t4_24hpf_seurat <- make_zeb_seurat(zeb_t4_24hpf_df,
                                    zeb_min_cells,
                                    zeb_min_features,
                                    zeb_n_features)

zeb_t5_24hpf_seurat <- make_zeb_seurat(zeb_t5_24hpf_df,
                                    zeb_min_cells,
                                    zeb_min_features,
                                    zeb_n_features)
```

"""
Make list of above Seurat Objects
"""

```{r include=TRUE}
zeb_seurat_list <- list(zeb_24hpf_seurat, zeb_t1_24hpf_seurat, zeb_t2_24hpf_seurat, zeb_t3_24hpf_seurat, zeb_t4_24hpf_seurat, zeb_t5_24hpf_seurat)
```


"""
Integration Routine Pieces
"""
```{r include=TRUE}
test_dims <- 50
test_n_anchor_feats <- 8000
test_object_list <- zeb_seurat_list
```

```{r include=TRUE}
zeb_anchors <- FindIntegrationAnchors(object.list = test_object_list,
                                      dims = 1:test_dims,
                                      anchor.features = test_n_anchor_feats)
```

```{r include=TRUE}
cat("IntegrateData, \n\n")
zeb_integrated <- IntegrateData(anchorset = zeb_anchors, dims = 1:test_dims)
```

```{r include=TRUE}
cat("DefaultAssay, \n\n")
DefaultAssay(zeb_integrated) <- "integrated"
```

```{r include=TRUE}
cat("ScaleData, \n\n")
```


################### INTEGRATION PIPELINE ####################

# Helper Function
```{r include=TRUE}
make_integrated_seurat <- function(object_list, dims, n_anchor_feats, npcs){
  # Args:
    # object_list: list of Seurat objects. e.g. zeb_seurat_list.
    # dims: input dimensions for FindIntegrationAnchors and IntegrateData. 
    # npcs: # pcs for PCA and TSNE.
  
  # Routine: Do integration. Scale, PCA, TSNE.
  
  # Returns:
    # integrated_seurat: output of above routine.
  cat("Finding Zeb Anchors, \n\n")
  zeb_anchors <- FindIntegrationAnchors(object.list = object_list,
                                      dims = 1:dims,
                                      anchor.features = n_anchor_feats)
  cat("IntegrateData, \n\n")
  zeb_integrated <- IntegrateData(anchorset = zeb_anchors, dims = 1:dims)
  cat("DefaultAssay, \n\n")
  DefaultAssay(zeb_integrated) <- "integrated"
  cat("ScaleData, \n\n")
  zeb_integrated <- ScaleData(zeb_integrated, verbose = FALSE)
   cat("RunPCA, \n\n")
  zeb_integrated <- RunPCA(zeb_integrated, npcs = npcs, verbose = FALSE)
   cat("RunTSNE, \n\n")
  zeb_integrated <- RunTSNE(zeb_integrated, dims = 1:npcs)
  
  return(zeb_integrated)
}
```

<!-- # dims=50, n_anchor_feats=8000, npcs=70  -->
<!-- ```{r include=TRUE} -->
<!-- zeb_integrated_50 <- make_integrated_seurat(zeb_seurat_list, 50, 8000, 70) -->
<!-- ``` -->

